---
title: "pije segmented regressions: rwc"
author: "Indra Boving & Joe Celebrezze"
date: "4/15/2021"
output: html_document
---

# Setup
```{r}
knitr::opts_chunk$set(echo = TRUE)
#lots of extra here, but oh well___ 
library(ggplot2)
library(gapminder)
library(tidyverse)
library(lme4)
library(here)
library(segmented)
library(nlme)
library(lubridate)
library(plotrix)
filter = dplyr::filter
here = here::here
select = dplyr::select

# Function to plot mixed effects model segmented regressions:
source(here::here("scripts", "scripts_functions", "plot_segmented_MEM_V2.R"))
```

# -------
# Visualization Function
```{r}
rsegplot.rwc <- function(model, dataframe, x.variable = 'rwc', y.variable, max.x,
                         x.lab = 'Relative Water Content', y.lab = NULL) {
  
  p <- summary.segmented(model)$psi[2]
  m <- slope(model, .coef = fixef(model))[[1]][[1]]
  b <- intercept(model, .coef = fixef(model))[[1]][[1]]
  m2 <- slope(model, .coef = fixef(model))[[1]][[2]]
  b2 <- intercept(model, .coef = fixef(model))[[1]][[2]]
  yvar <- dataframe[[y.variable]]
  xvar <- dataframe[[x.variable]]
  confint <- confint.segmented(model, x.variable, .coef=fixef(model))
  lower <- confint[2]
  upper <- confint[3]
  ymax <- max(yvar)
  ymin <- min(yvar)
  
  wacky <- plot(xvar, yvar, xlim = c(0, max.x), ylim = c(ymin-0.05*ymin, ymax+0.05*ymax), 
                xlab = x.lab, ylab = y.lab,
                pch = 16, col = alpha('black', 0.8),
                cex.lab = 1.3)
  polygon(x = c(lower, upper, upper, lower), y = c(ymax + 0.2*ymax, ymax +0.2*ymax, ymin - 30, ymin - 30), col = alpha('gray', 0.3), lty = 2)
  for(z in 1:length(xvar)){
    if(z < p){
      segments(x0 = 0, x1 = p, y0 = b, y1 = m*((b2 - b)/(m - m2))+b, lwd = 3, col = "#9D0208")
    }else{
      segments(x0 = p, x1 = max.x, y0 = m2*((b - b2)/(m2 - m))+b2 , y1 = m2*max.x + b2, lwd = 3, col = "#9D0208")}}
  return(wacky)
}
```


# Reading in Dataframe
```{r}
seg_data_subset <- read_csv(here("processed-data", "analysis 2.0", "sierra_flam_data_all.csv")) %>% 
  mutate(id = individual)
```

# Color by Season

```{r}
seg_data_subset$color <- "#ee8577"
seg_data_subset$color[seg_data_subset$year_month=='2020_october']="#ce4441"
seg_data_subset$color[seg_data_subset$year_month=='2020_september']="#c969a1"
seg_data_subset$color[seg_data_subset$year_month=='2021_august']="#ffbb44"
```

# Splitting by Species and by Sampling Date

```{r} 
seg_data_subset <- seg_data_subset %>% 
  mutate_if(is.character, str_to_lower) %>% 
  mutate(spp = str_trim(spp),
         rwc_scaled = scale(rwc),
    name = paste(spp,"_max", sep = ""), 
    name_subset = paste(spp, "_subset_seg", sep = ""), #this is def working. 
   # name_yearmonth = intersect(spp, year_month), 
    name_yearmonth = paste(spp, year_month, "subset_seg", sep = "_")) %>% 
  drop_na(rwc, mpa) #Dropping NA values for both rwc and mpa

pije_subset_seg <- seg_data_subset %>% 
  filter(spp == "pije")

pije_2020_oct_subset_seg <- seg_data_subset %>% 
  filter(spp == "pije", 
         year_month == "2020_october")

pije_2020_sept_subset_seg <- seg_data_subset %>% 
  filter(spp == "pije", 
         year_month == "2020_september")

pije_2020_subset_seg <- seg_data_subset %>% 
  filter(spp == "pije", 
         year_month %in% c("2020_september", "2020_october"))

pije_2021_aug_subset_seg <- seg_data_subset %>% 
  filter(spp == "pije", 
         year_month == "2021_august")

# seg_data_subset %>% 
#   group_split(spp) %>%
#   #rowwise() %>% 
#   setNames(unique(seg_data_subset$name_subset))  %>% #this is not working...wrong name for df. 
#   list2env(envir = globalenv())

# seg_data_subset %>% 
#   group_split(name_yearmonth) %>%
#   setNames(unique(seg_data_subset$name_yearmonth))  %>%
#   list2env(envir = globalenv())
```


# Maximums for RWC

```{r}
max_seg_data <- seg_data_subset %>% 
  type.convert(as.is = TRUE) %>% 
  select(rwc, spp) %>% 
  group_by(spp) %>% 
  summarise(across(where(is.numeric), max, .names = "max_{.col}")) 

pije_max_rwc <- max_seg_data %>% 
  filter(spp == "pije") %>% 
  select(max_rwc) %>% 
  pull()
```

# PV Curve Data
Note: will add TLP in later and use full function, but for now (since I am just seeing if RWC performs any better than rwc or mpa) I am going to simplify it. I am pessimistic that this will work any better than rwc or mpa anyways since I think it is more of an issue on the flammability data being noisy with the hot plate method rather than it being a messy correlation with rwc and/or mpa

# Summary Vis.

```{r}
pije_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(year_month, location, tti, fh, fd, gd, temp_change, prop_ignite) %>%
  gather(-year_month, -location, key = "var", value = "value") %>%
  ggplot() +
  geom_density(aes(x = value, 
                   color = year_month, 
                   fill = year_month), 
               alpha = .4) +
  facet_wrap(~ var, scales = "free") 
```

```{r}
pije_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(year_month, year, location, tti, fh, fd, gd, temp_change, prop_ignite) %>%
  gather(-year_month, -location, -year, key = "var", value = "value") %>%
  ggplot() +
  geom_density(aes(x = value, 
                   color = as.factor(year), 
                   fill =  as.factor(year)),
               alpha = .4) +
  facet_wrap(~ var, scales = "free") 
```

```{r}
pije_cor <- pije_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(tti, fh, fd, gd, temp_change, prop_ignite, rwc, mpa) %>% 
  drop_na() %>% 
  cor()

corrplot::corrplot.mixed(pije_cor, order = 'AOE')
```


# -------

# Seg. Regressions 

We're just going to do a few metrics, to represent each of the axes: 

Ignitability: TTI, Prop.ignite

Combustibility: FH, Max Temp, Temp Change

Sustainability: FD, 

Consumability: GD

Maybe: Max temp

### Holding Vectors
This will be a dataframe with all to collect results as we go: 

No random effects: 

```{r}
rwc_psi_tti <- c(rep(NaN, 1))
rwc_psi_fh <- c(rep(NaN, 1))
rwc_psi_fd <- c(rep(NaN, 1))
rwc_psi_gd <- c(rep(NaN, 1))
#rwc_psi_gti <- c(rep(NaN, 1))
#rwc_psi_rwc_pfg <- c(rep(NaN, 1))
#rwc_psi_ttfg <- c(rep(NaN, 1))
rwc_psi_fd <- c(rep(NaN, 1))
rwc_psi_prop_ignite <- c(rep(NaN, 1))
rwc_psi_temp_change <- c(rep(NaN, 1))

rwc_st_err_tti <- c(rep(NaN, 1))
rwc_st_err_fh <- c(rep(NaN, 1))
rwc_st_err_fd <- c(rep(NaN, 1))
rwc_st_err_gd <- c(rep(NaN, 1))
#rwc_st_err_gti <- c(rep(NaN, 1))
#rwc_st_err_rwc_pfg <- c(rep(NaN, 1))
#rwc_st_err_ttfg <- c(rep(NaN, 1))
rwc_st_err_fd <- c(rep(NaN, 1))
rwc_st_err_prop_ignite <- c(rep(NaN, 1))
rwc_st_err_temp_change <- c(rep(NaN, 1))

rwc_p_value_tti <- c(rep(NaN, 1))
rwc_p_value_fh <- c(rep(NaN, 1))
rwc_p_value_fd <- c(rep(NaN, 1))
rwc_p_value_gd <- c(rep(NaN, 1))
#rwc_p_value_gti <- c(rep(NaN, 1))
#rwc_p_value_rwc_pfg <- c(rep(NaN, 1))
#rwc_p_value_ttfg <- c(rep(NaN, 1))
rwc_p_value_fd <- c(rep(NaN, 1))
rwc_p_value_prop_ignite <- c(rep(NaN, 1))
rwc_p_value_temp_change <- c(rep(NaN, 1))

rwc_pije_thresholds_seg <- tibble::data_frame(rwc_psi_tti, rwc_st_err_tti, rwc_p_value_tti,
                              rwc_psi_fh, rwc_st_err_fh, rwc_p_value_fh,
                              rwc_psi_fd, rwc_st_err_fd,rwc_p_value_fd,
                              rwc_psi_gd, rwc_st_err_gd, rwc_p_value_gd, 
                              #rwc_psi_gti, rwc_st_err_gti, 
                              #rwc_psi_rwc_pfg, rwc_st_err_rwc_pfg, 
                              #rwc_psi_ttfg, rwc_st_err_ttfg,
                              rwc_psi_prop_ignite, rwc_st_err_prop_ignite, rwc_p_value_prop_ignite,
                              rwc_psi_temp_change, rwc_st_err_temp_change, rwc_p_value_temp_change
                              )
```


Randem effecs: 

```{r}
rwc_psi_tti <- c(rep(NaN, 1))
rwc_psi_fh <- c(rep(NaN, 1))
rwc_psi_fd <- c(rep(NaN, 1))
rwc_psi_gd <- c(rep(NaN, 1))
#rwc_psi_gti <- c(rep(NaN, 1))
#rwc_psi_rwc_pfg <- c(rep(NaN, 1))
#rwc_psi_ttfg <- c(rep(NaN, 1))
rwc_psi_fd <- c(rep(NaN, 1))
rwc_psi_prop_ignite <- c(rep(NaN, 1))
rwc_psi_temp_change <- c(rep(NaN, 1))

rwc_st_err_tti <- c(rep(NaN, 1))
rwc_st_err_fh <- c(rep(NaN, 1))
rwc_st_err_fd <- c(rep(NaN, 1))
rwc_st_err_gd <- c(rep(NaN, 1))
#rwc_st_err_gti <- c(rep(NaN, 1))
#rwc_st_err_rwc_pfg <- c(rep(NaN, 1))
#rwc_st_err_ttfg <- c(rep(NaN, 1))
rwc_st_err_fd <- c(rep(NaN, 1))
rwc_st_err_prop_ignite <- c(rep(NaN, 1))
rwc_st_err_temp_change <- c(rep(NaN, 1))

rwc_pije_thresholds_rand_seg <- tibble::data_frame(rwc_psi_tti, rwc_st_err_tti,
                              rwc_psi_fh, rwc_st_err_fh, 
                              rwc_psi_fd, rwc_st_err_fd,
                              rwc_psi_gd, rwc_st_err_gd, 
                              #rwc_psi_gti, rwc_st_err_gti, 
                              #rwc_psi_rwc_pfg, rwc_st_err_rwc_pfg, 
                              #rwc_psi_ttfg, rwc_st_err_ttfg,
                              rwc_psi_prop_ignite, rwc_st_err_prop_ignite, 
                              rwc_psi_temp_change, rwc_st_err_temp_change)
```


### Time to Ignition

```{r}
pije_subset_seg_tti <- pije_subset_seg %>%
  drop_na(tti)

#Segmented regression with random changepoints: 

o_mod<-lme(tti~rwc + year_month + site, random=~1|id, data=pije_subset_seg_tti)
os_mod_b<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_b)

#put into the df:
rwc_pije_thresholds_rand_seg[1] <- summary(os_mod_b)$psi[2]
rwc_pije_thresholds_rand_seg[2] <- summary(os_mod_b)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(tti~rwc + year_month + site, data = pije_subset_seg_tti)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_pije_thresholds_seg[1] <- summary(u_mod_b)$psi[2]
rwc_pije_thresholds_seg[2] <- summary(u_mod_b)$psi[3]
rwc_pije_thresholds_seg[3] <- u_mod_davies$p.value


rsegplot.rwc(os_mod_b, pije_subset_seg_tti, max.x = pije_max_rwc, y.variable = 'tti', y.lab = "Time to Ignition (s)")
```
Combustibility Metrics:

### Flame Height
```{r}
pije_subset_seg_fh <- pije_subset_seg %>% drop_na(fh) 

o_mod<-lme(fh~rwc + year_month + site, random=~1|id, data=pije_subset_seg_fh)
os_mod<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
rwc_pije_thresholds_rand_seg[3] <- summary(os_mod)$psi[2]
rwc_pije_thresholds_rand_seg[4] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fh~rwc + year_month + site, data = pije_subset_seg_fh)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_pije_thresholds_seg[4] <- summary(u_mod_b)$psi[2]
rwc_pije_thresholds_seg[5] <- summary(u_mod_b)$psi[3]
rwc_pije_thresholds_seg[6] <- u_mod_davies$p.value

rsegplot.rwc(os_mod, pije_subset_seg_fh, max.x = pije_max_rwc, y.variable = 'fh', y.lab = "Flame Height (cm)")
```

Sustainability Metrics:
### Flame Duration
```{r}
pije_subset_seg_fd <- pije_subset_seg %>% drop_na(fd)

o_mod<-lme(fd~rwc + year_month + site, random=~1|id, data=pije_subset_seg_fd)
os_mod <-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
rwc_pije_thresholds_rand_seg[5] <- summary(os_mod)$psi[2]
rwc_pije_thresholds_rand_seg[6] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fd~rwc + year_month + site, data = pije_subset_seg_fd)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_pije_thresholds_seg[7] <- summary(u_mod_b)$psi[2]
rwc_pije_thresholds_seg[8] <- summary(u_mod_b)$psi[3]
rwc_pije_thresholds_seg[9] <- u_mod_davies$p.value

rsegplot.rwc(os_mod, pije_subset_seg_fd, max.x = pije_max_rwc, y.variable = 'fd', y.lab = "Flame Duration (s)")
```

### Glow Duration
```{r}
pije_subset_seg_gd <- pije_subset_seg %>% drop_na(gd)

o_mod<-lme(gd~rwc + year_month + site, random=~1|id, data=pije_subset_seg_gd)
os_mod <-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
rwc_pije_thresholds_rand_seg[7] <- summary(os_mod)$psi[2]
rwc_pije_thresholds_rand_seg[8] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(gd~rwc + year_month + site, data = pije_subset_seg_gd)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_pije_thresholds_seg[10] <- summary(u_mod_b)$psi[2]
rwc_pije_thresholds_seg[11] <- summary(u_mod_b)$psi[3]
rwc_pije_thresholds_seg[12] <- u_mod_davies$p.value

rsegplot.rwc(os_mod, pije_subset_seg_gd, max.x = pije_max_rwc, y.variable = 'gd', y.lab = "Glow Duration (s)")
```


### Prop. Ignite (5%)
```{r}
pije_subset_seg_prop_ignite <- pije_subset_seg %>% drop_na(prop_ignite)

o_mod<-lme(prop_ignite~rwc + year_month + site, random=~1|id, pije_subset_seg_prop_ignite )
os_mod<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
rwc_pije_thresholds_rand_seg[9] <- summary(os_mod)$psi[2]
rwc_pije_thresholds_rand_seg[10] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(prop_ignite~rwc + year_month + site, data = pije_subset_seg_prop_ignite)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_pije_thresholds_seg[13] <- summary(u_mod_b)$psi[2]
rwc_pije_thresholds_seg[14] <- summary(u_mod_b)$psi[3]
rwc_pije_thresholds_seg[15] <- u_mod_davies$p.value

rsegplot.rwc(os_mod, pije_subset_seg_prop_ignite, max.x = pije_max_rwc, y.variable = 'prop_ignite', y.lab = "Proportion Ignted (5% Bins of rwc)")
```

### Temp Change

```{r}
pije_subset_seg_temp_change <- pije_subset_seg %>% 
  drop_na(temp_change)

o_mod<-lme(lower_temp_max~rwc + year_month + site, random=~1|id, data=pije_subset_seg_temp_change)
os_mod<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)
os_mod

#put into the df:
rwc_pije_thresholds_rand_seg[11] <- summary(os_mod)$psi[2]
rwc_pije_thresholds_rand_seg[12] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(temp_change~rwc + year_month + site, data = pije_subset_seg_temp_change)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_pije_thresholds_seg[16] <- summary(u_mod_b)$psi[2]
rwc_pije_thresholds_seg[17] <- summary(u_mod_b)$psi[3]
rwc_pije_thresholds_seg[18] <- u_mod_davies$p.value

rsegplot.rwc(os_mod, pije_subset_seg_temp_change, max.x = pije_max_rwc, y.variable = 'temp_change', y.lab = "Temp Change (C)")
```

# Final Table 
```{r}
#No random effects: 
pije_rwc_summary_df <- rwc_pije_thresholds_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'rwc_', ''),
         across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "segmented") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
pije_rwc_summary_df

#with random effects: 
pije_rwc_rand_summary_df <- rwc_pije_thresholds_rand_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'rwc_', ''),
         across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "random") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
pije_rwc_rand_summary_df

pije_rwc <- bind_rows(pije_rwc_rand_summary_df, pije_rwc_summary_df) %>% 
  mutate(spp = "pije", 
         water_variable = "rwc") 

#ggsave(plot=gridExtra::tableGrob(pije_rwc), filename=here("figures", "segmented_tables", "rand_segmented_rwc_pije.png"))
```

