---
title: "Data Wrangling & PV Curves"
author: "Indra Boving"
date: "10/24/2021"
output: html_document
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(janitor)
library(plotly)
library(DT)
library(broom)
library(lubridate)
library(udpipe)
library(dlookr)
library(tidyverse)
library(kableExtra)

here = here::here

source(here("scripts", "scripts_functions", "figure_info_sierra_flammability.R"))
source(here("scripts", "scripts_functions", "outlierKD2.R"))
```

# Overview

This script organizes the compiled PV Curve data and does some basic visualizations. Additionally, it compiles water-relations data from the flammability testing and organizes to compare with PV Curves (saturated water content and lfm). Lastly, it approximates saturated water content and RWC from the field-collected data.

**Goal**: see how PV curves (which use RWC) compare to benchtop or field (where need to convert all values to RWC)
#--------------------------
# Lit-Derived Species Data

```{r}
p50s <- c(-2.65, -3.74, -7.98, -7.75, -8.08, NA, NA, NA, NA, -4.41, -3.02)
spp.p50 <- c("PIPO", "CECO", "ADFA", "CADE", "CEME", "QUKE", "CECO", "PIJE", "CECO", "ARGL", "ABCO")

p50_reference <- c()

tlp <- c(-2.91, NA, -3.4, -3.14, -2.24, -2.8, -2.6, NA, NA, NA, NA)
spp.tlp <- c("PIPO", "CECO", "ADFA", "ADFA", "CEME", "CEME", "ABGR", NA, NA, NA, "ABCO")

tlp_reference <-c("Jackson & Spomer, 1979", NA, "Pivavoroff, 2019", "Ramirez dissertation", "Ramirez dissertation", "Fletcher et al. 2018", "Jackson & Spomer, 1979", NA, NA, NA, "Boving, SEKI proj.")

lit_values <- data.frame(spp.p50, p50s, spp.tlp, tlp, tlp_reference)
datatable(lit_values)
```
#--------------------------
# 1. PV Curves

This section is to summarise all of our PV curve data

Read in data and clean names, remove any odd curves

```{r}
Sys.setenv("VROOM_CONNECTION_SIZE" = 500073)
#pv_allcurves_data <- readr::read_csv(here("raw-data", "allcurves.csv"), show_col_types = FALSE)

#pv_allcurves_data_txt <- readr::read_delim(here("raw-data", "allcurves_copy_txt.txt"), show_col_types = FALSE)

# pv_allcurves_data_old <- read.csv(here("raw-data", "allcurves.csv")) %>%
#   clean_names() %>%
#   mutate(lfm = (((fresh_weight - dry_weight)/dry_weight)* 100)) %>%
#   mutate(neg_mpa = -1/water_potential) %>%
#   mutate(sample = as.character(sample)) %>%
#   mutate(date = as.Date(date, format = '%m.%d.%Y')) %>%
#   mutate(year = year(date)) %>%
#   mutate(month = month(date))

pv_allcurves_data <- read_csv(here("raw-data", "allcurves.csv")) %>%
  clean_names() %>%
  select(-swc) %>%
  mutate(fresh_weight_saturated = as.numeric(fresh_weight_saturated)) %>%
  dplyr::mutate(water_weight = fresh_weight - dry_weight,
     	lfm = (((fresh_weight - dry_weight)/dry_weight)* 100),
     	swc = fresh_weight_saturated - dry_weight,
     	rwc = fresh_weight/fresh_weight_saturated,
     	rwd = 100 - rwc,
     	tlp = tlp,
     	neg_mpa = -1/water_potential,
     	sample = as.character(sample),
     	date = mdy(date),
    	# date = as.Date(date, format = '%m.%d.%Y'),
     	year = year(date),
     	month = month(date)
     	)

  #deal with bag added to CECO in 2020:

#pv curve data without CECO:
pv_allcurves_noceco <- pv_allcurves_data %>%
  filter(!(spp %in% c("CECO") & year == 2020))

#Just CECO TLP information:
pv_tlp_data_ceco <- read_csv(here("raw-data", "PV_sierra_summaries.csv")) %>%
  clean_names() %>%
  mutate(fresh_weight_saturated = swc,
     	po = po_m_pa,
     	tlp = ytlp_m_pa,
     	rwc_at_tlp = rwctlp,
     	lfm_at_tlp = lf_mtlp,
     	date = mdy(date),
     	year = year(date),
     	month = month(date),
     	#timing = "fall",
     	sample = replicate,
     	.keep = "unused"
     	) %>%
  filter(species %in% c("CECO") & year == 2020) %>%
  select(-date, -e_m_pa, - cft_m_pa_1, -ctlp_m_pa_1, -cft_mol_m_2_m_pa_1)

#Just CECO full curve data:
pv_ceco_2020 <- pv_allcurves_data %>%
  filter(spp %in% c("CECO") & year == 2020) %>%
  select(-lfm, swc, rwc, rwd, water_weight) %>%
  mutate(fresh_weight = fresh_weight - 0.8754, #<- avg. weight of plastic bags used during analysis (bag was used and not accounted for)
     	#fresh_weight_saturated = fresh_weight_saturated - 0.8754,
     	water_weight = fresh_weight - dry_weight,
     	lfm = (((fresh_weight - dry_weight)/dry_weight)* 100),
    	# swc = fresh_weight_saturated - dry_weight,
     	#rwc = fresh_weight/fresh_weight_saturated,
     	#rwd = 100 - rwc
    	) %>%
  select(-po, -tlp, -rwc_at_tlp, -lfm_at_tlp, -fresh_weight_saturated)

pv_ceco_2020_tlp_data <- merge(pv_ceco_2020, pv_tlp_data_ceco,
                           	by = c("sample", "month", "year"),
                           	all.x = T) %>%
  mutate( water_weight = fresh_weight - dry_weight,
     	lfm = (((fresh_weight - dry_weight)/dry_weight)* 100),
     	swc = fresh_weight_saturated - dry_weight,
     	rwc = fresh_weight/fresh_weight_saturated,
     	rwd = 100 - rwc
    	)

#put fixed CECO back into dataset:

pv_allcurves_data_fixed <- bind_rows(pv_allcurves_noceco, pv_ceco_2020_tlp_data)

#Need to also do something like this:
 # group_by("spp", "sample") %>%
 #  mutate(rwc_at_tlp_r = rwc from the row where tlp is equal to tlp_excel)

data.not.adfa <- pv_allcurves_data_fixed %>% #deal wirh some weird outliners in ADFA
   filter(spp != "ADFA")

data.adfa <- pv_allcurves_data_fixed %>%
  filter(lfm < 300, spp == "ADFA") #remove outlier ADFAs (not sure why this is how it is?)

pv_allcurves_data_clean  <- rbind(data.adfa, data.not.adfa)

pv_allcurves_data_clean <- pv_allcurves_data_clean %>%
  unite(individual, c("year", "month", "spp", "sample"), sep = '_', remove = FALSE) %>%
  write_csv(here("processed-data", "all_pv_curves_clean.csv"))
```

Visualize to make sure everything makes sense:

```{r, warning = F}
pv_allcurves_data_clean%>%
  filter(timing == "fall",
     	year != 2016) %>%
ggplot(aes(y = neg_mpa, x = rwd, color = spp)) +
  geom_jitter(alpha = .5, size = 1) +
  labs(title = "Pressure Volume Curves",
     	y = "-1/Mpa",
   	x = "Relative Water Deficit (%)") +
  #color_all +
  facet_wrap(~year)
```

Visualize LFM and Mpa ("Pressure Moisture Curves"):

```{r, warning = F}
pv_allcurves_data_clean %>%
  filter(timing == "fall",
     	year != 2016) %>%
  ggplot(aes(y = neg_mpa, x = lfm, color = spp)
  ) +
  geom_jitter(alpha = .5, size = 1) +
  labs(title = "Pressure Moisture Curves",
   	y = "-1/Mpa",
   	x = "Live Fuel Moisture (%)") +
  facet_wrap( ~ year, scales = "free") 
```

## Summaries
```{r}
pv_segs <- read_csv(here("raw-data",  "PV_sierra_summaries_fixed.csv")) %>%
  clean_names() %>%
  mutate(date = mdy(date),
     	year = year(date)) %>%
 # filter(timing == "fall", !year %in% c(2016, 2020)) %>%
  #drop_na(swc) %>%
  group_by(species, year
       	) %>%
  summarise(lfm_tlp = mean(lf_mtlp),
        	sd_lfm = sd(lf_mtlp),
        	tlp = mean(ytlp_m_pa),
        	sd_tlp = sd(ytlp_m_pa),
        	rwc_tlp = mean(rwctlp),
        	sd_rwc = sd(rwctlp),
        	po = mean(po_m_pa),
        	sd_po = sd(po_m_pa),
       	# swc = mean(swc),
       	# sd_swc = sd(swc),
        	e = mean(e_m_pa),
        	sd_e = sd(e_m_pa)
        	) %>%
  rename(spp = species)
pv_segs

datatable(pv_segs)
```

## Kable Table
Setup
```{r}
pv_segs_kable <- pv_segs %>% 
  mutate(spp = case_when(
    spp == "ABCO" ~ "Ab. concolor",
    spp == "CADE" ~ "Ca. decurrens",
    spp == "PIJE" ~ "Pi. jeffreyii",
    spp == "CECO" ~ "Ce. cordulatus",
    spp == "ARPA" ~ "Ar. patula",
    spp == "QUKE" ~ "Qu. kelloggii",
  )) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  mutate(lfm.kable = paste(lfm_tlp, "+/-", sd_lfm)) %>% 
  mutate(tlp.kable = paste(tlp, "+/-", sd_tlp)) %>% 
  mutate(rwc.kable = paste(rwc_tlp, "+/-", sd_rwc)) %>% 
  mutate(po.kable = paste(po, "+/-", sd_po)) %>% 
  mutate(e.kable = paste(e, "+/-", sd_e)) %>% 
  select(spp, year, lfm.kable, tlp.kable, rwc.kable, po.kable, e.kable)

pv_segs_kable$spp <- factor(pv_segs_kable$spp, levels = c("Ab. concolor", "Pi. jeffreyii", "Ca. decurrens", "Ar. patula", "Ce. cordulatus", "Qu. kelloggii"))
```

Kable
```{r}
pv_segs_kable %>% kable(format = 'html', escape = F, col.names = c('Species', 'Year', 'LFM', 'TLP', 'RWC',  paste('P', "\U2080"), 'e')) %>% 
  kable_styling(bootstrap_options = c('hover', 'bordered', 'condensed'), fixed_thead = T, font_size = 30) %>% 
  row_spec(c(1:2, 5:6, 9:10), background = '#EEEEEE') %>% 
  column_spec(1, italic = T) %>% 
  save_kable(here('figures', 'extra-figures', 'pv.curve.summary.html'))
```


#--------------------------
# 2. SWC and RWC

- Read in data

- Calculate SWC so we can get RWC

These were constructed via simultaneous measurements on LFM and Mpa during flammability testing.

```{r warning=FALSE, message=FALSE}
flam_curve_phys_czo <- readr::read_csv(here("raw-data", "czo.flam.curve.physiological.data.csv"),
                                   	show_col_types = FALSE) %>%
  clean_names() %>%
  mutate(location = "czo")

flam_curve_phys_seki <- readr::read_csv(here("raw-data", "seki.flam.curve.physiological.data.csv"),
                                    	show_col_types = FALSE) %>%
  clean_names() %>%
  mutate(location = "seki")

flam_curve_phys_all_notlp <- rbind(flam_curve_phys_czo, flam_curve_phys_seki) %>%
  mutate(lfm = lfm_n_as_imputed, water_potential = mpa) %>%
  mutate(pos_mpa = -1*water_potential) %>%
  mutate(month = case_when(
	year_month == "2020_September" ~ 9,
	year_month == "2020_January" ~ 1,
	year_month == "2020_October" ~ 10,
	year_month == "2016_December" ~ 12,
	year_month == "2019_December" ~ 9,
	year_month == "2028_January" ~ 1)) %>%
  mutate(timing = case_when(
 	year_month == "2020_September" ~ "fall",
	year_month == "2020_January" ~ "spring",
	year_month == "2020_October" ~ "fall",
	year_month == "2016_December" ~ "fall",
	year_month == "2019_December" ~ "fall",
	year_month == "2028_January" ~ "spring")) %>%
  select(individual, year_month, month, timing, dry_wt, spp, model, rwc, lfm, max_mpa_sample, mpa, gww_gdw, gww_gdw_saturated, fresh_wt, site, sample, location, pos_mpa, water_potential)

diagnostics <- dlookr::diagnose(flam_curve_phys_all_notlp)

diagnostics
```

```{r warning=FALSE, message=FALSE}
pv_spp_summary <- pv_segs  %>% 
  group_by(spp) %>% 
  summarise(lfm_tlp = mean(lfm_tlp), sd_lfm = mean(sd_lfm), tlp = mean(tlp), sd_tlp = mean(sd_tlp), rwc_tlp = mean(rwc_tlp), sd_rwc = mean(sd_rwc), po = mean(po), sd_po = mean(sd_po), e = mean(e), sd_e = mean(sd_e))


# merge the tlps from the PV curve summary into the flam curve dataset:
flam_curve_phys_all <- merge(flam_curve_phys_all_notlp, pv_spp_summary, by = "spp", all = T)
```

This is effectively what we're trying to do to get the saturated water content except we'll do it for each individual, not for each species.

```{r}
ggplot(flam_curve_phys_all, aes(x = pos_mpa,
                            	y = gww_gdw,
                            	color = spp)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, size = .5) +
  labs(title = "Intercept = saturated water content",
   	y = "water:dry matter",
   	x = "water potential (+Mpa)")
```

We need the extrapolated saturated water content so that we can determine the relative water content. We do that here by:
1. Finding a lm for each indvidual that relates **water content:dry matter** with **water potential**.
2. Extracting the y-intercept. This is the extrapolated saturated water content.
3. Add that value back into the dataset so it is useful.

```{r, warning= FALSE}
#get the extrapolated saturated water content:
swc_all <- flam_curve_phys_all %>%
  filter(mpa > tlp) %>% #for points above the tlp (estimated to be around ~2)
  group_by(individual) %>%
  summarise(swc_sat = lm(formula = gww_gdw ~ pos_mpa)$coefficients[["(Intercept)"]])

#add that back to the master dataset:
flam_curve_phys_all <- merge(flam_curve_phys_all, swc_all, by="individual", all = T) %>%
  mutate(rwc_new = 100 * (gww_gdw/swc_sat))
```

Make a smaller df to see what that looks like:

```{r, warning= FALSE}
subset <- flam_curve_phys_all %>%
 # select(individual, dry_wt, lfm, mpa,pos_mpa, gww_gdw, tlp, swc_sat, rwc_new, spp) %>%
  filter(rwc_new < 100)

unique(subset$individual)

rwc_at_tlp_mean <- pv_allcurves_data_clean %>%
  select(rwc_at_tlp) %>%
  drop_na() %>%
  mutate(rwc_at_tlp = mean(rwc_at_tlp)) %>%
  distinct() %>%
  pull()

subset %>%
  ggplot(aes(y = mpa,
         	x = rwc_new,
         	color = spp)) +
  geom_point(size = .5) +
 # geom_smooth(method = "lm", se = FALSE) +
  geom_smooth(method = loess, se = F, size = .5, color = "black") +
  ylim(-10, 0) +
  labs(y = "MPa",
   	x = "RWC",
   	title= "Estimated RWC and MPa: Drydown 'PV-Curves'"
     	) +
  geom_vline(xintercept = rwc_at_tlp_mean, linetype = "dotted")
```


```{r, warning= FALSE}
subset %>%
  ggplot(aes(y = -1/mpa,
         	x = 100 - rwc_new,
         	color = spp)) +
  geom_point(size = .5) +
  geom_smooth(method = loess, se = F, size = .5, color = "black") +
  geom_vline(xintercept = 100 - rwc_at_tlp_mean, linetype = "dotted") +
  labs(y = "-1/MPa",
   	x = "RWD",
   	title= "Estimated RWC and MPa: Drydown 'PV-Curves'",
   	caption = "dotted line is TLP"
     	) +
  facet_wrap(~spp, scales = "free")
```

```{r}
#for just 1 individual- looks kinda bad?
flam_curve_phys_all %>%
  filter(individual == "2020_September_CEME_1.3") %>%
  ggplot(aes(x = pos_mpa, y = gww_gdw, color = individual)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm")
```

New dataset with calculated RWC:

## Write .csv
```{r}
flam_curve_phys_all %>%
  write_csv(here("processed-data", "flam_curve_phys_all.csv"))
```

#--------------------------
# 3. Field Data

## 2021

Saturated content here is the wettest LFM observed during the field season/100. (indicated with _wettest)

```{r, message = FALSE}
field_data_2021_raw <- read.csv(here("raw-data", "CZO_alldata_compiled.csv")) %>%
  clean_names() %>%
  select(-spp_1) %>%
  mutate(lfm_tlp = lf_mtlp,
     	age = new_old) %>%
  select(-new_old) %>%
  mutate(age_new = case_when(
	age %in% c("O") & spp %in% c("QUKE") ~ "new",
	age %in% c("N") & spp %in% c("QUKE") ~ "new",
	age %in% c("old") & spp %in% c("QUKE") ~ "new",
	age %in% c("new") & spp %in% c("QUKE") ~ "new",
	age %in% c("O") ~ "old",
	age %in% c("N") ~ "new",
	TRUE ~ as.character(age))
  )

field_data_2021 <- field_data_2021_raw %>%
 # select(bottle_number:location) %>%
  mutate(date = mdy(date),
     	month = month(date),
     	month = month(date),
     	g_ww = wet_weight - bottle_weight,
     	g_dw = dry_weight - bottle_weight,
     	gww_gdw = g_ww/g_dw) %>%
  mutate(timing = case_when(
	month <= 7 ~ "spring",
	month > 7 ~ "fall" ))  %>%
  unite(unique_id, c("spp", "age", "site", "pod"), remove = FALSE) %>%
  group_by(unique_id) %>%
  dplyr::mutate(wettest_lfm = max((lfm))) %>%
  mutate(rwc_wettest = 100 * (lfm/wettest_lfm)) %>%
  mutate(rwd_wettest = 100 - rwc_wettest) %>%
  mutate(water_potential = midday) %>%
  mutate(swc = wettest_lfm/100)
```

## 2020

Saturated content here is the wettest LFM observed during the field season/100.

```{r, message = FALSE}
#LFM data:
field_data_2020_lfm_raw <- read_csv(here("raw-data", "LFM_Sierra_AllDates.csv"), show_col_types = FALSE) %>%
  clean_names()  %>%
  mutate(age_new = case_when(
	#age %in% c("O") & spp %in% c("QUKE", "CECO") ~ "new",
   # age %in% c("N") & spp %in% c("QUKE", "CECO") ~ "old",
   # age %in% c("old") & spp %in% c("QUKE", "CECO") ~ "new",
  #  age %in% c("new") & spp %in% c("QUKE", "CECO") ~ "old",
	age %in% c("O", "old", "Old") ~ "old",
	age %in% c("N", "new", "New") ~ "new",
	TRUE ~ as.character(age))
  )

field_data_2020_lfm <- field_data_2020_lfm_raw %>%
 # select(bottle_number:location) %>%
  mutate(date = mdy(date),
     	month = month(date),
     	g_ww = wet_with_bottle - bottle_weight,
     	g_dw = dry_with_bottle - bottle_weight,
     	gww_gdw = g_ww/g_dw) %>%
  mutate(timing = case_when(
	month <= 7 ~ "spring",
	month > 7 ~ "fall" ))  %>%
  unite(unique_id, c("spp", "age", "site", "pod"), remove = FALSE) %>%
  group_by(unique_id) %>%
  dplyr::mutate(wettest_lfm = max((lfm))) %>%
  mutate(rwc_wettest = 100 * (lfm/wettest_lfm)) %>%
  mutate(rwd_wettest = 100 - rwc_wettest) %>%
 # mutate(water_potential = midday) %>%
  mutate(swc_wettest = wettest_lfm/100)

field_data_2020_mpa_raw <- read_csv(here("raw-data", "field.summer.2020.csv"), show_col_types = FALSE)

field_data_2020_mpa  <- field_data_2020_mpa_raw  %>%
  clean_names() %>%
  select(spp:location) %>%
  unite(unique_id, c("spp","age", "site", "pod"), remove = FALSE) %>%
  mutate(date = mdy(date),
     	month = month(date),
     	mpa = midday)%>%
 select(-predawn1, -predawn2, -midday1, -midday2, -lfm)

field_data_2020 <- merge(field_data_2020_lfm, field_data_2020_mpa,
                    	# by = c("unique_id", "spp", "pod", "type", "site", "date", "location",
                           	# "month", "doy", "age"),
                     	all.y = T) %>%
  mutate(water_potential = mpa)

for (i in unique(field_data_2020$spp)) {
 
  df <- field_data_2020 %>%
	filter(spp == i)
 
  outlierKD(df, lfm)
}
```


## All dates
```{r}
field_data_all_nopv <- merge(field_data_2020, field_data_2021, all = T) %>%
  mutate(year = year(date))

field_data_all_pv <- merge(pv_spp_summary, field_data_all_nopv, by = "spp", all = T)

field_data_all <- field_data_all_pv %>%
   mutate(month = month(date),
      	year = year(date)) %>%
   mutate(age = case_when(
 	age == "New" ~ "new",
 	age == "Old" ~ "old",
 	age == "new" ~ "new",
 	age == "old" ~ "old",
 	age == "both" ~ "both",
 	TRUE ~ as.character(age)
   )) %>%
   mutate(spp = fct_relevel(spp, "ABCO","PIJE","CADE","CECO", "ARPA","QUKE"))  %>%
  mutate(strategy = case_when( #based on slope of predawn~midday line
	spp == "ABCO" ~ "Isohydric",
	spp == "PIJE" ~ "Isohydric",
 	spp == "CADE" ~ "Isohydric",
	spp == "CECO" ~ "Anisohydric",
	spp == "ARPA" ~ "Anisohydric",
	spp == "QUKE" ~ "Anisohydric"
  )) %>%
   mutate(strategy_binary = case_when( #based on slope of predawn~midday line
	spp == "ABCO" ~ "1",
	spp == "ARPA" ~ "2",
	spp == "CADE" ~ "1",
	spp == "CECO" ~ "2",
	spp == "PIJE" ~ "1",
	spp == "QUKE" ~ "2"
  )) %>%
   mutate(spp = fct_relevel(spp, "ABCO","PIJE","CADE","CECO", "ARPA","QUKE"))  %>%
   mutate(Species = case_when(
 	spp == "ABCO" ~ "A. concolor",
	spp == "PIJE" ~ "P. jeffreyi",
	spp == "CADE" ~ "C. decurrens",
	spp == "CECO" ~ "C. cordulatus",
	spp == "ARPA" ~ "A. patula",
	spp == "QUKE" ~ "Q. kelloggii"
	)) %>%
  mutate(type = case_when(
	spp == "PIJE" ~ "tree",
	spp == "QUKE" ~ "tree",
	spp == "CECO" ~ "shrub",
	spp == "ARPA" ~ "shrub",
	spp == "ABCO" ~ "tree",
	spp == "CADE" ~ "tree"
  )) %>%
  mutate(F.Group = case_when(
	spp == "ARPA" ~ "Angiosperm",
	spp == "ABCO" ~ "Gymnosperm",
	spp == "CADE" ~ "Gymnosperm",
	spp == "CECO" ~ "Angiosperm",
	spp == "PIJE" ~ "Gymnosperm",
	spp == "QUKE" ~ "Angiosperm"
  ))
```

We probably also want to get swc to be the extrapolated value, so....


This is effectively what we're trying to do to get the saturated water content except we'll do it for each individual, not for each species.

```{r}
ggplot(field_data_all_pv, aes(x = -1*water_potential,
                          	y = gww_gdw,
                          	color = spp)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, size = .5) +
 # color_all +
  labs(title = "Intercept = saturated water content",
   	y = "water:dry matter",
   	x = "water potential (+Mpa)") #+
 # theme(legend.position = "none")
#+
 # facet_wrap(~year)
```

We need the extrapolated saturated water content so that we can determine the relative water content. We do that here by:
1. Finding a lm for each indvidual that relates **water content:dry matter** with **water potential**.
2. Extracting the y-intercept. This is the extrapolated saturated water content.
3. Add that value back into the dataset so it is useful.

## Write .csv

```{r}
field_data_all %>%
  mutate(age = case_when(
	age_new %in% c("O", "both") ~ "old",
	age_new %in% c("N") ~ "new",
	TRUE ~ as.character(age_new)
  )) %>% 
  rename(lfm_tlp = lfm_tlp.x) %>% 
  select(-lfm_tlp.y) %>% 
write_csv(here("processed-data", "field_data_2020_2021.csv"))
```

#--------------------------

# 4. Stems vs. Leaves

```{r}
stems_leaves_2021 <- read_csv(here("raw-data", "CZO_October_StemsLeaves_2.csv")) %>%
  clean_names() %>%
  mutate(date = mdy(date),
     	month = month(date),
     	year = year(date),
     	age = new_old) %>%
  unite(unique_id, c("spp", "age", "site", "pod"), remove = FALSE)
 
stems_leaves_2021 %>%
write_csv(here("processed-data", "stems_leaves_2021.csv"))
```