---
title: "Mixed Effects Models - Field Data, Flammability, PV Curves"
author: "Indra Boving"
date: "11/8/2022"
output: html_document
---

Thid code is to visualize and investigate the relationships between water potential and lfm in PV curves, Flammability benchtop drydowns, and in field-collected data.

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#library(datapasta)
library(ggplot2)
library(purrr) #for visualizing all variables in one big plot
library(naniar) #for dealing with NAs nicely 
library(tidyverse)
library(ggpubr)
library(cowplot)
#library(GGally) #for corr plots
#require(kimisc) # has the nlist function to create a named list
#library(strengejacke)
library(sjPlot) # table functions
library(here)
#library(effects) #for plofhng model effects
#library(sjstats) #use for r2 functions
library("broom.mixed")
library(MuMIn)
library(modelsummary)
library(nlme)
library(lme4)
library(MetBrewer)
library(remef)
library(kableExtra)
library(janitor)
library(lubridate)
library(specr)
#library(cars)
#install.packages("specr")

filter = dplyr::filter
mutate = dplyr::mutate
select = dplyr::select
here = here::here

source(here::here("scripts", "scripts_functions", "figure_info_sierra_flammability.R")) #color and theme info is here
```

# 1. PV Curves

```{r,warning=FALSE}
pv_all_df <- read_csv(here("processed-data", "all_pv_curves_clean.csv"), show_col_types = FALSE) %>% 
  filter(!spp %in% c("ADFA", "CEME")) %>% 
  mutate(sample = as.factor(sample)) %>% 
  mutate(month = as.factor(month)) %>% 
  mutate(date = ymd(date)) %>% 
  unite(individual, c('spp','sample','date'), sep = '_', remove = F) %>% 
  mutate(year_month = str_c(year, '_', month), 
         year = as.factor(year)) %>% 
  clean_names() %>% 
  group_by(spp) %>% 
  mutate(plant = udpipe::unique_identifier(individual), 
         plant = as.factor(plant),
         fresh_weight_saturated = as.numeric(fresh_weight_saturated)) %>% 
  group_by(spp, plant) %>% 
  mutate(maxLFM = ((fresh_weight_saturated - dry_weight)/dry_weight)*100) %>% 
   mutate(spp = fct_relevel(spp, "ABCO","PIJE","CADE","CECO", "ARPA","QUKE")) %>% 
  mutate(strategy = case_when( #based on slope of predawn~midday line
    spp == "ABCO" ~ "Isohydric", 
    spp == "PIJE" ~ "Isohydric", 
     spp == "CADE" ~ "Isohydric", 
    spp == "CECO" ~ "Anisohydric", 
    spp == "ARPA" ~ "Anisohydric", 
    spp == "QUKE" ~ "Anisohydric"
  )) %>% 
   mutate(strategy_binary = case_when( #based on slope of predawn~midday line
    spp == "ABCO" ~ "1", 
    spp == "ARPA" ~ "2", 
    spp == "CADE" ~ "1", 
    spp == "CECO" ~ "2", 
    spp == "PIJE" ~ "1", 
    spp == "QUKE" ~ "2"
  )) %>% 
   mutate(Species = case_when(
     spp == "ABCO" ~ "A. concolor",
    spp == "PIJE" ~ "P. jeffreyi", 
    spp == "CADE" ~ "C. decurrens", 
    spp == "CECO" ~ "C. cordulatus", 
    spp == "ARPA" ~ "A. patula", 
    spp == "QUKE" ~ "Q. kelloggii"
    )) %>% 
  mutate(type = case_when(
    spp == "PIJE" ~ "tree", 
    spp == "QUKE" ~ "tree", 
    spp == "CECO" ~ "shrub", 
    spp == "ARPA" ~ "shrub", 
    spp == "ABCO" ~ "tree", 
    spp == "CADE" ~ "tree"
  )) %>% 
  mutate(F.Group = case_when(
    spp == "ARPA" ~ "Angiosperm", 
    spp == "ABCO" ~ "Gymnosperm",
    spp == "CADE" ~ "Gymnosperm",
    spp == "CECO" ~ "Angiosperm",
    spp == "PIJE" ~ "Gymnosperm",
    spp == "QUKE" ~ "Angiosperm"
  )) %>% 
  filter(timing == "fall")%>% 
  mutate(ilfm = 1/lfm) %>% 
  filter(individual != 'QUKE_2_2020-10-21',
         individual !='QUKE_4_2020-10-21')

# model criticism plots
qqnorm(pv_all_df$lfm) #normally distributed
qqline(pv_all_df$lfm)

qqnorm(pv_all_df$ilfm)
qqline(pv_all_df$ilfm) #NOT normally distributed

write_csv(pv_all_df, (here("processed-data", "var-decomp", "all_pv_curves_clean_vardecomp.csv")))
```

## Summaries
```{r}
pv_summaries_2 <- read_csv(here("raw-data", "PV_sierra_summaries.csv")) %>% 
  clean_names() %>% 
   mutate(spp = fct_relevel(species, "ABCO","PIJE","CADE","CECO", "ARPA","QUKE"), 
          tlp = ytlp_m_pa, 
          lfmtlp = lf_mtlp)  %>% 
  mutate(strategy = case_when( #based on slope of predawn~midday line
    spp == "ABCO" ~ "Isohydric", 
    spp == "PIJE" ~ "Isohydric", 
     spp == "CADE" ~ "Isohydric", 
    spp == "CECO" ~ "Anisohydric", 
    spp == "ARPA" ~ "Anisohydric", 
    spp == "QUKE" ~ "Anisohydric"
  )) %>% 
   mutate(strategy_binary = case_when( #based on slope of predawn~midday line
    spp == "ABCO" ~ "1", 
    spp == "ARPA" ~ "2", 
    spp == "CADE" ~ "1", 
    spp == "CECO" ~ "2", 
    spp == "PIJE" ~ "1", 
    spp == "QUKE" ~ "2"
  )) %>% 
   mutate(spp = fct_relevel(spp, "ABCO","PIJE","CADE","CECO", "ARPA","QUKE"))  %>% 
   mutate(Species = case_when(
     spp == "ABCO" ~ "A. concolor",
    spp == "PIJE" ~ "P. jeffreyi", 
    spp == "CADE" ~ "C. decurrens", 
    spp == "CECO" ~ "C. cordulatus", 
    spp == "ARPA" ~ "A. patula", 
    spp == "QUKE" ~ "Q. kelloggii"
    )) %>% 
  mutate(type = case_when(
    spp == "PIJE" ~ "tree", 
    spp == "QUKE" ~ "tree", 
    spp == "CECO" ~ "shrub", 
    spp == "ARPA" ~ "shrub", 
    spp == "ABCO" ~ "tree", 
    spp == "CADE" ~ "tree"
  )) %>% 
  mutate(F.Group = case_when(
    spp == "ARPA" ~ "Angiosperm", 
    spp == "ABCO" ~ "Gymnosperm",
    spp == "CADE" ~ "Gymnosperm",
    spp == "CECO" ~ "Angiosperm",
    spp == "PIJE" ~ "Gymnosperm",
    spp == "QUKE" ~ "Angiosperm"
  )) %>% 
  mutate(date = lubridate::mdy(date), 
         year = year(date))

fgroup_pv_summaries <- pv_summaries_2 %>% 
  group_by(F.Group) %>% 
  mutate(mean_tlp_group = mean(tlp))
```
## Plot

```{r}
dat_text <- data.frame(
  F.Group = c("Angiosperm", "Gymnosperm"),
  label   = c(NA, "b")
)

pv_plot <- pv_all_df %>%
  filter(!spp %in% c("ADFA", "CEME")) %>%
  ggplot(aes(
    x = -1 * water_potential,
    y = lfm,
    color = spp,
   # shape = as.factor(year)
  )) +
  geom_vline(aes(xintercept = -1*mean_tlp_group, 
                 lty = F.Group), data = fgroup_pv_summaries) +
  geom_point(alpha = .5, 
              aes(shape = as.factor(year))
             ) +
  color_many2 +
  theme(legend.position = "none",
        axis.title.x = element_text("")) +
  labs(title = "PV Curves",
       x = "",
       y = "LFM") +
  xlim(0, 10) +
  # annotate(
  #   geom = "text",
  #   x = 9,
  #   y = 232,
  #   label = 'b',
  #   fontface = 'bold',
  #   size = 10
  # ) +  
  geom_text(
  data    = dat_text,
  color = "black",
  fontface = 'bold', size = 10,
  mapping = aes(x = 9, y = 232, label = label))+
  facet_wrap(~F.Group)+
  theme(plot.margin = unit(c(.2, .5,-.5, .25), "cm")) #margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
  
pv_plot
```

F.test: 
Allowa us to compare the variance between two groups, in this case angiosperms and gymnosperms:
```{r}
res.ftest <- var.test(lfm ~ F.Group, data = pv_all_df)
res.ftest
#There is a significant difference between the variaance 
```

Var decomp: 
https://cran.r-project.org/web/packages/specr/vignettes/decompose_var.html 
```{r}
pv_mod <- lmer(lfm~(1|water_potential) + (1|F.Group) + (1|plant), data = pv_all_df)
summary(pv_mod)
anova(pv_mod)

specr::icc_specs(pv_mod) %>%
  mutate_if(is.numeric, round, 2)
```


## Plot (-MPa)
```{r}
dat_text <- data.frame(
  F.Group = c("Angiosperm", "Gymnosperm"),
  label   = c(NA, "b")
)

pv_plot_neg <- pv_all_df %>%
  filter(!spp %in% c("ADFA", "CEME")) %>%
  ggplot(aes(
    x = -1/water_potential,
    y = lfm,
    color = spp
  )) +
  geom_vline(aes(xintercept = -1/mean_tlp_group, 
                 lty = F.Group), data = fgroup_pv_summaries) +
  geom_point(alpha = .5) +
  color_many2 +
  theme(legend.position = "none",
        axis.title.x = element_text("")) +
  labs(title = "PV Curves",
       x = "",
       y = "LFM") +
  xlim(0, 15) +
  # annotate(
  #   geom = "text",
  #   x = 9,
  #   y = 232,
  #   label = 'b',
  #   fontface = 'bold',
  #   size = 10
  # ) +  
  geom_text(
  data    = dat_text,
  color = "black",
  fontface = 'bold', size = 10,
  mapping = aes(x = 14, y = 232, label = label))+
  facet_wrap(~F.Group)+
  theme(plot.margin = unit(c(.2, .5,-.5, .25), "cm")) #margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
  
pv_plot_neg
```

## MEM
```{r}
m10.5 <- lmer(lfm~ water_potential*F.Group + (1|plant), data = pv_all_df)
summary(m10.5)
AIC(m10.5)

m10 <- lmer(lfm~ water_potential + F.Group + (1|plant), data = pv_all_df)
summary(m10)
AIC(m10)

anova(m10, m10.5) #don't need interaction

m10.75 <- lmer(lfm~ water_potential + F.Group + as.factor(year) + (1|plant), data = pv_all_df)
summary(m10.75) #yes add year

anova(m10, m10.75)

m10.757 <- lmer(lfm~ water_potential*as.factor(year) + F.Group + (1|plant), data = pv_all_df)
summary(m10.757)

anova(m10.75, m10.757) # dont need year interaction

qqnorm(resid(m10.75))
r <- resid(m10.75)
plot(fitted(m10.75), r)

anova(m10.75)
car::Anova(m10.75)

specr::icc_specs(m10.75) %>%
  mutate_if(is.numeric, round, 2)
```

# 2. Flam. Drydown

```{r, warning=FALSE}
flam_curve_phys_all_raw <- read_csv(here("processed-data", "sierra_flam_data_all.csv"), show_col_types = FALSE)

flam_curve_df <- flam_curve_phys_all_raw %>% 
   filter(!spp %in% c("ADFA", "CEME")) %>% 
  mutate(water_potential = -1*pos_mpa, 
         swc = swc_sat, 
         month = as.factor(month)) %>% 
  group_by(spp) %>% 
  mutate(plant = udpipe::unique_identifier(individual), 
         maxLFM = gww_gdw_saturated * 100) %>% 
  mutate(spp = toupper(spp)) %>% 
  mutate(strategy = case_when( #based on slope of predawn~midday line
    spp == "ABCO" ~ "Isohydric", 
    spp == "PIJE" ~ "Isohydric", 
     spp == "CADE" ~ "Isohydric", 
    spp == "CECO" ~ "Anisohydric", 
    spp == "ARPA" ~ "Anisohydric", 
    spp == "QUKE" ~ "Anisohydric"
  )) %>% 
   mutate(strategy_binary = case_when( #based on slope of predawn~midday line
    spp == "ABCO" ~ "1", 
    spp == "ARPA" ~ "2", 
    spp == "CADE" ~ "1", 
    spp == "CECO" ~ "2", 
    spp == "PIJE" ~ "1", 
    spp == "QUKE" ~ "2"
  )) %>% 
   mutate(Species = case_when(
     spp == "ABCO" ~ "A. concolor",
    spp == "PIJE" ~ "P. jeffreyi", 
    spp == "CADE" ~ "C. decurrens", 
    spp == "CECO" ~ "C. cordulatus", 
    spp == "ARPA" ~ "A. patula", 
    spp == "QUKE" ~ "Q. kelloggii"
    )) %>% 
  mutate(type = case_when(
    spp == "PIJE" ~ "tree", 
    spp == "QUKE" ~ "tree", 
    spp == "CECO" ~ "shrub", 
    spp == "ARPA" ~ "shrub", 
    spp == "ABCO" ~ "tree", 
    spp == "CADE" ~ "tree"
  )) %>% 
  mutate(F.Group = case_when(
    spp == "ARPA" ~ "Angiosperm", 
    spp == "ABCO" ~ "Gymnosperm",
    spp == "CADE" ~ "Gymnosperm",
    spp == "CECO" ~ "Angiosperm",
    spp == "PIJE" ~ "Gymnosperm",
    spp == "QUKE" ~ "Angiosperm"
  )) %>% 
  select(lfm, water_potential, mpa, year, month, year_month, plant, F.Group, spp) %>% 
  mutate(ilfm = 1/lfm)

# model criticism plots
qqnorm(flam_curve_df$lfm) #normally distributed
qqline(flam_curve_df$lfm)

qqnorm(flam_curve_df$ilfm)
qqline(flam_curve_df$ilfm) #NOT normally distributed

write_csv(flam_curve_df, here("processed-data", "var-decomp", "flam_curve_vardecomp.csv"))
```


## Plot
```{r}
dat_text <- data.frame(
  F.Group = c("Angiosperm", "Gymnosperm"),
  label   = c(NA, "c")
)

flam_plot <- flam_curve_df %>% 
  filter(lfm < 300, 
         lfm > 50) %>% 
  filter(!spp %in% c("ADFA", "CEME")) %>% 
  ggplot(aes(y = lfm, 
             x = -1*water_potential, 
             color = spp)) +
  geom_vline(aes(xintercept = -1*mean_tlp_group, 
                 lty = F.Group), data = fgroup_pv_summaries) +
  geom_point(alpha = .5, 
             aes( shape = as.factor(year))
             ) +
 # geom_smooth(method = "lm", se = F) +
  color_many2 +
  theme(legend.position = "none")+
  labs(title = "Flam", 
       x = "Water Potential", 
       y = "LFM")+
  theme(plot.margin = unit(c(.2, .5, .3, .25), "cm")) +
 # xlim(0, 9) + 
  geom_text(
  data    = dat_text,
  color = "black",
  fontface = 'bold', size = 10,
  mapping = aes(x = 9, y = 210, label = label))+
 # annotate(geom = "text", x = 9, y = 225, label = 'c', fontface = 'bold', size = 10)+
  facet_wrap(~F.Group)
flam_plot
```

## Plot (-MPa)
```{r}
dat_text <- data.frame(
  F.Group = c("Angiosperm", "Gymnosperm"),
  label   = c(NA, "c")
)

flam_plot_neg <- flam_curve_df %>% 
  filter(lfm < 300, 
         lfm > 50) %>% 
  filter(!spp %in% c("ADFA", "CEME")) %>% 
  ggplot(aes(y = lfm, 
             x = -1/water_potential, 
             color = spp)) +
  geom_vline(aes(xintercept = -1/mean_tlp_group, 
                 lty = F.Group), data = fgroup_pv_summaries) +
  geom_point(alpha = .5) +
 # geom_smooth(method = "lm", se = F) +
  color_many +
  theme(legend.position = "none")+
  labs(title = "Flam", 
       x = "Water Potential", 
       y = "LFM")+
  theme(plot.margin = unit(c(.2, .5, .3, .25), "cm")) +
  xlim(0, 15) + 
  geom_text(
  data    = dat_text,
  color = "black",
  fontface = 'bold', size = 10,
  mapping = aes(x = 14, y = 210, label = label))+
 # annotate(geom = "text", x = 9, y = 225, label = 'c', fontface = 'bold', size = 10)+
  facet_wrap(~F.Group)
flam_plot_neg
```

## MEM
```{r}
m11.5 <- lmer(lfm~ water_potential + F.Group + (1|plant), data = flam_curve_df)
summary(m11.5)

m11 <- lmer(lfm~ water_potential*F.Group + (1|plant), data = flam_curve_df)

anova(m11, m11.5) #Yes interaction between mpa and f group

m11.75  <- lmer(lfm~ water_potential*F.Group + as.factor(year) + (1|plant), data = flam_curve_df)
m11.75 #there shouldn't be an interaction between year and f group, so dont include
summary(m11.75)

anova(m11, m11.75) 

qqnorm(resid(m11.75))
r <- resid(m11.75)
plot(fitted(m11.75), r)

anova(m11.75)
car::Anova(m11.75)

performance::multicollinearity(m11.75)

specr::icc_specs(m11) %>%
  mutate_if(is.numeric, round, 2)
```


# 3. Field Data
```{r}
field_data_all <- read_csv(here("processed-data", "field_data_2020_2021.csv"), show_col_types = FALSE) %>% 
    filter(lfm < 300, 
         lfm > 50, 
        # age == "new"
         ) %>% 
 # select(-mpa, -water_potential) %>% 
  mutate(water_potential = midday, 
         unique_id2 = str_c(spp, "_",pod, '_', site),
         plant = udpipe::unique_identifier(unique_id2)) %>% 
  mutate(year_month = str_c(year, '_', month)) %>% 
 # group_by(spp, plant) %>% 
  mutate(maxLFM = wettest_lfm)  %>% 
  mutate(strategy = case_when( #based on slope of predawn~midday line
    spp == "ABCO" ~ "Isohydric", 
    spp == "PIJE" ~ "Isohydric", 
     spp == "CADE" ~ "Isohydric", 
    spp == "CECO" ~ "Anisohydric", 
    spp == "ARPA" ~ "Anisohydric", 
    spp == "QUKE" ~ "Anisohydric"
  )) %>% 
   mutate(strategy_binary = case_when( #based on slope of predawn~midday line
    spp == "ABCO" ~ "1", 
    spp == "ARPA" ~ "2", 
    spp == "CADE" ~ "1", 
    spp == "CECO" ~ "2", 
    spp == "PIJE" ~ "1", 
    spp == "QUKE" ~ "2"
  )) %>% 
   mutate(Species = case_when(
     spp == "ABCO" ~ "A. concolor",
    spp == "PIJE" ~ "P. jeffreyi", 
    spp == "CADE" ~ "C. decurrens", 
    spp == "CECO" ~ "C. cordulatus", 
    spp == "ARPA" ~ "A. patula", 
    spp == "QUKE" ~ "Q. kelloggii"
    )) %>% 
  mutate(type = case_when(
    spp == "PIJE" ~ "tree", 
    spp == "QUKE" ~ "tree", 
    spp == "CECO" ~ "shrub", 
    spp == "ARPA" ~ "shrub", 
    spp == "ABCO" ~ "tree", 
    spp == "CADE" ~ "tree"
  )) %>% 
  mutate(F.Group = case_when(
    spp == "ARPA" ~ "Angiosperm", 
    spp == "ABCO" ~ "Gymnosperm",
    spp == "CADE" ~ "Gymnosperm",
    spp == "CECO" ~ "Angiosperm",
    spp == "PIJE" ~ "Gymnosperm",
    spp == "QUKE" ~ "Angiosperm"
  )) %>% 
  mutate(ilfm = 1/lfm) 

field_data_all_2 <- field_data_all %>% 
  drop_na(lfm, water_potential, plant, F.Group, year)

write_csv(field_data_all, (here("processed-data", "var-decomp", "field_data_vardecomp.csv")))

# model criticism plots
qqnorm(field_data_all$lfm)
qqline(field_data_all$lfm) #NOT Normal

qqnorm(field_data_all$ilfm)
qqline(field_data_all$ilfm) #Normal-ish
```
## Plot
```{r}
dat_text <- data.frame(
  F.Group = c("Angiosperm", "Gymnosperm"),
  label   = c(NA, "a")
)

field_plot <- field_data_all %>% 
  filter(lfm < 300, 
         lfm > 50) %>% 
  ggplot(aes(y = lfm, 
             x = -1*water_potential, 
             color = spp)) +
  geom_vline(aes(xintercept = -1*mean_tlp_group, 
                 lty = F.Group), data = fgroup_pv_summaries) +
  geom_point(alpha = .5, 
             aes(shape = as.factor(year))
             )+
  facet_wrap(~F.Group) +
 # geom_smooth(method = 'nls', formula = 'y~x*exp(1)') + 
  geom_smooth(method = "loess", se = F) +
  color_many2 +
  theme(legend.position = "none") +
  labs(title = "Field", 
       x = "", 
       y = "LFM") +
  theme(plot.margin = unit(c(.2, .5, -.5, .25), "cm")) +
  xlim(0, 10) +
  geom_text(
  data    = dat_text,
  color = "black",
  fontface = 'bold', size = 10,
  mapping = aes(x = 9, 
                y = 300, 
                #y = 2,
                label = label)
 )
  #annotate(geom = "text", x = 9, y = 300, label = 'a', fontface = 'bold', size = 10) 
field_plot
```
## ****Plot inverse LFM (1/lfm) (IN SI)
```{r}
field_plot_ilfm<- field_data_all %>% 
  filter(lfm < 300, 
         lfm > 50) %>% 
  ggplot(aes(y = 1/lfm, 
             x = water_potential, 
             color = spp)) +
  geom_point(alpha = .3, 
             #aes(shape = as.factor(year) )
             )+
  facet_wrap(~F.Group, scales = "free") +
  geom_smooth(method = "lm", se = F) +
  color_many +
  theme(legend.position = "none") +
  labs(title = "Field", 
       x = "Water Potential", 
       y = "1/LFM") +
  theme(plot.margin = unit(c(.2, .5, .5, .25), "cm")) 
field_plot_ilfm
```
## Plot (log-LFM)
```{r}
field_plot_logged<- field_data_all %>% 
  filter(lfm < 300, 
         lfm > 50) %>% 
  ggplot(aes(y = log(lfm), 
             x = -1*water_potential, 
             color = spp)) +
  geom_vline(aes(xintercept = -1*mean_tlp_group, 
                 lty = F.Group), data = fgroup_pv_summaries) +
  geom_point(alpha = .5, 
             aes(shape = as.factor(year))
             )+
  facet_wrap(~F.Group) +
 # geom_smooth(method = "lm", se = F) +
  color_many +
  theme(legend.position = "none") +
  labs(title = "Field", 
       x = "", 
       y = "LFM") +
  theme(plot.margin = unit(c(.2, .5, -.5, .25), "cm")) +
  xlim(0, 10) +
  geom_text(
  data    = dat_text,
  color = "black",
  fontface = 'bold', size = 10,
  mapping = aes(x = 9, 
               # y = 300, 
                y = 2,
                label = label)
 )
  #annotate(geom = "text", x = 9, y = 300, label = 'a', fontface = 'bold', size = 10) 
field_plot_logged
```

## Plot (-MPa)
```{r}
dat_text <- data.frame(
  F.Group = c("Angiosperm", "Gymnosperm"),
  label   = c(NA, "a")
)

field_plot_neg <- field_data_all %>% 
  filter(lfm < 300, 
         lfm > 50) %>% 
  ggplot(aes(y = lfm, 
             x = -1/water_potential, 
             color = spp)) +
  geom_vline(aes(xintercept = -1/mean_tlp_group, 
                 lty = F.Group), data = fgroup_pv_summaries) +
  geom_point(alpha = .5)+
  facet_wrap(~F.Group) +
 # geom_smooth(method = "lm", se = F) +
  color_many +
  theme(legend.position = "none") +
  labs(title = "Field", 
       x = "", 
       y = "LFM") +
  theme(plot.margin = unit(c(.2, .5, -.5, .25), "cm")) +
  xlim(0, 2) +
  geom_text(
  data    = dat_text,
  color = "black",
  fontface = 'bold', size = 10,
  mapping = aes(x = 1.7, y = 300, label = label))
  #annotate(geom = "text", x = 9, y = 300, label = 'a', fontface = 'bold', size = 10) 
field_plot_neg
```


We should visualize in LFM~MPa space for the sake of comparing to benchtop curves, but transforming to 1/LFM is actually normally distributed (could show this in SI?).


## MEM
```{r}
m12.5 <- lm(ilfm~ water_potential*F.Group + as.factor(year), data = field_data_all)
summary(m12.5)
plot(m12.5, which = 1) 
plot(m12.5, which = 2)
plot(m12.5, which = 5)


m12.5a <- lm(ilfm~ water_potential*F.Group*age + as.factor(year), data = field_data_all)
summary(m12.5a)
plot(m12.5a, which = 1) 
plot(m12.5a, which = 2)
plot(m12.5a, which = 5)

m12.5ab <- lm(ilfm~ water_potential*F.Group + age + as.factor(year), data = field_data_all)
summary(m12.5ab)  

AIC(m12.5, m12.5a,m12.5ab) #
```


```{r}
lmer12 <- lmer(lfm~ water_potential*F.Group + as.factor(year)+ (1|plant), data = field_data_all)
summary(lmer12)
plot(lmer12, which = 1) 
qqnorm(residuals(lmer12)) 
qqline(residuals(lmer12))

#checking model random effects: 
modrandomeffects <- ranef(lmer12)
qqnorm(modrandomeffects$plant$`(Intercept)`)
qqline(modrandomeffects$plant$`(Intercept)`)
library(car)
qqp(modrandomeffects$plant$`(Intercept)`)
modrandomeffects$plant

lmer12.5 <- lmer(ilfm~ water_potential*F.Group + as.factor(year)+ (1|plant), data = field_data_all)
summary(lmer12.5)
plot(lmer12.5, which = 1) 
qqnorm(residuals(lmer12.5)) 
qqline(residuals(lmer12.5))


summary(m12.5)

#Transformed model: 
#y = a/(b+x)
#nonlin12.4 <- nls(lfm~)
```

####Just Angiosperms: 

```{r}
angios_field_data <- field_data_all %>% 
  filter(F.Group == "Angiosperm")

hist(angios_field_data$lfm)
hist(angios_field_data$ilfm)

m12.5a <- lm(ilfm~ water_potential, data = angios_field_data )
summary(m12.5a)
plot(m12.5a, which = 1) 
plot(m12.5a, which = 2)
plot(m12.5a, which = 5)

lmer12a <- lmer(lfm~ water_potential + as.factor(year)+ (1|plant), data = angios_field_data )
summary(lmer12a)
plot(lmer12a, which = 1) 
qqnorm(residuals(lmer12a)) 
qqline(residuals(lmer12a))


lmer12.5a <- lmer(ilfm~ water_potential + as.factor(year)+ (1|plant), data = angios_field_data )
summary(lmer12.5a)
plot(lmer12.5a, which = 1) 
qqnorm(residuals(lmer12.5a)) 
qqline(residuals(lmer12.5a))
```

####Just Gymnosperms: 

```{r}
gymnos_field_data <- field_data_all %>% 
  filter(F.Group == "Gymnosperm")

hist(gymnos_field_data$lfm)
hist(gymnos_field_data$ilfm)

m12.5g <- lm(ilfm~ water_potential, data = gymnos_field_data )
summary(m12.5g)
plot(m12.5g, which = 1) 
plot(m12.5g, which = 2)
plot(m12.5g, which = 5)

lmer12g <- lmer(lfm~ water_potential + as.factor(year)+ (1|plant), data = angios_field_data )
summary(lmer12g)
plot(lmer12g, which = 1) 
qqnorm(residuals(lmer12g)) 
qqline(residuals(lmer12g))

lmer12g <- lmer(log(lfm)~ log(water_potential*-1) + as.factor(year)+ (1|plant), data = angios_field_data )
summary(lmer12g)
plot(lmer12g, which = 1) 
qqnorm(residuals(lmer12g)) 
qqline(residuals(lmer12g))


lmer12.5g <- lmer(ilfm~ water_potential + as.factor(year)+ (1|plant), data = angios_field_data )
summary(lmer12.5g)
plot(lmer12.5g, which = 1) 
qqnorm(residuals(lmer12.5g)) 
qqline(residuals(lmer12.5g))
```
# 4. Arranging/Combining

## Scatterplots
```{r, fig.height=6, fig.width=5}
field_plot_leg <- field_data_all %>% 
  filter(lfm < 300, 
         lfm > 50) %>% 
  ggplot(aes(y = lfm, 
             x = -1*water_potential, 
             color = spp)) +
  geom_vline(aes(xintercept = -1*mean_tlp_group, 
                 lty = F.Group), data = fgroup_pv_summaries) +
  geom_point(alpha = .5, 
             aes(shape = as.factor(year))) +
  labs(color = "Species", 
       lty = "TLP", 
       shape = "Year") +
 # geom_smooth(method = "lm", se = F) +
  color_many 
legend <- cowplot::get_legend(field_plot_leg)

#Mpas:
plots <- cowplot::plot_grid(field_plot, pv_plot, flam_plot,
          ncol = 1, 
         nrow = 3
          )
plots_legend <- cowplot::plot_grid(plots, legend, rel_widths = c(5, 1), rel_heights = c(-.1, -0.1, -.1))
plots_legend

ggsave(plot=plots_legend, bg = "white" , here("figures", 'extra-figures', "flam_pv_field"), device="jpg")
```

## -MPa Plots
```{r, fig.height=6, fig.width=5}
#Mpas:
plots_neg <- cowplot::plot_grid(field_plot_neg, pv_plot_neg, flam_plot_neg,
          ncol = 1, 
         nrow = 3
          )
plots_legend_neg <- cowplot::plot_grid(plots_neg, legend, rel_widths = c(5, 1), rel_heights = c(-.1, -0.1, -.1))
plots_legend_neg

ggsave(plot=plots_legend, bg = "white" , here::here("figures", "extra-figures", "flam_pv_field_neg"), device="jpg")
```

## MEM
```{r}
tab_model <- sjPlot::tab_model(m10.75, m11.75, m12.4,
                               show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
         string.pred = "Coeffcient", 
        dv.labels = c("PV", "Flam", "Field"),
         title = "LFM ~ MPa",
  string.p = "P-Value", 
  p.style = "stars")
tab_model
```

#5. For Pepperwood/to share

```{r}
pepperwood_df <- field_data_all_2 %>%
  select(spp, Species, unique_id, age_new, date, year, location, lfm, water_potential, location) %>%
   filter(lfm < 300,
         lfm > 50) %>%
  rename(tissue_age = age_new) %>%
  mutate(ilfm = 1/(lfm-100)) %>%
  filter(ilfm < 3,
         ilfm > 0)

pepperwood_df %>%
  ggplot(aes(y = lfm,
             x = water_potential,
             color = as.factor(year),
             shape = tissue_age)) +
  geom_point() +
  facet_wrap(~Species)

pepperwood_df %>%
  mutate(month = month(date)) %>%
  filter(!(spp %in% c("PIJE", "ABCO", "ARPA") & tissue_age == "new")) %>%
  ggplot(aes(y = ilfm,
             x = water_potential,
             color = as.factor(Species)
            # shape = as.factor(month))
         )) +
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  facet_wrap(~Species, scales = "free")

pepperwood_df %>%
  mutate(month = month(date)) %>%
 # filter(tissue_age == "new") %>%
  ggplot(aes(y = ilfm,
             x = water_potential,
             color = as.factor(month),
            # shape = tissue_age
            # shape = as.factor(month))
         )) +
  geom_point(aes(shape = tissue_age)) +
  geom_smooth(method = "lm", se = F)

pepperwood_df %>%
  mutate(month = month(date)) %>%
 # filter(tissue_age == "new") %>%
  ggplot(aes(y = lfm,
             x = water_potential,
             color = as.factor(month),
            # shape = tissue_age
            # shape = as.factor(month))
         )) +
  geom_point(aes(shape = tissue_age)) +
  geom_smooth(method = "lm", se = F)



pepperwood_df %>%
  mutate(month = month(date)) %>%
  filter(tissue_age == "old",
         year == 2021) %>%
  ggplot(aes(y = ilfm,
             x = water_potential,
             color = as.factor(month),
            # shape = tissue_age
            # shape = as.factor(month))
         )) +
  geom_point(aes(shape = tissue_age)) +
  geom_smooth(method = "lm", se = F)

pepperwood_df %>%
  mutate(month = month(date)) %>%
  filter(tissue_age == "old",
         year == 2021) %>%
  ggplot(aes(y = lfm,
             x = water_potential,
             color = as.factor(month),
            # shape = tissue_age
            # shape = as.factor(month))
         )) +
  geom_point(aes(shape = tissue_age)) +
  geom_smooth(method = "lm", se = F)

write.csv(pepperwood_df, here('processed-data', 'sierra_lfm_mpa.csv'))
```