---
title: "Variance Decomposition - LFM vs. MPa"
author: "Indra Boving"
date: "11/8/2022"
output: html_document
---
# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(datapasta)
library(ggplot2)
library(purrr) #for visualizing all variables in one big plot
library(naniar) #for dealing with NAs nicely 
library(tidyverse)
library(ggpubr)
library(cowplot)
library(GGally) #for corr plots
require(kimisc) # has the nlist function to create a named list
#library(strengejacke)
library(sjPlot) # table functions
library(here)
library(effects) #for plofhng model effects
library(sjstats) #use for r2 functions
library("broom.mixed")
library(MuMIn)
library(modelsummary)
library(nlme)
library(lme4)
library(MetBrewer)
library(remef)
library(kableExtra)
library(janitor)
library(lubridate)
library(specr)
library(gridExtra)
library(grid)
library(patchwork)

filter = dplyr::filter
mutate = dplyr::mutate
select = dplyr::select
here = here::here

# if (!require("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# 
# BiocManager::install("variancePartition")
library('variancePartition')

source(here::here("scripts", "scripts_functions", "figure_info_sierra_flammability.R")) #color and theme info is here

source(here::here("scripts", "scripts_functions", "plotPercentBars_IB.R"))
```

# Data

Scatterplots:
```{r,warning=FALSE, message=TRUE}
pv_all_df <- read_csv(here("processed-data", "var-decomp", "all_pv_curves_clean_vardecomp.csv"))

fgroup_pv_summaries <- read_csv(here("processed-data", "var-decomp", "fgroup_pv_summaries.csv"))

flam_curve_phys_all_raw <- read_csv(here("processed-data", "var-decomp", "flam_curve_vardecomp.csv"))

field_data_all <- read_csv(here("processed-data", "var-decomp", "field_data_vardecomp.csv")) %>% 
    filter(lfm < 300, 
         lfm > 50, 
        # age == "new"
         ) %>% 
  mutate(Species = case_when(
    spp == "ARPA" ~ "Ar. patula", 
    spp == "ABCO" ~ "Ab. concolor",
    spp == "CADE" ~ "Ca. decurrens",
    spp == "CECO" ~ "Ce. cordulatus",
    spp == "PIJE" ~ "Pi. jeffreyi",
    spp == "QUKE" ~ "Qu. kelloggii"
  )) 
```

Removing outliers from PV Curve Data (for Angiosperms, Fig. 4c)
```{r}
pv_all_df <- pv_all_df %>% 
  filter(individual != 'QUKE_2_2020-10-21',
         individual !='QUKE_4_2020-10-21')
```


Vardecomps:
```{r, fig.height=3, fig.width=1}
flam_curve_df_2.1 <- read_csv(here("processed-data", "var-decomp", "flam_curve_vardecomp.csv"), show_col_types = FALSE) %>% 
  drop_na(lfm, water_potential, spp, plant, year_month, F.Group) %>% 
  mutate(plant = as.factor(plant), 
         F.Group = as.factor(F.Group), 
         year = as_factor(year))

angio_flam <- flam_curve_df_2.1 %>% 
  filter(F.Group == "Angiosperm")

gymno_flam <- flam_curve_df_2.1 %>% 
  filter(F.Group == "Gymnosperm")

pv_all_df_2.1 <-  read_csv(here("processed-data", "var-decomp", "all_pv_curves_clean_vardecomp.csv"), show_col_types = FALSE) %>% 
  filter(individual != c('QUKE_2_2020-10-21', 'QUKE_4_2020-10-21')) %>% 
  mutate(plant = as.factor(plant), 
         year = as.factor(year), 
         spp = as.factor(spp)) %>% 
  select(lfm, water_potential, F.Group, plant, year, year_month, spp) %>% 
  na.omit()

angio_pv <- pv_all_df_2.1%>% 
  filter(F.Group == "Angiosperm")

gymno_pv <- pv_all_df_2.1 %>% 
  filter(F.Group == "Gymnosperm") 

field_data_all_2.1 <- read_csv(here("processed-data", "var-decomp", "field_data_vardecomp.csv"), show_col_types = FALSE)  %>% 
  drop_na(lfm, water_potential, spp, plant, year_month, age_new) %>% 
  mutate(plant = as.factor(plant), 
         log_lfm = as.numeric(log(lfm))) %>% 
  mutate(plant = case_when(
    str_detect(unique_id2, "1.1_1") | str_detect(unique_id2, "_1_1") ~ 1,
    str_detect(unique_id2, "1.2_1") | str_detect(unique_id2, "_2_1") ~ 2,
    str_detect(unique_id2, "1.3_1") | str_detect(unique_id2, "_3_1") ~ 3,
    str_detect(unique_id2, "1.4_1") | str_detect(unique_id2, "_4_1") ~ 4,
    str_detect(unique_id2, "1.5_1") | str_detect(unique_id2, "_5_1") ~ 5,
    str_detect(unique_id2, "1.6_1") | str_detect(unique_id2, "_6_1") ~ 6,
    str_detect(unique_id2, "2.1_2") | str_detect(unique_id2, "_1_2") ~ 7,
    str_detect(unique_id2, "2.2_2") | str_detect(unique_id2, "_2_2") ~ 8,
    str_detect(unique_id2, "2.3_2") | str_detect(unique_id2, "_3_2") ~ 9,
    str_detect(unique_id2, "2.4_2") | str_detect(unique_id2, "_4_2") ~ 10,
    str_detect(unique_id2, "2.5_2") | str_detect(unique_id2, "_5_2") ~ 11
  )) %>% 
  mutate(age_new_num = case_when(age_new == 'new' ~ 1,
                                 age_new == 'old' ~ 0,
                                 age_new == 'both' ~ 0.5)) %>% 
  mutate(plant = as.factor(plant)) %>% 
  drop_na(log_lfm) 

angio_field <- field_data_all_2.1 %>% 
  filter(F.Group == "Angiosperm")

gymno_field <- field_data_all_2.1 %>% 
  filter(F.Group == "Gymnosperm")
```

# Variance Decomp.
```{r, fig.height=1, fig.width=1.6}
form <- ~ water_potential + (1|year_month) + (1|plant) + (1|spp)

lfm_matrix <- angio_pv %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, angio_pv)
varPart

pv_vardecomp_angio <- plotPercentBars.new(varPart, col = c(vcol)) + theme(legend.position = "none")
pv_vardecomp_angio

ggsave(plot=pv_vardecomp_angio, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "pv_vardecomp_angio"), device="jpg")

form <- ~ water_potential + (1|year_month)+ (1|spp) + (1|plant)

lfm_matrix <- gymno_pv %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, gymno_pv)
varPart
summary(gymno_pv)
summary(angio_pv)

pv_vardecomp_gymno <- plotPercentBars.new(varPart, col = c(vcol)) + theme(legend.position = "none")
pv_vardecomp_gymno

ggsave(plot=pv_vardecomp_gymno, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "pv_vardecomp_gymno"), device="jpg")

#------

form <- ~ water_potential + (1|spp) + (1|year_month) + (1|plant)  

lfm_matrix <- angio_flam %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, angio_flam)
varPart

flam_vardecomp_angio <- plotPercentBars.new(varPart, col = c(vcol)) + theme(legend.position = "none")
flam_vardecomp_angio

ggsave(plot=flam_vardecomp_angio, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "flam_vardecomp_angio"), device="jpg")

#------

form <- ~ water_potential  + (1|spp) + (1|year_month) + (1|plant)  

lfm_matrix <- gymno_flam %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, gymno_flam)
varPart

flam_vardecomp_gymno <- plotPercentBars.new(varPart, col = c(vcol)) + theme(legend.position = "none")
flam_vardecomp_gymno

ggsave(plot=flam_vardecomp_gymno, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "flam_vardecomp_gymno"), device="jpg")

#------

form <- ~ water_potential + (1|age_new) + (1|spp) + (1|year_month) + (1|plant)

lfm_matrix <- angio_field %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, angio_field)
varPart

field_vardecomp_angio <- plotPercentBars.new(varPart, col = c(vcol))+ theme(legend.position = "none")  
field_vardecomp_angio

ggsave(plot=field_vardecomp_angio, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "field_vardecomp_angio"), device="jpg")

#------
```


```{r, fig.height=1, fig.width=1.6}
form <- ~ water_potential + (1|age_new) + (1|spp) + (1|year_month) + (1|plant)

lfm_matrix <- gymno_field %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, gymno_field)
varPart

field_vardecomp_gymno <- plotPercentBars.new(varPart, col = c(vcol))+ theme(legend.position = "none")
field_vardecomp_gymno

ggsave(plot=field_vardecomp_gymno, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "field_vardecomp_gymno"), device="jpg")
```

# Scatterplots

## Function
```{r}
lfm.vs.mpa.scatterplot <- function(f.group.lab = " ", f.group, y.lab = " ", df, y.axis = F, x.axis = F, y.max, present.title = F) {
  
# For color palette
if(f.group == "Angiosperm") {color_pal <- c('#5792CC', '#4D5B75', '#6E406E')}
if(f.group == "Gymnosperm") {color_pal <- c('#42401D', '#5DA493', '#D8AB43')}
  
# For TLP linetype
if(f.group == "Angiosperm") {fgr_lty <- 1}
if(f.group == "Gymnosperm") {fgr_lty <- 2}
  
# For axis text and ticks
if(y.axis == T) {y.text <- element_text(size = 16)}
if(y.axis == T) {y.tick <- NULL}
if(y.axis == F) {y.text <- element_blank()}
if(y.axis == F) {y.tick <- element_blank()}
if(x.axis == T) {x.text <- element_text(size = 16)}
if(x.axis == T) {x.tick <- NULL}
if(x.axis == F) {x.text <- element_blank()}
if(x.axis == F) {x.tick <- element_blank()}
  
# For plot title
if(present.title == T) {plot.title.format <- element_text(size = 30, face = 'bold', hjust = 0.5)}
if(present.title == F) {plot.title.format <- element_blank()}

fgroup_pv_summaries <- fgroup_pv_summaries %>% 
  filter(F.Group == f.group)
  
plot <- df %>% 
  filter(lfm < 300, 
         lfm > 50) %>% 
  filter(F.Group == f.group) %>% 
  ggplot(aes(y = lfm, 
             x = -1*water_potential, 
             color = spp)) +
  geom_vline(aes(xintercept = -1*mean_tlp_group), lty = fgr_lty, data = fgroup_pv_summaries) +
  geom_jitter(alpha = .5, 
              size = 2) +
  scale_color_manual(values = color_pal) +
  scale_y_continuous(limits = c(50, y.max), breaks = c(y.max/5, 2*y.max/5, 3*y.max/5, 4*y.max/5)) +
  labs(title = f.group.lab,
       x = " ", 
       y = y.lab) +
   theme(legend.position = "none",
         plot.title = plot.title.format,
         axis.title = element_text(face = 'bold', size = 26),
         axis.text.y = y.text,
         axis.text.x = x.text,
         axis.ticks.y = y.tick,
         axis.ticks.x = x.tick,
         strip.background = element_blank(),
         strip.text = element_text(size  = 26, face = "bold"),
         plot.margin = unit(c(0.05, 0, 0, 0.1), 'cm')) + # previous: 0.05, 0, 0, 0.1
  xlim(0, 10)

return(plot)
}
```


###- Field plot (a)

```{r}
field_data_all$spp <- factor(field_data_all$spp, levels = c('ABCO', 'PIJE', 'CADE', 'ARPA', 'CECO', 'QUKE'))

field_plot_angio <- lfm.vs.mpa.scatterplot(f.group.lab = "Angiosperm", f.group = "Angiosperm", y.lab = "Field Data", y.axis = T, y.max = 300, df = field_data_all_2.1, present.title = T) +
  annotate(geom = "text", x = 0.5, y = 280, label = 'a', fontface = 'bold', size = 12)
field_plot_angio

field_vd_sp_angio <- field_plot_angio + annotation_custom(ggplotGrob(field_vardecomp_angio),
                                     xmin = 7.1, xmax = 10,
                                     ymin = 95, ymax = 295)
field_vd_sp_angio

field_plot_gymno <- lfm.vs.mpa.scatterplot(f.group.lab = "Gymnosperm", f.group = "Gymnosperm", y.max = 300, df = field_data_all_2.1, present.title = T) +
  annotate(geom = "text", x = 0.5, y = 280, label = 'b', fontface = 'bold', size = 12)
field_plot_gymno

field_vd_sp_gymno <- field_plot_gymno + annotation_custom(ggplotGrob(field_vardecomp_gymno),
                                     xmin = 7.1, xmax = 10,
                                     ymin = 95, ymax = 295)
field_vd_sp_gymno
```

### - PV plot (b)

```{r}
pv_plot_df <- pv_all_df %>% 
  filter(!spp %in% c("ADFA", "CEME"))

pv_plot_df$spp <- factor(pv_plot_df$spp, levels = c('ABCO', 'PIJE', 'CADE', 'ARPA', 'CECO', 'QUKE'))

pv_plot_angio <- lfm.vs.mpa.scatterplot(f.group = "Angiosperm", y.lab = "PV Curves", y.axis = T, y.max = 250, df = pv_plot_df) +
  annotate(geom = "text", x = 0.5, y = 230, label = 'c', fontface = 'bold', size = 12)
pv_plot_angio

pv_vd_sp_angio <- pv_plot_angio + annotation_custom(ggplotGrob(pv_vardecomp_angio),
                                     xmin = 7.1, xmax = 10,
                                     ymin = 85, ymax = 246)
pv_vd_sp_angio

pv_plot_gymno <- lfm.vs.mpa.scatterplot(f.group = "Gymnosperm", y.max = 250, df = pv_plot_df) +
  annotate(geom = "text", x = 0.5, y = 230, label = 'd', fontface = 'bold', size = 12)
pv_plot_gymno

pv_vd_sp_gymno <- pv_plot_gymno + annotation_custom(ggplotGrob(pv_vardecomp_gymno),
                                     xmin = 7.1, xmax = 10,
                                     ymin = 85, ymax = 246)
pv_vd_sp_gymno
```

### - Flam plot (c)
```{r}
flam_all_df <- flam_curve_phys_all_raw %>% 
  filter(!spp %in% c("ADFA", "CEME"))

flam_plot_angio <- lfm.vs.mpa.scatterplot(f.group = "Angiosperm", y.lab = "Flam. Data", y.axis = T, y.max = 250, x.axis = T, df = flam_all_df) +
  annotate(geom = "text", x = 0.5, y = 230, label = 'e', fontface = 'bold', size = 12)
flam_plot_angio

flam_vd_sp_angio <- flam_plot_angio + annotation_custom(ggplotGrob(flam_vardecomp_angio),
                                     xmin = 7.1, xmax = 10,
                                     ymin = 85, ymax = 246)
flam_vd_sp_angio

flam_plot_gymno <- lfm.vs.mpa.scatterplot(f.group = "Gymnosperm", y.max = 250, x.axis = T, df = flam_all_df) +
  annotate(geom = "text", x = 0.5, y = 230, label = 'f', fontface = 'bold', size = 12)
flam_plot_gymno

flam_vd_sp_gymno <- flam_plot_gymno + annotation_custom(ggplotGrob(flam_vardecomp_gymno),
                                     xmin = 7.1, xmax = 10,
                                     ymin = 85, ymax = 246)
flam_vd_sp_gymno
```

## Arranging

Legend 1 - Scatterplot:
```{r}
field_data_all$Species <- factor(field_data_all$Species, levels = c("Ab. concolor", "Pi. jeffreyi", "Ca. decurrens", "Ar. patula", "Ce. cordulatus", "Qu. kelloggii"))

field_plot_leg <- ggplot(aes(y = lfm, 
             x = -1*water_potential, 
             color = Species), 
         data = field_data_all) +
  geom_vline(aes(xintercept = -1*mean_tlp_group, 
                 lty = F.Group), 
             data = fgroup_pv_summaries) +
  geom_point(size = 3,
             alpha = .7, 
             data = field_data_all) +
  labs(color = "Species", 
       lty = "TLP") +
   theme(plot.margin = unit(c(.2, .5, .3, .25), "cm"),
        axis.title = element_text(face = 'bold', size = 26),
        axis.text = element_text(size = 16),
        legend.title = element_text(face = 'bold', size = 24),
        legend.text = element_text(face = 'italic', size = 20),
        legend.key = element_rect(fill = 'white')) +
  color_many2 

field_plot_leg
legend_dots <- cowplot::get_legend(field_plot_leg)
```

Legend 2 - Var. Decomp.
```{r}
#-------

form <- ~ water_potential + (1|spp) + (1|year_month) + (1|plant) + (1|age_new)

lfm_matrix <- field_data_all_2.1 %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, field_data_all_2.1)
varPart

legend_title <- "Predictor"

legend <- plotPercentBars.legend(varPart, col = c(vcol)) +
  scale_fill_discrete(labels=c("Residuals" = "Residuals",
                             "water_potential" = 'Water Potential',
                             "year_month" = "Timing", 
                             "year" = "Timing",
                             "spp" = "Species", 
                             "plant" = "Plant", 
                             "age_new" = "Old/New Growth"), 
             limits = c("Residuals", "Water Potential", "Timing",
                       "Species", "Plant", "Old/New Growth"),
             type = c('grey', '#280b53',  '#d44842', "#9f2a63", '#65156e', '#fac228')) +
   theme(plot.margin = unit(c(.2, .1, .3, .25), "cm"),
         axis.title = element_text(face = 'bold', size = 26),
        axis.text = element_text(size = 22),
        legend.title = element_text(face = 'bold', size = 24),
       legend.text = element_text(size = 20)
        ) +
  labs(fill = "Predictor")
legend

cow_legend <- cowplot::get_legend(legend)
cow_legend

blank_plot <- ggplot(data = field_data_all_2.1, aes(x = lfm, y = mpa)) +
  geom_point(color = 'white') +
  theme_void()

legend <- cowplot::plot_grid(blank_plot, legend_dots, cow_legend, ncol = 1, rel_heights = c(0.7, 1, 1.6))
legend
```

Combining
```{r}
y.grob <- textGrob("Live Fuel Moisture (%)", 
                   rot = 90,
                   gp=gpar(fontface="bold", 
                           col="black", 
                           fontsize=30))
x.grob <- textGrob("Water Potential (-MPa)",
                   gp=gpar(fontface="bold", 
                           col="black", 
                           fontsize=30))


plots <- cowplot::plot_grid(field_vd_sp_angio, field_vd_sp_gymno, pv_vd_sp_angio, pv_vd_sp_gymno, flam_vd_sp_angio, flam_vd_sp_gymno, ncol = 2, nrow = 3, rel_heights = c(1.15,1,1.08), rel_widths = c(1.08, 1))
plots

plots2 <- gridExtra::grid.arrange(arrangeGrob(plots, left = y.grob, bottom = x.grob))

plots_legend <- cowplot::plot_grid(plots2, legend, rel_widths = c(5, 1.5), rel_heights = c(1,.5))
plots_legend

ggsave(plot=plots_legend, bg = "white" , here("figures", "main-figures", "Fig5.LFM.vs.MPa.Scatterplots.jpg"), height = 10.5, width = 14.5)
```


# Split by TLP

Angio, above: 
both angiosperms (breakpoint = -2.6 +/- .152 MPa, TLP = -2.6 +/- .27 MPa), and for gymnosperms (breakpoint = -2.05 +/- .102 MPa, p = 0.278, TLP = -2.3 +/- .142 MPa). 

```{r, fig.height=1, fig.width=.6}
angio_above <- angio_field %>% 
  filter(water_potential > -2.6)

form <- ~ water_potential + (1|spp) + (1|year_month) + (1|plant) + (1|age_new)

lfm_matrix <- angio_above %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, angio_above )
varPart

above_vardecomp_angio <- plotPercentBars.new(varPart, col = c(vcol)) + theme(legend.position = "none")+
  labs(title = "Angiosperm, above")
above_vardecomp_angio

ggsave(plot=pv_vardecomp_angio, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "above_vardecomp_angio"), device="jpg")

angio_below <- angio_field %>% 
  filter(water_potential < -2.6)

#below

lfm_matrix <- angio_below %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, angio_below )
varPart

below_vardecomp_angio <- plotPercentBars.new(varPart, col = c(vcol)) + theme(legend.position = "none")+
  labs(title = "Angiosperm, below")
below_vardecomp_angio

ggsave(plot=pv_vardecomp_angio, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "below_vardecomp_angio"), device="jpg")



#gymno above

gymno_above <- gymno_field %>% 
  filter(water_potential > -2.3)


lfm_matrix <- gymno_above %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, gymno_above )
varPart

above_vardecomp_gymno <- plotPercentBars.new(varPart, col = c(vcol)) + theme(legend.position = "none")+
  labs(title = "Gymnosperm, above")
above_vardecomp_gymno

ggsave(plot=pv_vardecomp_gymno, bg = "white" , here::here("figures",  "extra-figures", "var_decomp", "above_vardecomp_gymno"), device="jpg")

#gymno below

gymno_below <- gymno_field %>% 
  filter(water_potential < -2.3)


lfm_matrix <- gymno_below %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, gymno_below )
varPart

below_vardecomp_gymno <- plotPercentBars.new(varPart, col = c(vcol)) + 
  theme(legend.position = "none") +
  labs(title = "Gymnosperm, below")


below_vardecomp_gymno+
  theme(strip.text = element_text("Gymnosperm, below"))

ggsave(plot=pv_vardecomp_gymno, bg = "white" , here::here("figures",  "extra-figures", "var_decomp", "below_vardecomp_gymno"), device="jpg")
```


```{r, fig.height= 4, fig.width=4}
plots_stacked <- cowplot::plot_grid(above_vardecomp_angio, 
                                    above_vardecomp_gymno, 
                                    below_vardecomp_angio, 
                                    below_vardecomp_gymno, 
                                    ncol = 2,
                                    labels=c('a', 'b', 'c', 'd'),
                                    label_size = 22,
                                    label_fontface = "bold",
                                    label_y = 1.03)
plots_stacked

plots_stacked_legend <- cowplot::plot_grid(plots_stacked, cow_legend, ncol = 2, rel_widths = c(4,1))
plots_stacked_legend

ggsave(plot=plots_stacked_legend, bg = "white" , here::here("figures",  "supp-figures", "FigS3.var_decomp_split_TLP.jpg"), height = 7, width = 9)
```

#New growth only:

###- Field plot - new growth only

```{r}

form <- ~ water_potential + (1|spp) + (1|year_month) + (1|plant) 

angio_field_new <- angio_field %>% 
  filter(age_new == 'new') 
  
lfm_matrix <- angio_field_new  %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, angio_field_new )
varPart

field_vardecomp_angio_new <- plotPercentBars.new(varPart, col = c(vcol))+ theme(legend.position = "none")  
field_vardecomp_angio

ggsave(plot=field_vardecomp_angio_new, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "field_vardecomp_angio_new"), device="jpg")

#------

form <- ~ water_potential + (1|spp) + (1|year_month) + (1|plant) 

gymno_field_new <- gymno_field %>% 
  filter(age_new == 'new') 

lfm_matrix <- gymno_field_new %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, gymno_field_new)
varPart

field_vardecomp_gymno_new <- plotPercentBars.new(varPart, col = c(vcol))+ theme(legend.position = "none")
field_vardecomp_gymno_new

ggsave(plot=field_vardecomp_gymno_new, bg = "white" , here::here("figures", "extra-figures", "var_decomp", "field_vardecomp_gymno_new"), device="jpg")

#-----
field_data_all_new <- field_data_all %>% 
  filter(age_new == 'new')
  
field_data_all_new$spp <- factor(field_data_all_new$spp, levels = c('ABCO', 'PIJE', 'CADE', 'ARPA', 'CECO', 'QUKE'))

field_plot_angio_new  <- lfm.vs.mpa.scatterplot(f.group.lab = "Angiosperm", f.group = "Angiosperm", y.lab = "Field Data", y.axis = T, y.max = 300, df = field_data_all_new) +
  annotate(geom = "text", x = 0.5, y = 280, label = 'a', fontface = 'bold', size = 20)
field_plot_angio_new 

field_vd_sp_angio_new  <- field_plot_angio_new  + annotation_custom(ggplotGrob(field_vardecomp_angio_new),
                                     xmin = 7.25, xmax = 10,
                                     ymin = 100, ymax = 280)
field_vd_sp_angio_new 

field_plot_gymno_new  <- lfm.vs.mpa.scatterplot(f.group.lab = "Gymnosperm", f.group = "Gymnosperm", y.max = 300, df = field_data_all_new) +
  annotate(geom = "text", x = 0.5, y = 280, label = 'b', fontface = 'bold', size = 20)
field_plot_gymno_new 

field_vd_sp_gymno_new <- field_plot_gymno_new  + annotation_custom(ggplotGrob(field_vardecomp_gymno_new),
                                     xmin = 7.45, xmax = 10,
                                     ymin = 100, ymax = 280)
field_vd_sp_gymno_new

field_plot_new_combined <- cowplot::plot_grid(field_vd_sp_angio_new, field_vd_sp_gymno_new, legend, ncol=3, rel_widths = c(5, 5, 1.5), rel_heights = c(1,1, .5))
field_plot_new_combined

ggsave(plot=field_plot_new_combined, bg = "white" , here("figures", "extra-figures", "New_LFM_MPa_Scatterplots.jpg"), height = 10, width = 14)
```

