---
title: "Mixed Effects Models - Time to Ignition"
author: "Indra Boving & Joe Celebrezze"
date: "6/21/2022"
output: html_document
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#lots of extra here, but oh well... 
library(ggplot2)
library(gapminder)
library(data.table)
library(purrr) #for visualizing all variables in one big plot
library(naniar) #for dealing with NAs nicely 
library(tidyverse)
library(devtools)
library(ggfortify)
library(ggpubr)
library(jtools)
library(cowplot)
library(lmerTest)
library(ggeffects)  
library(GGally) #for corr plots
require(kimisc) # has the nlist function to create a named list
require(AICcmodavg) # has the aictab function
library(psych)

#devtools::install_github("strengejacke/strengejacke")
library(strengejacke)
library(sjPlot) # table functions
library(sjmisc) # sample data

library(lme4) # fitting models
library(here)
library(effects) #for plotting model effects
library(sjstats) #use for r2 functions
library(TMB)
library(glmmTMB)
library(lattice)
library(equatiomatic)
library("broom.mixed")
#library(ggbiplot)
select = dplyr::select
here = here::here
library(MuMIn)
library(modelsummary)
#install_github("BlakeRMills/MetBrewer") 
#library("BlakeRMills/MetBrewer")
#library(memmented)
filter = dplyr::filter
mutate = dplyr::mutate
library(nlme)
library(MetBrewer)
#install.packages("memmented")
#devtools::install_github("hohenstein/remef")
library(remef)
library(kableExtra)
```


#------------------------------------
# 1. Data wrangling
Reading in dataframe

- For the Sierra analysis, this is combining all species and dropping the august sampling data (not enough samples and it was measured a lil differently). 

```{r}
mem_data_all <- read_csv(here("processed-data", "sierra_flam_data_all.csv")) %>% 
  select(lfm, mpa, tti, fh, fd, gd, prop_ignite, temp_change, ignition, sample_wt, dry_wt, fresh_wt, water_wt, location, site, year_month, spp, individual) %>% 
  mutate(dw_flam_sample = sample_wt * (dry_wt/fresh_wt),
         ww_flam_sample = sample_wt * (water_wt/fresh_wt)) %>% 
  mutate(excess_water = (ww_flam_sample - dw_flam_sample)) %>% 
  mutate(mpa_scaled = scale(mpa)) %>% 
  group_by(spp) %>% 
  mutate(dw_flam_sample_scaled = scale(dw_flam_sample), 
         sample_wt_scaled = scale(sample_wt), 
         ww_flam_sample_scaled = scale(ww_flam_sample),
         lfm_scaled = scale(lfm), 
         excess_water_scaled = scale(excess_water)) %>% 
  filter(!year_month %in% c("2021_august"))
```

```{r}
mem_data_all %>% 
ggplot(aes( 
           y = mpa_scaled, 
           x = tti, 
           color = spp)) +
  geom_point()+
  geom_smooth(method = "lm")
```

Maxs and mins from the field data: 

```{r}
# adfa_min <- 55
# adfa_max <- 110
# 
# ceme_min <- 55
# ceme_max <- 140
```

### All dates datasets

```{r, message=FALSE, warning=FALSE, include=FALSE}
# mem.adfa.subset <- mem_data_all  %>% 
#   filter(spp == "ADFA") %>% 
#   filter(ignition == "1")
# 
# mem.CEME.subset <- mem_data_all  %>% 
#   filter(spp == "CEME")%>% 
#   filter(ignition == "1")
# 
# mem.adfa.subset.allignitions <- mem_data_all  %>% 
#   filter(spp == "ADFA")
# 
# mem.CEME.subset.allignitions <- mem_data_all %>% 
#   filter(spp == "CEME")
# 
# mem.adfa.subset.limited <- mem.adfa.subset %>% 
#   filter(lfm < adfa_max, lfm > adfa_min)
# 
# mem.CEME.subset <- mem_data_all %>% 
#   filter(spp == "CEME")
# 
# mem.CEME.subset.limited <- mem.CEME.subset %>% 
#   filter(lfm < ceme_max, lfm > ceme_min)
```

#------------------------------------
# 2.0 Predicting flam metrics: TTI, FH, FD, GD, Temp change, prop ignite. 

## 2.0.1 TTI: Figures of models

```{r}
tti_mpa_m1 <- lmer(tti ~ mpa + spp + year_month + (1 | individual), data =  mem_data_all)
summary(tti_mpa_m1)

#remove fixed effect of spp:
#     see what names are associated: 
term2coef(tti_mpa_m1, "spp")

r1_1 <- remef(tti_mpa_m1 , fix = c("spparpa", "sppcade", "sppceco", "spppije", "sppquke"))
summary(r1_1)
head(r1_1)

# remove fixed effect of 'Days' and the intercept
#r1_2 <- remef(fm1, fix = "Days", keep.intercept = FALSE)
```

```{r}
# (pp <- plot_model(mpa_mod_fig.mpa,type="pred",
#        terms=c("mpa","year_month"),pred.type="re"))
# 
# (pp <- plot_model(mpa_mod_fig.mpa,type="pred",
#        terms=c("mpa","spp"),pred.type="re"))
```

#### Check assumptions

```{r}
plot(tti_mpa_m1)
#qqnorm(mpa_mod_fig.mpa, ~ranef(., level=2))
#https://stats.stackexchange.com/questions/77891/checking-assumptions-lmer-lme-mixed-models-in-r for above code - getting an error right now though
```

# ---------------------------------
# MODEL SELECTION 1
What covariates to include?

## Site, spp, year_month, sample_wt
```{r}
sw_mpa_mod_fig.mpa <- lmer(tti ~ mpa + spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_mpa_mod_fig.mpa)
```

```{r}
sw_max_model <- lmer(tti ~ spp + dw_flam_sample_scaled + ww_flam_sample_scaled +  mpa_scaled + lfm_scaled + excess_water_scaled + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_max_model)

tidy_tti <- broom.mixed::tidy(sw_max_model)
```

```{r}
sw_max_model_nolfm <- lmer(tti ~ spp + dw_flam_sample_scaled +  ww_flam_sample_scaled +  mpa_scaled + excess_water_scaled + site +  year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_max_model_nolfm)
```

```{r}
sw_max_model_nompa <- lmer(tti ~ spp + dw_flam_sample_scaled +  ww_flam_sample_scaled +  lfm+ excess_water_scaled + site +  year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_max_model_nompa)
```

```{r}
sw_m3 <- lmer(tti ~ spp + ww_flam_sample_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m3)
```

```{r}
sw_m6 <- lmer(tti ~ dw_flam_sample_scaled +  spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m6)
```

```{r}
sw_m6.5 <- lmer(tti ~ dw_flam_sample_scaled +  ww_flam_sample_scaled +  spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m6.5)
```

```{r}
sw_m7 <- lmer(tti ~ mpa_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m7)
```

```{r}
sw_m10 <- lmer(tti ~ lfm_scaled + spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m10)

```

```{r}
sw_m11 <- lmer(tti ~ mpa_scaled*spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m11)
```

```{r}
sw_m12 <- lmer(tti ~ excess_water_scaled + spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m12)
```

```{r}
sw_m12.5 <- lmer(tti ~ excess_water_scaled + mpa_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m12.5) ##High correlation! Don't use
```

```{r}
sw_m13 <- lmer(tti ~ excess_water_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m13) ##High correlation! Don't use
```

```{r}
sw_m14 <- lmer(tti ~ excess_water_scaled + spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m14)
```

```{r}
sw_m15 <- lmer(tti ~ excess_water_scaled * spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m15)
```

```{r}
tab_model(sw_mpa_mod_fig.mpa, 
          sw_m11, 
          sw_m7, 
          sw_m10,
          sw_m3, 
          sw_m6, 
          sw_m6.5, 
          sw_m12, 
          sw_m12.5, 
          sw_m13, 
          sw_m14,
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c('Intercept', 
                          'Water Potential (scaled)', 
                         # 'spp Effect (C. megacarpus)',
                          'Water Potential x spp Effect
                          (interaction)',
                          'LFM (%)',
                          'Water Weight (g)', 
                          'Dry Weight (g)',
                          'Site Effect (Site 1)',
                          'Excess Water (scaled)',
                          'Excess Water x spp Effect
                          (interaction)'),
         dv.labels = c("mpa_spp", 
                       "sw_m11", 
                       "sw_m7", 
                       #"m10",
                       "sw_m10",
                       "sw_m3", 
                       "sw_m6", 
                       "sw_m6.5", 
                       "sw_m12",
                       "sw_m12.5", 
                       "sw_m13", 
                       "sw_m14"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity; site + spp + year_month + sample wt",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM_figures','site_yearmonth_samplewt_tti.html')) # saving _html into figures folder
```
#####TTI top models
```{r}
tab_model(sw_m11, sw_m12.5, sw_m13, sw_m7,
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c('Intercept', 
                          'Water Potential (scaled)', 
                         # 'spp Effect (C. megacarpus)',
                          'Water Potential x spp Effect
                          (interaction)',
                          'LFM (%)',
                          'Water Weight (g)', 
                          'Dry Weight (g)',
                          'Site Effect (Site 1)',
                          'Excess Water (scaled)',
                          'Excess Water x spp Effect
                          (interaction)'),
         dv.labels = c(#"mpa_spp", 
                       "sw_m11", 
                       #"m7", 
                       #"m10",
                      # "m10",
                       #"m3", 
                       #"m6", 
                       #"m6.5", 
                      # "m12",
                       "sw_m12.5", 
                       "sw_m13", 
                       "sw_m7"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity; site + spp + year_month + sample wt",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM_figures','site_yearmonth_samplewt_topAIC_tti.html')) # saving _html into figures folder
```

## Site, spp, year_month

```{r}
mpa_mod_fig.mpa <- lmer(tti ~ mpa + spp + site + year_month + (1 | individual), data = mem_data_all)

qqnorm(resid(mpa_mod_fig.mpa))
r <- resid(mpa_mod_fig.mpa)
plot(fitted(mpa_mod_fig.mpa), r)

performance::multicollinearity(mpa_mod_fig.mpa)
```

```{r}
max_model <- lmer(tti ~ spp + dw_flam_sample_scaled +  ww_flam_sample_scaled +  mpa_scaled + lfm_scaled+ excess_water_scaled + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(max_model)
```

```{r}
max_model_noww <- lmer(tti ~ spp + dw_flam_sample_scaled +  mpa_scaled + lfm_scaled+ excess_water_scaled + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(max_model_noww)
```

```{r}
max_model_nolfm <- lmer(tti ~ spp + dw_flam_sample_scaled +  ww_flam_sample_scaled +  mpa_scaled + excess_water_scaled + site +  year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(max_model_nolfm)
```

```{r}
max_model_nompa <- lmer(tti ~ spp + dw_flam_sample_scaled +  ww_flam_sample_scaled +  lfm+ excess_water_scaled + site +  year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(max_model_nompa)
```

```{r}
m3 <- lmer(tti ~ spp + ww_flam_sample_scaled +  site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m3)
```

```{r}
m6 <- lmer(tti ~ dw_flam_sample_scaled +  spp + site + year_month + (1 | individual), data = mem_data_all)

qqnorm(resid(m6))
r <- resid(m6)
plot(fitted(m6), r)

performance::multicollinearity(m6)
```

```{r}
m6.5 <- lmer(tti ~ dw_flam_sample_scaled +  ww_flam_sample_scaled +  spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m6.5)
```

```{r}
m7 <- lmer(tti ~ mpa_scaled + lfm_scaled+ spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m7)
```

```{r}
m10 <- lmer(tti ~ lfm_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)

qqnorm(resid(m10))
r <- resid(m10)
plot(fitted(m10), r)

performance::multicollinearity(m10)
```

```{r}
m11 <- lmer(tti ~ mpa_scaled*spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m11)
```

```{r}
m12 <- lmer(tti ~ excess_water_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m12)
```

```{r}
m12.5 <- lmer(tti ~ dw_flam_sample_scaled +  mpa_scaled + lfm_scaled+ spp + site + year_month + (1 | individual), data = mem_data_all)

qqnorm(resid(m12.5))
r <- resid(m12.5)
plot(fitted(m12.5), r)

performance::multicollinearity(m12.5) ##High correlation! Don't use
```

```{r}
m13 <- lmer(tti ~ excess_water_scaled + lfm_scaled+ spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m13) ##High correlation! Don't use
```

```{r}
m14 <- lmer(tti ~ excess_water_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m14)
```

```{r}
m15 <- lmer(tti ~ excess_water_scaled * spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m15)
```

```{r}
tab_model(mpa_mod_fig.mpa, m11, m7, m10, m3, m6, m6.5, m12, m15, m10, m13, m14,max_model_noww,
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c('Intercept', 
                          'Water Potential (scaled)', 
                          'spp Effect (C. megacarpus)',
                          'Water Potential x spp Effect
                          (interaction)',
                          'LFM (%)',
                          'Water Weight (g)', 
                          'Dry Weight (g)',
                          'Site Effect (Site 1)',
                          'Excess Water (scaled)',
                          'Excess Water x spp Effect
                          (interaction)'),
         dv.labels = c("mpa_spp", 
                       "m11", 
                       "m7", 
                      # "m7",
                       "m10",
                       "m3", 
                       "m6", 
                       "m6.5", 
                       "m12",
                       "m15", 
                       "m10",
                       "m13", 
                       "m14",
                       "max_model_noww"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity; site, spp, year_month",
        # caption = "site, spp, year_month",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM_figures','site_yearmonth_tti.html')) # saving _tti.html into figures folder
```
######TTI top models: 

The following models are the best models: 
```{r}
tab_model(m7, m11, m12.5, m13,
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c('Intercept', 
                          'Water Potential (scaled)', 
                          'spp Effect (C. megacarpus)',
                          'Water Potential x spp Effect
                          (interaction)',
                          'LFM (%)',
                          'Water Weight (g)', 
                          'Dry Weight (g)',
                          'Site Effect (Site 1)',
                          'Excess Water (scaled)',
                          'Excess Water x spp Effect
                          (interaction)'),
         dv.labels = c("m7", 
                       "m11", 
                       "m12.5",
                       "m13"),
         string.pred = "Coeffcient", 
         title = "BEST models with no collinearity; site, spp, year_month",
        # caption = "site, spp, year_month",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM_figures','site_yearmonth_topAIC_tti.html')) # saving _tti.html into figures folder
```

#TTI best model in table: 
```{r}
tab_model(m11, sw_m12.5,
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c('Intercept', 
                          'MPa (scaled)',
                          'A. patula',
                          "C. decurrens", 
                          "C. cordulatus", 
                          "P. jeffryii", 
                          "Q. kelloggii", 
                          "Plot",
                          "SEKI", 
                          'MPa x A. patula',
                          "MPa x C. decurrens", 
                          "MPa x C. cordulatus", 
                          "MPa x P. jeffryii", 
                          "MPa x Q. kelloggii",
                          'Excess Water (scaled)',
                          'LFM (scaled)',
                          "Sample weight (scaled"),
         dv.labels = c("sw_m11", 
                       #"m11", 
                       "sw_m12.5"),
         string.pred = "Coeffcient", 
         title = "BEST models with no collinearity; site, spp, year_month",
        # caption = "site, spp, year_month",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM_figures','tti_topAIC_tti.html')) # saving
```