---
title: "PV Curves"
author: "Indra Boving"
date: "11/8/2022"
output: html_document
---
# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(datapasta)
library(ggplot2)
library(purrr) #for visualizing all variables in one big plot
library(naniar) #for dealing with NAs nicely 
library(tidyverse)
library(ggpubr)
library(cowplot)
library(GGally) #for corr plots
require(kimisc) # has the nlist function to create a named list
#library(strengejacke)
library(sjPlot) # table functions
library(here)
library(effects) #for plofhng model effects
library(sjstats) #use for r2 functions
library("broom.mixed")
library(MuMIn)
library(modelsummary)
library(nlme)
library(lme4)
library(MetBrewer)
library(remef)
library(kableExtra)
library(janitor)
library(lubridate)
library(specr)
#install.packages("specr")

filter = dplyr::filter
mutate = dplyr::mutate
select = dplyr::select
here = here::here

source(here::here("scripts", "scripts_functions", "figure_info_sierra_flammability.R")) #color and theme info is here

# if (!require("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# 
# BiocManager::install("variancePartition")
library('variancePartition')
```

based on this paper: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8930200/#DS1 

#Data: 

```{r}
flam_curve_df_2.1 <- read_csv(here("processed-data", "analysis 2.0", "flam_curve_vardecomp_2.csv"), show_col_types = FALSE) %>% 
  drop_na(lfm, water_potential, spp, plant, year_month, F.Group) %>% 
  mutate(plant = as.factor(plant), 
         F.Group = as.factor(F.Group), 
         year = as_factor(year))

pv_all_df_2.1 <-  read_csv(here("processed-data", "analysis 2.0", "all_pv_curves_clean_vardecomp_2.csv"), show_col_types = FALSE) %>% 
  mutate(plant = as.factor(plant), 
         year = as.factor(year))

field_data_all_2.1 <- read_csv(here("processed-data", "analysis 2.0", "field_data_vardecomp_2.csv"), show_col_types = FALSE) %>% 
  drop_na(lfm, water_potential, spp, plant, year_month) %>% 
  mutate(plant = as.factor(plant), 
         log_lfm = as.numeric(log(lfm))) %>% 
  drop_na(log_lfm)
```

#Information:

From: https://rdrr.io/github/GabrielHoffman/variancePartition/man/calcVarPart-method.html 

For linear model, variance fractions are computed based on the sum of squares explained by each component. For the linear mixed model, the variance fractions are computed by variance component estimates for random effects and sum of squares for fixed effects.

For a generalized linear model, the variance fraction also includes the contribution of the link function so that fractions are reported on the linear (i.e. link) scale rather than the observed (i.e. response) scale. For linear regression with an identity link, fractions are the same on both scales. But for logit or probit links, the fractions are not well defined on the observed scale due to the transformation imposed by the link function.

The variance implied by the link function is the variance of the corresponding distribution:

logit -> logistic distribution -> variance is pi^2/3

probit -> standard normal distribution -> variance is 1

For the Poisson distribution with rate λ, the variance is log(1 + 1/λ).

For the negative binomial distribution with rate λ and shape θ, the variance is log(1 + 1/λ + 1/θ).

Variance decomposition is reviewed by Nakagawa and Schielzeth (2012), and expanded to other GLMs by Nakagawa, Johnson and Schielzeth (2017). See McKelvey and Zavoina (1975) for early work on applying to GLMs. Also see DeMaris (2002)

We note that Nagelkerke's pseudo R^2 evaluates the variance explained by the full model. Instead, a variance partitioning approach evaluates the variance explained by each term in the model, so that the sum of each systematic plus random term sums to 1 (Hoffman and Schadt, 2016; Nakagawa and Schielzeth, 2012). 

#Pressure Volume Curves

Try using variancePartition:

Best model from MEM: 

m10.75 <- lmer(lfm~ water_potential + F.Group + as.factor(year) + (1|plant), data = pv_all_df)
summary(m10.75) 

```{r}
form <- ~ water_potential + (1|year) + (1|plant)  + (1|spp)


lfm_matrix <- pv_all_df_2.1 %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, pv_all_df_2.1 )
varPart

plotVarPart(varPart)

pv_vardecomp <- plotPercentBars(varPart, col = c(vcol)) +
  labs(x = "PV")
pv_vardecomp
```



```{r}
varPart <- calcVarPart(lmer(lfm ~ water_potential  + (1|spp) + (1|year_month) + (1|F.Group) + (1|plant), pv_all_df_2.1))
varPart
```

#Flam curves

m11.75  <- lmer(lfm~ water_potential*F.Group + as.factor(year) + (1|plant), data = flam_curve_df)

No interaction:

```{r}
#pv_mod <- lmer(lfm ~ water_potential  + (1|spp) + (1|date), flam_curve_df_2.1)

form <- ~ water_potential  + (1|spp) + (1|year) + (1|plant)  

lfm_matrix <- flam_curve_df_2.1 %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, flam_curve_df_2.1)
varPart

plotVarPart(varPart)

flam_vardecomp <- plotPercentBars(varPart, col = c(vcol)) +
  labs(x = "Flam curve") 
flam_vardecomp
```

```{r}
#pv_mod <- lmer(lfm ~ water_potential  + (1|spp) + (1|date), flam_curve_df_2.1)

form <- ~ water_potential*spp  + (1|spp) + (1|year) + (1|plant)  

lfm_matrix <- flam_curve_df_2.1 %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, flam_curve_df_2.1)
varPart

plotVarPart(varPart)

flam_vardecomp_ints <- plotPercentBars(varPart#, col = c(vcol)
                                  ) +
  labs(x = "Flam curve") 
flam_vardecomp_ints
```

#FIeld data

(split at TLP)

Best model in MEM: 

m12.4<- lmer(log(lfm)~ water_potential*as.factor(year) + water_potential*F.Group + F.Group + (1|plant), data = field_data_all)

Above tlp:
```{r}
above <- field_data_all_2.1 %>% 
  group_by(spp) %>% 
  filter(lfm > lfm_tlp)

below <- field_data_all_2.1 %>% 
  group_by(spp) %>% 
  filter(lfm < lfm_tlp)
```


```{r}
form <- ~ water_potential + water_potential + (1|spp) + (1|year_month) + (1|plant) + (1|age_new)

lfm_matrix <- field_data_all_2.1 %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, field_data_all_2.1)
varPart

plotVarPart(varPart)

field_vardecomp_all <- plotPercentBars(varPart, col = c(vcol))+
  labs(x = "Field data", 
       title = "all together")  
field_vardecomp_all
```
```{r}
form <- ~ water_potential*spp  + (1|spp) + (1|year_month) + (1|plant) + (1|age_new)
#+ (1|F.Group) 


lfm_matrix <- field_data_all_2.1 %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, field_data_all_2.1)
varPart

plotVarPart(varPart)

field_vardecomp_ints <- plotPercentBars(varPart)+
  labs(x = "Field data", 
       title = "all together")  
field_vardecomp_ints
```

```{r}
form <- ~ water_potential  + (1|spp) + (1|year_month) + (1|plant)  + (1|age_new) #+ (1|F.Group)

lfm_matrix <- above %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, above)
varPart

plotVarPart(varPart)

field_vardecomp_above <- plotPercentBars(varPart, col = c(vcol))+
  labs(x = "Field data", 
       title = "Above")  
field_vardecomp_above
```

```{r}
form <- ~ water_potential*spp  + (1|spp) + (1|year_month) + (1|plant)  + (1|age_new) #+ (1|F.Group)

lfm_matrix <- above %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, above)
varPart

plotVarPart(varPart)

field_vardecomp_above_ints <- plotPercentBars(varPart)+
  labs(x = "Field data", 
       title = "Above")  
field_vardecomp_above_ints
```

```{r}
form <- ~ water_potential + (1|spp) + (1|year_month) + (1|plant)  + (1|age_new)

#form <- ~ water_potential  + spp + year_month + (1|plant) + F.Group + age_new

lfm_matrix <- below %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, below)
varPart

plotVarPart(varPart)

field_vardecomp_below <- plotPercentBars(varPart, col = c(vcol))+
  labs(x = "Feild data", 
       title = "Below")  
field_vardecomp_below
```
```{r}
form <- ~ water_potential*spp + (1|spp) + (1|year_month) + (1|plant)  + (1|age_new)

#form <- ~ water_potential  + spp + year_month + (1|plant) + F.Group + age_new

lfm_matrix <- below %>% 
  ungroup() %>% 
  mutate(id = row_number()) %>% 
  select(id, log_lfm) %>% 
  pivot_wider(names_from = id, 
              values_from = log_lfm) 

varPart <- fitExtractVarPartModel(lfm_matrix, form, below)
varPart

plotVarPart(varPart)

field_vardecomp_below_ints <- plotPercentBars(varPart)+
  labs(x = "Feild data", 
       title = "Below")  
field_vardecomp_below_ints
```

#Combine:

```{r}
cowplot::plot_grid(field_vardecomp_all, flam_vardecomp, pv_vardecomp, nrow = 3)


cowplot::plot_grid(field_vardecomp, field_vardecomp_above, field_vardecomp_below, nrow = 3)

cowplot::plot_grid(field_vardecomp_ints, field_vardecomp_above_ints, field_vardecomp_below_ints, nrow = 3)

cowplot::plot_grid(field_vardecomp_ints, pv_vardecomp, flam_vardecomp_ints, nrow = 3)
```

