---
title: "abco segmented regressions"
author: "Indra Boving & Joe Celebrezze"
date: "4/15/2021"
output: html_document
---

#Setup:
```{r}
knitr::opts_chunk$set(echo = TRUE)
#lots of extra here, but oh well___ 
library(ggplot2)
library(gapminder)
library(tidyverse)
library(lme4)
library(here)
library(segmented)
library(nlme)
citation('nlme')
library(lubridate)
#install.packages("plotrix")
library(plotrix)
filter = dplyr::filter
here = here::here
select = dplyr::select
#source(here("source-code", "source-segmented_lme_R"))

# Function to plot mixed effects model segmented regressions:

source(here::here("scripts", "scripts_functions", "plot_segmented_MEM.R"))
```

# Reading in Dataframe
```{r}
seg_data_subset <- read_csv(here("processed-data", "analysis 2.0", "sierra_flam_data_all.csv")) %>% 
  mutate(id = individual)
```

# Color by Season

```{r}
seg_data_subset$color <- 'black'
seg_data_subset$color[seg_data_subset$year_month=='2020_October']="purple"
seg_data_subset$color[seg_data_subset$year_month=='2020_September']="pink"
```

# Splitting by Species and by Sampling Date

```{r} 
seg_data_subset <- seg_data_subset %>% 
  mutate_if(is.character, str_to_lower) %>% 
  mutate(spp = str_trim(spp),
         lfm_scaled = scale(lfm),
    name = paste(spp,"_max", sep = ""), 
    name_subset = paste(spp, "_subset_seg", sep = ""), 
   # name_yearmonth = intersect(spp, year_month), 
    name_yearmonth = paste(spp, year_month, "subset_seg", sep = "_")) 

seg_data_subset %>% 
  group_split(spp) %>%
  setNames(unique(seg_data_subset$name_subset))  %>%
  list2env(envir = globalenv())

seg_dfs <- list(abco_subset_seg, 
                arpa_subset_seg, 
                cade_subset_seg, 
                ceco_subset_seg,
                pije_subset_seg, 
                quke_subset_seg)
 
seg_data_subset %>% 
  group_split(name_yearmonth) %>%
  setNames(unique(seg_data_subset$name_yearmonth))  %>%
  list2env(envir = globalenv())
```


# Maximums for LFM, MPa

```{r}
max_seg_data <- seg_data_subset %>% 
  type.convert(as.is = TRUE) %>% 
  select(mpa, lfm, spp) %>% 
  group_by(spp) %>% 
  summarise(across(where(is.numeric), max, .names = "max_{.col}")) 

abco_max_mpa <- max_seg_data %>% 
  filter(spp == "abco") %>% 
  select(max_mpa) %>% 
  pull()

abco_max_lfm <- max_seg_data %>% 
  filter(spp == "abco") %>% 
  select(max_lfm) %>% 
  pull()
```

# PV Curve Data


```{r}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"), show_col_types = FALSE) %>% 
   filter(timing == "fall") %>% 
  mutate_if(is.character, str_to_lower) %>% 
  #mutate_at(spp, str_to_lower) %>% 
  mutate(spp = str_trim(spp),
    name = paste(spp,"_pv", sep = "")) %>% 
  filter(!spp %in% c("ADFA", "CEME"))

pv_summary_df_timing %>% 
  group_split(spp) %>%
   setNames(unique(pv_summary_df_timing$name)) %>%
  list2env(envir = globalenv())
```


```{r}
mean_mpa_abco <- abco_pv %>% 
  select(mean_tlp) %>% 
  pull()

lwr_mpa_abco <- abco_pv %>% 
  select(lwr) %>% 
  pull()

upr_mpa_abco <- abco_pv %>% 
  select(upr) %>% 
  pull()

mean_lfm_abco <- abco_pv %>% 
  select(mean_lfm) %>% 
  pull()

lwr_lfm_abco <- abco_pv %>% 
  select(lwr_lfm) %>% 
  pull()

upr_lfm_abco <- abco_pv %>% 
  select(upr_lfm) %>% 
  pull()
```

# -------

#Segmented regressions: 

We're just going to do a few metrics, to represent each of the axes: 

TTI, FH, FD, GD

Maybe: Max temp

## LFM

Ignitability Metrics:

### Time to Ignition

```{r}
o_mod<-lme(tti~lfm + year_month + site, random=~1|id, data=abco_subset_seg)
os_mod_b<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_b)

u_mod <- lm(tti~lfm + year_month + site, data = abco_subset_seg)
u_mod_b <- segmented(u_mod, ~lfm)
davies.test(u_mod_b)
summary.segmented(u_mod_b)

#rsegplot.lfm.nolegend(os_mod_b, abco_subset_seg, y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```


### Prop. Ignite (5%)
```{r}
o_mod<-lme(prop_ignite~lfm + year_month + site, random=~1|id, data=abco_subset_seg)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

# #rsegplot.lfm(os_mod, abco_subset_seg, 'abco', y_variable = 'prop_ignite_bins5_nodate',y_lab = "Proportion Ignted (5% Bins of LFM)", tlp = mean_lfm_abco, tlp_lower = lwr_lfm_abco, tlp_upper = upr_lfm_abco)
```

### Glow to Ignition
```{r}
abco_subset_seg_gti <- abco_subset_seg %>% 
  drop_na(gti)

o_mod<-lme(gti~lfm + year_month + site, random=~1|id, data=abco_subset_seg_gti)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#rsegplot_lfm(os_mod, abco_subset_seg, 'abco', y_variable = 'gti',y_lab = "Glow to Ignition (s)", tlp = mean_lfm_abco, tlp_lower = lwr_lfm_abco, tlp_upper = upr_lfm_abco)
```

Combustibility Metrics:

### Flame Height
```{r}
o_mod<-lme(fh~lfm + year_month + site, random=~1|id, data=abco_subset_seg)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

##rsegplot_lfm(os_mod, abco_subset_seg, 'abco', y_variable = 'fh',y_lab = "Flame Height (cm)", tlp = mean_lfm_abco, tlp_lower = lwr_lfm_abco, tlp_upper = upr_lfm_abco)
```

### Max_ Temp_
```{r}
abco_subset_seg_lower_temp_max <- abco_subset_seg %>% 
  drop_na(lower_temp_max)


o_mod<-lme(lower_temp_max~lfm + year_month + site, random=~1|id, data=abco_subset_seg_lower_temp_max)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

##rsegplot_lfm(os_mod, abco_subset_seg, 'abco', y_variable = 'temp_max',y_lab = "Maximum Temperature (C)", tlp = mean_lfm_abco, tlp_lower = lwr_lfm_abco, tlp_upper = upr_lfm_abco)
```

Sustainability Metrics:
### Flame Duration
```{r}
o_mod<-lme(fd~lfm + year_month + site, random=~1|id, data=abco_subset_seg)
os_mod_f<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_f)

##rsegplot_lfm(os_mod, abco_subset_seg, 'abco', y_variable = 'fd',y_lab = "Flame Duration (s)", tlp = mean_lfm_abco, tlp_lower = lwr_lfm_abco, tlp_upper = upr_lfm_abco)
```


# -------


## Water Potential
```{r}
abco_subset_seg <- abco_subset_seg %>% 
  mutate(mpa_scaled = scale(mpa))
```


 
Ignitability Metrics:

### Time to Ignition
```{r}
o_mod<-lme(tti~mpa + year_month + site, random=~1|id, data=abco_subset_seg)
os_mod_b1<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_b1)

#rsegplot_mpa(os_mod, abco_subset_seg, 'abco', y_variable = 'tti',y_lab = "Time to Ignition (s)", tlp = mean_mpa_abco, tlp_lower = lwr_mpa_abco, tlp_upper = upr_mpa_abco)
```

### Prop_ Ignite (5%)
```{r}
o_mod<-lme(prop_ignite_bins5_nodate~mpa + year_month + site, random=~1|id, data=abco_subset_seg)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#rsegplot_mpa(os_mod, abco_subset_seg, 'abco', y_variable = 'prop_ignite_bins5_nodate',y_lab = "Proportion Ignted (5% Bins of LFM)", tlp = mean_mpa_abco, tlp_lower = lwr_mpa_abco, tlp_upper = upr_mpa_abco)
```

### Glow to Ignition
```{r}
o_mod<-lme(gti~mpa + year_month + site, random=~1|id, data=abco_subset_seg)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#rsegplot_mpa(os_mod, abco_subset_seg, 'abco', y_variable = 'gti',y_lab = "Glow to Ignition (s)", tlp = mean_mpa_abco, tlp_lower = lwr_mpa_abco, tlp_upper = upr_mpa_abco)
```

Combustibility Metrics:
### Flame Height
```{r}
o_mod<-lme(fh~mpa + year_month + site, random=~1|id, data=abco_subset_seg)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#rsegplot_mpa(os_mod, abco_subset_seg, 'abco', y_variable = 'fh',y_lab = "Flame Height (cm)", tlp = mean_mpa_abco, tlp_lower = lwr_mpa_abco, tlp_upper = upr_mpa_abco)
```

# -------

#Split by Sampling Date


