---
title: "abco segmented regressions"
author: "Indra Boving & Joe Celebrezze"
date: "4/15/2021"
output: html_document
---

#Setup:
```{r}
knitr::opts_chunk$set(echo = TRUE)
#lots of extra here, but oh well___ 
library(ggplot2)
library(gapminder)
library(tidyverse)
library(lme4)
library(here)
library(segmented)
library(nlme)
#citation('nlme')
library(lubridate)
#install.packages("plotrix")
library(plotrix)
filter = dplyr::filter
here = here::here
select = dplyr::select
#source(here("source-code", "source-segmented_lme_R"))

# Function to plot mixed effects model segmented regressions:

source(here::here("scripts", "scripts_functions", "plot_segmented_MEM_V2.R"))
```

# Reading in Dataframe
```{r}
seg_data_subset <- read_csv(here("processed-data", "analysis 2.0", "sierra_flam_data_all.csv")) %>% 
  mutate(id = individual)
```

# Color by Season

```{r}
seg_data_subset$color <- "#ee8577"
seg_data_subset$color[seg_data_subset$year_month=='2020_october']="#ce4441"
seg_data_subset$color[seg_data_subset$year_month=='2020_september']="#c969a1"
seg_data_subset$color[seg_data_subset$year_month=='2021_august']="#ffbb44"
```

# Splitting by Species and by Sampling Date

```{r} 
seg_data_subset <- seg_data_subset %>% 
  mutate_if(is.character, str_to_lower) %>% 
  mutate(spp = str_trim(spp),
         rwc_scaled = scale(rwc),
    name = paste(spp,"_max", sep = ""), 
    name_subset = paste(spp, "_subset_seg", sep = ""), #this is def working. 
   # name_yearmonth = intersect(spp, year_month), 
    name_yearmonth = paste(spp, year_month, "subset_seg", sep = "_")) 

abco_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco")

abco_2020_oct_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month == "2020_october")

abco_2020_sept_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month == "2020_september")

abco_2020_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month %in% c("2020_september", "2020_october"))

abco_2021_aug_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month == "2021_august")

# seg_data_subset %>% 
#   group_split(spp) %>%
#   #rowwise() %>% 
#   setNames(unique(seg_data_subset$name_subset))  %>% #this is not working...wrong name for df. 
#   list2env(envir = globalenv())

# seg_data_subset %>% 
#   group_split(name_yearmonth) %>%
#   setNames(unique(seg_data_subset$name_yearmonth))  %>%
#   list2env(envir = globalenv())
```


# Maximums for rwc, MPa

```{r}
max_seg_data <- seg_data_subset %>% 
  type.convert(as.is = TRUE) %>% 
  select(mpa, rwc, spp) %>% 
  group_by(spp) %>% 
  summarise(across(where(is.numeric), max, .names = "max_{.col}")) 

abco_max_mpa <- max_seg_data %>% 
  filter(spp == "abco") %>% 
  select(max_mpa) %>% 
  pull()

abco_max_rwc <- max_seg_data %>% 
  filter(spp == "abco") %>% 
  select(max_rwc) %>% 
  pull()
```

# PV Curve Data


```{r}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"), show_col_types = FALSE) %>% 
   filter(timing == "fall") %>% 
  mutate_if(is.character, str_to_lower) %>% 
  #mutate_at(spp, str_to_lower) %>% 
  mutate(spp = str_trim(spp),
    name = paste(spp,"_pv", sep = ""), 
    mean_tlp = -1*mean_tlp, 
    lwr = -1*lwr, 
    upr = -1*upr) %>% 
  filter(!spp %in% c("ADFA", "CEME")) 
  

pv_summary_df_timing %>% 
  group_split(spp) %>%
   setNames(unique(pv_summary_df_timing$name)) %>%
  list2env(envir = globalenv())

mean_mpa_abco <- abco_pv %>% 
  select(mean_tlp) %>% 
  pull()

lwr_mpa_abco <- abco_pv %>% 
  select(lwr) %>% 
  pull()

upr_mpa_abco <- abco_pv %>% 
  select(upr) %>% 
  pull()

mean_rwc_abco <- abco_pv %>% 
  select(mean_lfm) %>% 
  pull()

lwr_rwc_abco <- abco_pv %>% 
  select(lwr_lfm) %>% 
  pull()

upr_rwc_abco <- abco_pv %>% 
  select(upr_lfm) %>% 
  pull()
```
# -------

#Summary visualizations:

```{r}
abco_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(year_month, location, tti, fh, fd, gd, temp_change, prop_ignite) %>%
  gather(-year_month, -location, key = "var", value = "value") %>%
  ggplot() +
  geom_density(aes(x = value, 
                   color = year_month, 
                   fill = year_month), 
               alpha = .4) +
  facet_wrap(~ var, scales = "free") 
```

```{r}
abco_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(year_month, year, location, tti, fh, fd, gd, temp_change, prop_ignite) %>%
  gather(-year_month, -location, -year, key = "var", value = "value") %>%
  ggplot() +
  geom_density(aes(x = value, 
                   color = as.factor(year), 
                   fill =  as.factor(year)),
               alpha = .4) +
  facet_wrap(~ var, scales = "free") 
```

```{r}
abco_cor <- abco_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(tti, fh, fd, gd, temp_change, prop_ignite, rwc, mpa) %>% 
  drop_na() %>% 
  cor()

corrplot::corrplot.mixed(abco_cor, order = 'AOE')
```


# -------

#Segmented regressions: 

We're just going to do a few metrics, to represent each of the axes: 

Ignitability: TTI, Prop.ignite

Combustibility: FH, Max Temp, Temp Change

Sustainability: FD, 

Consumability: GD

Maybe: Max temp

#rwc

###Holding vectors: this will be a df with all to collect results as we go: 

No random effects: 

```{r}
rwc_psi_tti <- c(rep(NaN, 1))
rwc_psi_fh <- c(rep(NaN, 1))
rwc_psi_fd <- c(rep(NaN, 1))
rwc_psi_gd <- c(rep(NaN, 1))
#rwc_psi_gti <- c(rep(NaN, 1))
#rwc_psi_rwc_pfg <- c(rep(NaN, 1))
#rwc_psi_ttfg <- c(rep(NaN, 1))
rwc_psi_fd <- c(rep(NaN, 1))
rwc_psi_prop_ignite <- c(rep(NaN, 1))
rwc_psi_temp_change <- c(rep(NaN, 1))

rwc_st_err_tti <- c(rep(NaN, 1))
rwc_st_err_fh <- c(rep(NaN, 1))
rwc_st_err_fd <- c(rep(NaN, 1))
rwc_st_err_gd <- c(rep(NaN, 1))
#rwc_st_err_gti <- c(rep(NaN, 1))
#rwc_st_err_rwc_pfg <- c(rep(NaN, 1))
#rwc_st_err_ttfg <- c(rep(NaN, 1))
rwc_st_err_fd <- c(rep(NaN, 1))
rwc_st_err_prop_ignite <- c(rep(NaN, 1))
rwc_st_err_temp_change <- c(rep(NaN, 1))

rwc_p_value_tti <- c(rep(NaN, 1))
rwc_p_value_fh <- c(rep(NaN, 1))
rwc_p_value_fd <- c(rep(NaN, 1))
rwc_p_value_gd <- c(rep(NaN, 1))
#rwc_p_value_gti <- c(rep(NaN, 1))
#rwc_p_value_rwc_pfg <- c(rep(NaN, 1))
#rwc_p_value_ttfg <- c(rep(NaN, 1))
rwc_p_value_fd <- c(rep(NaN, 1))
rwc_p_value_prop_ignite <- c(rep(NaN, 1))
rwc_p_value_temp_change <- c(rep(NaN, 1))

rwc_abco_thresholds_seg <- tibble::data_frame(rwc_psi_tti, rwc_st_err_tti, rwc_p_value_tti,
                              rwc_psi_fh, rwc_st_err_fh, rwc_p_value_fh,
                              rwc_psi_fd, rwc_st_err_fd,rwc_p_value_fd,
                              rwc_psi_gd, rwc_st_err_gd, rwc_p_value_gd, 
                              #rwc_psi_gti, rwc_st_err_gti, 
                              #rwc_psi_rwc_pfg, rwc_st_err_rwc_pfg, 
                              #rwc_psi_ttfg, rwc_st_err_ttfg,
                              rwc_psi_prop_ignite, rwc_st_err_prop_ignite, rwc_p_value_prop_ignite,
                              rwc_psi_temp_change, rwc_st_err_temp_change, rwc_p_value_temp_change
                              )
```


Randem effecs: 

```{r}
rwc_psi_tti <- c(rep(NaN, 1))
rwc_psi_fh <- c(rep(NaN, 1))
rwc_psi_fd <- c(rep(NaN, 1))
rwc_psi_gd <- c(rep(NaN, 1))
#rwc_psi_gti <- c(rep(NaN, 1))
#rwc_psi_rwc_pfg <- c(rep(NaN, 1))
#rwc_psi_ttfg <- c(rep(NaN, 1))
rwc_psi_fd <- c(rep(NaN, 1))
rwc_psi_prop_ignite <- c(rep(NaN, 1))
rwc_psi_temp_change <- c(rep(NaN, 1))

rwc_st_err_tti <- c(rep(NaN, 1))
rwc_st_err_fh <- c(rep(NaN, 1))
rwc_st_err_fd <- c(rep(NaN, 1))
rwc_st_err_gd <- c(rep(NaN, 1))
#rwc_st_err_gti <- c(rep(NaN, 1))
#rwc_st_err_rwc_pfg <- c(rep(NaN, 1))
#rwc_st_err_ttfg <- c(rep(NaN, 1))
rwc_st_err_fd <- c(rep(NaN, 1))
rwc_st_err_prop_ignite <- c(rep(NaN, 1))
rwc_st_err_temp_change <- c(rep(NaN, 1))

rwc_abco_thresholds_rand_seg <- tibble::data_frame(rwc_psi_tti, rwc_st_err_tti,
                              rwc_psi_fh, rwc_st_err_fh, 
                              rwc_psi_fd, rwc_st_err_fd,
                              rwc_psi_gd, rwc_st_err_gd, 
                              #rwc_psi_gti, rwc_st_err_gti, 
                              #rwc_psi_rwc_pfg, rwc_st_err_rwc_pfg, 
                              #rwc_psi_ttfg, rwc_st_err_ttfg,
                              rwc_psi_prop_ignite, rwc_st_err_prop_ignite, 
                              rwc_psi_temp_change, rwc_st_err_temp_change)
```


### Time to Ignition

```{r}
abco_subset_seg_tti <- abco_subset_seg %>%
  drop_na(tti, rwc)

#Segmented regression with random changepoints: 

o_mod<-lme(tti~rwc + year_month + site, random=~1|id, data=abco_subset_seg_tti)
os_mod_b<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_b)

#put into the df:
rwc_abco_thresholds_rand_seg[1] <- summary(os_mod_b)$psi[2]
rwc_abco_thresholds_rand_seg[2] <- summary(os_mod_b)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(tti~rwc + year_month + site, data = abco_subset_seg_tti)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_abco_thresholds_seg[1] <- summary(u_mod_b)$psi[2]
rwc_abco_thresholds_seg[2] <- summary(u_mod_b)$psi[3]
rwc_abco_thresholds_seg[3] <- u_mod_davies$p.value


#rsegplot.rwc(os_mod_b, abco_subset_seg_tti, max.x = abco_max_rwc, y.variable = 'tti', y.lab = "Time to Ignition (s)", tlp = mean_rwc_abco, tlp.lower = lwr_rwc_abco, tlp.upper = upr_rwc_abco)
```
Combustibility Metrics:

### Flame Height
```{r}
abco_subset_seg_fh <- abco_subset_seg %>% drop_na(fh) 

o_mod<-lme(fh~rwc + year_month + site, random=~1|id, data=abco_subset_seg_fh)
os_mod<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
rwc_abco_thresholds_rand_seg[3] <- summary(os_mod)$psi[2]
rwc_abco_thresholds_rand_seg[4] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fh~rwc + year_month + site, data = abco_subset_seg_fh)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_abco_thresholds_seg[4] <- summary(u_mod_b)$psi[2]
rwc_abco_thresholds_seg[5] <- summary(u_mod_b)$psi[3]
rwc_abco_thresholds_seg[6] <- u_mod_davies$p.value

#rsegplot.rwc(os_mod, abco_subset_seg_fh, max.x = abco_max_rwc, y.variable = 'fh', y.lab = "Flame Height (cm)", tlp = mean_rwc_abco, tlp.lower = lwr_rwc_abco, tlp.upper = upr_rwc_abco)
```

Sustainability Metrics:
### Flame Duration
```{r}
abco_subset_seg_fd <- abco_subset_seg %>% drop_na(fd)

o_mod<-lme(fd~rwc + year_month + site, random=~1|id, data=abco_subset_seg_fd)
os_mod <-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
rwc_abco_thresholds_rand_seg[5] <- summary(os_mod)$psi[2]
rwc_abco_thresholds_rand_seg[6] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fd~rwc + year_month + site, data = abco_subset_seg_fd)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_abco_thresholds_seg[7] <- summary(u_mod_b)$psi[2]
rwc_abco_thresholds_seg[8] <- summary(u_mod_b)$psi[3]
rwc_abco_thresholds_seg[9] <- u_mod_davies$p.value

#rsegplot.rwc(os_mod_f, abco_subset_seg_fd, max.x = abco_max_rwc, y.variable = 'fd', y.lab = "Flame Duration (s)", tlp = mean_rwc_abco, tlp.lower = lwr_rwc_abco, tlp.upper = upr_rwc_abco)
```

### glow Duration
```{r}
abco_subset_seg_gd <- abco_subset_seg %>% drop_na(gd)

o_mod<-lme(gd~rwc + year_month + site, random=~1|id, data=abco_subset_seg_gd)
os_mod <-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
rwc_abco_thresholds_rand_seg[7] <- summary(os_mod)$psi[2]
rwc_abco_thresholds_rand_seg[8] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(gd~rwc + year_month + site, data = abco_subset_seg_gd)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_abco_thresholds_seg[10] <- summary(u_mod_b)$psi[2]
rwc_abco_thresholds_seg[11] <- summary(u_mod_b)$psi[3]
rwc_abco_thresholds_seg[12] <- u_mod_davies$p.value

#rsegplot.rwc(os_mod, abco_subset_seg_gd, max.x = abco_max_rwc, y.variable = 'gd', y.lab = "Glow Duration (s)", tlp = mean_rwc_abco, tlp.lower = lwr_rwc_abco, tlp.upper = upr_rwc_abco)
```


### Prop. Ignite (5%)
```{r}
abco_subset_seg_prop_ignite <- abco_subset_seg %>% drop_na(prop_ignite)

o_mod<-lme(prop_ignite~rwc + year_month + site, random=~1|id, abco_subset_seg_prop_ignite )
os_mod<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
rwc_abco_thresholds_rand_seg[9] <- summary(os_mod)$psi[2]
rwc_abco_thresholds_rand_seg[10] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(prop_ignite~rwc + year_month + site, data = abco_subset_seg_prop_ignite)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_abco_thresholds_seg[13] <- summary(u_mod_b)$psi[2]
rwc_abco_thresholds_seg[14] <- summary(u_mod_b)$psi[3]
rwc_abco_thresholds_seg[15] <- u_mod_davies$p.value

#rsegplot.rwc(os_mod, abco_subset_seg_prop_ignite, max.x = abco_max_rwc, y.variable = 'prop_ignite', y.lab = "Proportion Ignted (5% Bins of rwc)", tlp = mean_rwc_abco, tlp.lower = lwr_rwc_abco, tlp.upper = upr_rwc_abco)
```

<!-- ### Glow to Ignition -->
<!-- ```{r} -->
<!-- abco_subset_seg_gti <- abco_subset_seg %>%  -->
<!--   drop_na(gti) -->

<!-- o_mod<-lme(gti~rwc + year_month + site, random=~1|id, data=abco_subset_seg_gti) -->
<!-- os_mod<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1)) -->
<!-- #summarizing results (note the '_coef' argument) -->
<!-- summary.segmented(os_mod) -->

<!-- #rsegplot.rwc(os_mod, abco_subset_seg_gti, max.x = abco_max_rwc, y.variable = 'gti', y.lab = "Glow to Ignition (s)", tlp = mean_rwc_abco, tlp.lower = lwr_rwc_abco, tlp.upper = upr_rwc_abco) -->
<!-- ``` -->



<!-- ### Max_ Temp_ -->
<!-- ```{r} -->
<!-- abco_subset_seg_lower_temp_max <- abco_subset_seg %>%  -->
<!--   drop_na(lower_temp_max) -->

<!-- o_mod<-lme(lower_temp_max~rwc + year_month + site, random=~1|id, data=abco_subset_seg_lower_temp_max) -->
<!-- os_mod<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1)) -->
<!-- #summarizing results (note the '_coef' argument) -->
<!-- summary.segmented(os_mod) -->
<!-- os_mod -->

<!-- #rsegplot.rwc(os_mod, abco_subset_seg_lower_temp_max, max.x = abco_max_rwc, y.variable = 'lower_temp_max', y.lab = "Maximum Temperature (C)", tlp = mean_rwc_abco, tlp.lower = lwr_rwc_abco, tlp.upper = upr_rwc_abco) -->
<!-- ``` -->


### Temp change: 

```{r}
abco_subset_seg_temp_change <- abco_subset_seg %>% 
  drop_na(temp_change)

o_mod<-lme(lower_temp_max~rwc + year_month + site, random=~1|id, data=abco_subset_seg_temp_change)
os_mod<-segmented.default(o_mod, ~rwc, npsi=list(rwc=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)
os_mod

#put into the df:
rwc_abco_thresholds_rand_seg[11] <- summary(os_mod)$psi[2]
rwc_abco_thresholds_rand_seg[12] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(temp_change~rwc + year_month + site, data = abco_subset_seg_temp_change)
u_mod_b <- segmented(u_mod, ~rwc)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
rwc_abco_thresholds_seg[16] <- summary(u_mod_b)$psi[2]
rwc_abco_thresholds_seg[17] <- summary(u_mod_b)$psi[3]
rwc_abco_thresholds_seg[18] <- u_mod_davies$p.value

#rsegplot.rwc(os_mod, abco_subset_seg_temp_change, max.x = abco_max_rwc, y.variable = 'temp_change', y.lab = "Temp Change (C)", tlp = mean_rwc_abco, tlp.lower = lwr_rwc_abco, tlp.upper = upr_rwc_abco)
```
#rwc: FInal table: 


```{r}
#No random effects: 
abco_rwc_summary_df <- rwc_abco_thresholds_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'rwc_', ''),
         across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "segmented") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
abco_rwc_summary_df

#with random effects: 
abco_rwc_rand_summary_df <- rwc_abco_thresholds_rand_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'rwc_', ''),
         across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "random") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
abco_rwc_rand_summary_df

abco_rwc <- bind_rows(abco_rwc_rand_summary_df, abco_rwc_summary_df) %>% 
  mutate(spp = "abco", 
         water_variable = "rwc") 

#ggsave(plot=gridExtra::tableGrob(abco_rwc), filename=here("figures", "segmented_tables", "rand_segmented_rwc_abco.png"))
```



# -------

#MPa

###Holding vectors: this will be a df with all to collect results as we go: 

No random effects: 

```{r}
mpa_psi_tti <- c(rep(NaN, 1))
mpa_psi_fh <- c(rep(NaN, 1))
mpa_psi_fd <- c(rep(NaN, 1))
mpa_psi_gd <- c(rep(NaN, 1))
#mpa_psi_gti <- c(rep(NaN, 1))
#mpa_psi_mpa_pfg <- c(rep(NaN, 1))
#mpa_psi_ttfg <- c(rep(NaN, 1))
mpa_psi_fd <- c(rep(NaN, 1))
mpa_psi_prop_ignite <- c(rep(NaN, 1))
mpa_psi_temp_change <- c(rep(NaN, 1))

mpa_st_err_tti <- c(rep(NaN, 1))
mpa_st_err_fh <- c(rep(NaN, 1))
mpa_st_err_fd <- c(rep(NaN, 1))
mpa_st_err_gd <- c(rep(NaN, 1))
#mpa_st_err_gti <- c(rep(NaN, 1))
#mpa_st_err_mpa_pfg <- c(rep(NaN, 1))
#mpa_st_err_ttfg <- c(rep(NaN, 1))
mpa_st_err_fd <- c(rep(NaN, 1))
mpa_st_err_prop_ignite <- c(rep(NaN, 1))
mpa_st_err_temp_change <- c(rep(NaN, 1))

mpa_p_value_tti <- c(rep(NaN, 1))
mpa_p_value_fh <- c(rep(NaN, 1))
mpa_p_value_fd <- c(rep(NaN, 1))
mpa_p_value_gd <- c(rep(NaN, 1))
#mpa_p_value_gti <- c(rep(NaN, 1))
#mpa_p_value_mpa_pfg <- c(rep(NaN, 1))
#mpa_p_value_ttfg <- c(rep(NaN, 1))
mpa_p_value_fd <- c(rep(NaN, 1))
mpa_p_value_prop_ignite <- c(rep(NaN, 1))
mpa_p_value_temp_change <- c(rep(NaN, 1))

mpa_abco_thresholds_seg <- tibble::data_frame(mpa_psi_tti, mpa_st_err_tti, mpa_p_value_tti,
                              mpa_psi_fh, mpa_st_err_fh, mpa_p_value_fh,
                              mpa_psi_fd, mpa_st_err_fd,mpa_p_value_fd,
                              mpa_psi_gd, mpa_st_err_gd, mpa_p_value_gd, 
                              #mpa_psi_gti, mpa_st_err_gti, 
                              #mpa_psi_mpa_pfg, mpa_st_err_mpa_pfg, 
                              #mpa_psi_ttfg, mpa_st_err_ttfg,
                              mpa_psi_prop_ignite, mpa_st_err_prop_ignite, mpa_p_value_prop_ignite,
                              mpa_psi_temp_change, mpa_st_err_temp_change, mpa_p_value_temp_change
                              )
```


Randem effecs: 

```{r}
mpa_psi_tti <- c(rep(NaN, 1))
mpa_psi_fh <- c(rep(NaN, 1))
mpa_psi_fd <- c(rep(NaN, 1))
mpa_psi_gd <- c(rep(NaN, 1))
#mpa_psi_gti <- c(rep(NaN, 1))
#mpa_psi_mpa_pfg <- c(rep(NaN, 1))
#mpa_psi_ttfg <- c(rep(NaN, 1))
mpa_psi_fd <- c(rep(NaN, 1))
mpa_psi_prop_ignite <- c(rep(NaN, 1))
mpa_psi_temp_change <- c(rep(NaN, 1))

mpa_st_err_tti <- c(rep(NaN, 1))
mpa_st_err_fh <- c(rep(NaN, 1))
mpa_st_err_fd <- c(rep(NaN, 1))
mpa_st_err_gd <- c(rep(NaN, 1))
#mpa_st_err_gti <- c(rep(NaN, 1))
#mpa_st_err_mpa_pfg <- c(rep(NaN, 1))
#mpa_st_err_ttfg <- c(rep(NaN, 1))
mpa_st_err_fd <- c(rep(NaN, 1))
mpa_st_err_prop_ignite <- c(rep(NaN, 1))
mpa_st_err_temp_change <- c(rep(NaN, 1))

mpa_abco_thresholds_rand_seg <- tibble::data_frame(mpa_psi_tti, mpa_st_err_tti,
                              mpa_psi_fh, mpa_st_err_fh, 
                              mpa_psi_fd, mpa_st_err_fd,
                              mpa_psi_gd, mpa_st_err_gd, 
                              #mpa_psi_gti, mpa_st_err_gti, 
                              #mpa_psi_mpa_pfg, mpa_st_err_mpa_pfg, 
                              #mpa_psi_ttfg, mpa_st_err_ttfg,
                              mpa_psi_prop_ignite, mpa_st_err_prop_ignite, 
                              mpa_psi_temp_change, mpa_st_err_temp_change)
```


### Time to Ignition

```{r}
abco_subset_seg_tti <- abco_subset_seg %>%
  drop_na(tti)

#Segmented regression with random changepoints: 

o_mod<-lme(tti~mpa + year_month + site, random=~1|id, data=abco_subset_seg_tti)
os_mod_b<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_b)

#put into the df:
mpa_abco_thresholds_rand_seg[1] <- summary(os_mod_b)$psi[2]
mpa_abco_thresholds_rand_seg[2] <- summary(os_mod_b)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(tti~mpa + year_month + site, data = abco_subset_seg_tti)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[1] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[2] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[3] <- u_mod_davies$p.value


#rsegplot.mpa(os_mod_b, abco_subset_seg_tti, max.x = abco_max_mpa, y.variable = 'tti', y.lab = "Time to Ignition (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```
Combustibility Metrics:

### Flame Height
```{r}
abco_subset_seg_fh <- abco_subset_seg %>% drop_na(fh) 

o_mod<-lme(fh~mpa + year_month + site, random=~1|id, data=abco_subset_seg_fh)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
mpa_abco_thresholds_rand_seg[3] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[4] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fh~mpa + year_month + site, data = abco_subset_seg_fh)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[4] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[5] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[6] <- u_mod_davies$p.value

#rsegplot.mpa(os_mod, abco_subset_seg_fh, max.x = abco_max_mpa, y.variable = 'fh', y.lab = "Flame Height (cm)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)

```

Sustainability Metrics:
### Flame Duration
```{r}
abco_subset_seg_fd <- abco_subset_seg %>% drop_na(fd)

o_mod<-lme(fd~mpa + year_month + site, random=~1|id, data=abco_subset_seg_fd)
os_mod <-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
mpa_abco_thresholds_rand_seg[5] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[6] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fd~mpa + year_month + site, data = abco_subset_seg_fd)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[7] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[8] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[9] <- u_mod_davies$p.value

#rsegplot.mpa(os_mod, abco_subset_seg_fd, max.x = abco_max_mpa, y.variable = 'fd', y.lab = "Flame Duration (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```

### glow Duration
```{r}
abco_subset_seg_gd <- abco_subset_seg %>% drop_na(gd)

o_mod<-lme(gd~mpa + year_month + site, random=~1|id, data=abco_subset_seg_gd)
os_mod <-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
mpa_abco_thresholds_rand_seg[7] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[8] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(gd~mpa + year_month + site, data = abco_subset_seg_gd)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[10] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[11] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[12] <- u_mod_davies$p.value

#rsegplot.mpa(os_mod, abco_subset_seg_gd, max.x = abco_max_mpa, y.variable = 'gd', y.lab = "Glow Duration (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```


### Prop. Ignite (5%)
```{r}
abco_subset_seg_prop_ignite <- abco_subset_seg %>% drop_na(prop_ignite)

o_mod<-lme(prop_ignite~mpa + year_month + site, random=~1|id, abco_subset_seg_prop_ignite )
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
mpa_abco_thresholds_rand_seg[9] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[10] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(prop_ignite~mpa + year_month + site, data = abco_subset_seg_prop_ignite)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[13] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[14] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[15] <- u_mod_davies$p.value

#rsegplot.mpa(os_mod, abco_subset_seg_prop_ignite, max.x = abco_max_mpa, y.variable = 'prop_ignite', y.lab = "Proportion Ignted (5% Bins of mpa)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```

<!-- ### Glow to Ignition -->
<!-- ```{r} -->
<!-- abco_subset_seg_gti <- abco_subset_seg %>%  -->
<!--   drop_na(gti) -->

<!-- o_mod<-lme(gti~mpa + year_month + site, random=~1|id, data=abco_subset_seg_gti) -->
<!-- os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1)) -->
<!-- #summarizing results (note the '_coef' argument) -->
<!-- summary.segmented(os_mod) -->

<!-- #rsegplot.mpa(os_mod, abco_subset_seg_gti, max.x = abco_max_mpa, y.variable = 'gti', y.lab = "Glow to Ignition (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco) -->
<!-- ``` -->



<!-- ### Max_ Temp_ -->
<!-- ```{r} -->
<!-- abco_subset_seg_lower_temp_max <- abco_subset_seg %>%  -->
<!--   drop_na(lower_temp_max) -->

<!-- o_mod<-lme(lower_temp_max~mpa + year_month + site, random=~1|id, data=abco_subset_seg_lower_temp_max) -->
<!-- os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1)) -->
<!-- #summarizing results (note the '_coef' argument) -->
<!-- summary.segmented(os_mod) -->
<!-- os_mod -->

<!-- #rsegplot.mpa(os_mod, abco_subset_seg_lower_temp_max, max.x = abco_max_mpa, y.variable = 'lower_temp_max', y.lab = "Maximum Temperature (C)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco) -->
<!-- ``` -->


### Temp change: 

```{r}
abco_subset_seg_temp_change <- abco_subset_seg %>% 
  drop_na(temp_change)

o_mod<-lme(lower_temp_max~mpa + year_month + site, random=~1|id, data=abco_subset_seg_temp_change)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)
os_mod

#put into the df:
mpa_abco_thresholds_rand_seg[11] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[12] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(temp_change~mpa + year_month + site, data = abco_subset_seg_temp_change)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[16] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[17] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[18] <- u_mod_davies$p.value

#rsegplot.mpa(os_mod, abco_subset_seg_temp_change, max.x = abco_max_mpa, y.variable = 'temp_change', y.lab = "Temp Change (C)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```
#mpa: FInal table: 


```{r}
#No random effects: 
abco_mpa_summary_df <- mpa_abco_thresholds_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'mpa_', ''),
        across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "segmented") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
abco_mpa_summary_df

#with random effects: 
abco_mpa_rand_summary_df <- mpa_abco_thresholds_rand_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'mpa_', ''),
        across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "random") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
abco_mpa_rand_summary_df

abco_mpa <- bind_rows(abco_mpa_rand_summary_df, abco_mpa_summary_df) %>% 
  mutate(spp = "abco", 
         water_variable = "mpa") 

#ggsave(plot=gridExtra::tableGrob(abco_mpa), filename=here("figures", "segmented_tables", "rand_segmented_mpa_abco.png"))
```


#------------

#All together now:

```{r}
abco_all_segmented <- bind_rows(abco_rwc, abco_mpa)

abco_all_segmented_wide <- abco_all_segmented %>% 
  mutate(across('statistic', str_replace, ' ', '_')) %>% 
  pivot_wider(names_from = statistic, 
              values_from = value)

write_csv(abco_all_segmented_wide, 
          here::here("processed-data", "analysis 2.0", "segmented_reg_all", "abco_all_segmented_wide_rwc.csv"))
```

#Visualize: 

```{r}
abco_all_segmented_wide %>% 
  #filter(statistic == "psi") %>% 
  ggplot(aes(
    y = psi, 
    x = flam_metric,
    color = analysis, 
   # size = p_value
  )) +
  geom_point() +
  facet_wrap(~water_variable,scales = "free")
```


