---
title: "abco segmented regressions"
author: "Indra Boving & Joe Celebrezze"
date: "4/15/2021"
output: html_document
---

#Setup:
```{r}
knitr::opts_chunk$set(echo = TRUE)
#lots of extra here, but oh well___ 
library(ggplot2)
library(gapminder)
library(tidyverse)
library(lme4)
library(here)
library(segmented)
library(nlme)
#citation('nlme')
library(lubridate)
#install.packages("plotrix")
library(plotrix)
filter = dplyr::filter
here = here::here
select = dplyr::select
#source(here("source-code", "source-segmented_lme_R"))

# Function to plot mixed effects model segmented regressions:

source(here::here("scripts", "scripts_functions", "plot_segmented_MEM_V2.R"))
```

# Reading in Dataframe
```{r}
seg_data_subset <- read_csv(here("processed-data", "analysis 2.0", "sierra_flam_data_all.csv")) %>% 
  mutate(id = individual)
```

# Color by Season

```{r}
seg_data_subset$color <- "#ee8577"
seg_data_subset$color[seg_data_subset$year_month=='2020_october']="#ce4441"
seg_data_subset$color[seg_data_subset$year_month=='2020_september']="#c969a1"
seg_data_subset$color[seg_data_subset$year_month=='2021_august']="#ffbb44"
```

# Splitting by Species and by Sampling Date

```{r} 
seg_data_subset <- seg_data_subset %>% 
  mutate_if(is.character, str_to_lower) %>% 
  mutate(spp = str_trim(spp),
         lfm_scaled = scale(lfm),
    name = paste(spp,"_max", sep = ""), 
    name_subset = paste(spp, "_subset_seg", sep = ""), #this is def working. 
   # name_yearmonth = intersect(spp, year_month), 
    name_yearmonth = paste(spp, year_month, "subset_seg", sep = "_")) 

abco_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco")

abco_2020_oct_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month == "2020_october")

abco_2020_sept_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month == "2020_september")

abco_2020_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month %in% c("2020_september", "2020_october"))

abco_2021_aug_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month == "2021_august")

# seg_data_subset %>% 
#   group_split(spp) %>%
#   #rowwise() %>% 
#   setNames(unique(seg_data_subset$name_subset))  %>% #this is not working...wrong name for df. 
#   list2env(envir = globalenv())

# seg_data_subset %>% 
#   group_split(name_yearmonth) %>%
#   setNames(unique(seg_data_subset$name_yearmonth))  %>%
#   list2env(envir = globalenv())
```


# Maximums for LFM, MPa

```{r}
max_seg_data <- seg_data_subset %>% 
  type.convert(as.is = TRUE) %>% 
  select(mpa, lfm, spp) %>% 
  group_by(spp) %>% 
  summarise(across(where(is.numeric), max, .names = "max_{.col}")) 

abco_max_mpa <- max_seg_data %>% 
  filter(spp == "abco") %>% 
  select(max_mpa) %>% 
  pull()

abco_max_lfm <- max_seg_data %>% 
  filter(spp == "abco") %>% 
  select(max_lfm) %>% 
  pull()
```

# PV Curve Data


```{r}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"), show_col_types = FALSE) %>% 
   filter(timing == "fall") %>% 
  mutate_if(is.character, str_to_lower) %>% 
  #mutate_at(spp, str_to_lower) %>% 
  mutate(spp = str_trim(spp),
    name = paste(spp,"_pv", sep = ""), 
    mean_tlp = -1*mean_tlp, 
    lwr = -1*lwr, 
    upr = -1*upr) %>% 
  filter(!spp %in% c("ADFA", "CEME")) 
  

pv_summary_df_timing %>% 
  group_split(spp) %>%
   setNames(unique(pv_summary_df_timing$name)) %>%
  list2env(envir = globalenv())

mean_mpa_abco <- abco_pv %>% 
  select(mean_tlp) %>% 
  pull()

lwr_mpa_abco <- abco_pv %>% 
  select(lwr) %>% 
  pull()

upr_mpa_abco <- abco_pv %>% 
  select(upr) %>% 
  pull()

mean_lfm_abco <- abco_pv %>% 
  select(mean_lfm) %>% 
  pull()

lwr_lfm_abco <- abco_pv %>% 
  select(lwr_lfm) %>% 
  pull()

upr_lfm_abco <- abco_pv %>% 
  select(upr_lfm) %>% 
  pull()
```
# -------

#Summary visualizations:

```{r}
abco_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(year_month, location, tti, fh, fd, gd, temp_change, prop_ignite) %>%
  gather(-year_month, -location, key = "var", value = "value") %>%
  ggplot() +
  geom_density(aes(x = value, 
                   color = year_month, 
                   fill = year_month), 
               alpha = .4) +
  facet_wrap(~ var, scales = "free") 
```

```{r}
abco_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(year_month, year, location, tti, fh, fd, gd, temp_change, prop_ignite) %>%
  gather(-year_month, -location, -year, key = "var", value = "value") %>%
  ggplot() +
  geom_density(aes(x = value, 
                   color = as.factor(year), 
                   fill =  as.factor(year)),
               alpha = .4) +
  facet_wrap(~ var, scales = "free") 
```

```{r}
abco_cor <- abco_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(tti, fh, fd, gd, temp_change, prop_ignite, lfm, mpa) %>% 
  drop_na() %>% 
  cor()

corrplot::corrplot.mixed(abco_cor, order = 'AOE')
```


# -------

#Segmented regressions: 

We're just going to do a few metrics, to represent each of the axes: 

Ignitability: TTI, Prop.ignite

Combustibility: FH, Max Temp, Temp Change

Sustainability: FD, 

Consumability: GD

Maybe: Max temp

## LFM

Ignitability Metrics:

### Time to Ignition

```{r}
abco_subset_seg_tti <- abco_subset_seg %>%
  drop_na(tti)

o_mod<-lme(tti~lfm + year_month + site, random=~1|id, data=abco_subset_seg_tti)
os_mod_b<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_b)

u_mod <- lm(tti~lfm + year_month + site, data = abco_subset_seg_tti)
u_mod_b <- segmented(u_mod, ~lfm)
davies.test(u_mod_b)
summary.segmented(u_mod_b)

rsegplot.lfm(os_mod_b, abco_subset_seg_tti, max.x = abco_max_lfm, y.variable = 'tti', y.lab = "Time to Ignition (s)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```


### Prop. Ignite (5%)
```{r}
abco_subset_seg_prop_ignite <- abco_subset_seg %>% drop_na(prop_ignite)

o_mod<-lme(prop_ignite~lfm + year_month + site, random=~1|id, abco_subset_seg_prop_ignite )
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

rsegplot.lfm(os_mod, abco_subset_seg_prop_ignite, max.x = abco_max_lfm, y.variable = 'prop_ignite', y.lab = "Proportion Ignted (5% Bins of LFM)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```

### Glow to Ignition
```{r}
abco_subset_seg_gti <- abco_subset_seg %>% 
  drop_na(gti)

o_mod<-lme(gti~lfm + year_month + site, random=~1|id, data=abco_subset_seg_gti)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

rsegplot.lfm(os_mod, abco_subset_seg_gti, max.x = abco_max_lfm, y.variable = 'gti', y.lab = "Glow to Ignition (s)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```

Combustibility Metrics:

### Flame Height
```{r}
abco_subset_seg_fh <- abco_subset_seg %>% drop_na(fh) 

o_mod<-lme(fh~lfm + year_month + site, random=~1|id, data=abco_subset_seg_fh)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

rsegplot.lfm(os_mod, abco_subset_seg_fh, max.x = abco_max_lfm, y.variable = 'fh', y.lab = "Flame Height (cm)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```

### Max_ Temp_
```{r}
abco_subset_seg_lower_temp_max <- abco_subset_seg %>% 
  drop_na(lower_temp_max)

o_mod<-lme(lower_temp_max~lfm + year_month + site, random=~1|id, data=abco_subset_seg_lower_temp_max)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)
os_mod

rsegplot.lfm(os_mod, abco_subset_seg_lower_temp_max, max.x = abco_max_lfm, y.variable = 'lower_temp_max', y.lab = "Maximum Temperature (C)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```
### Max_ Temp_
```{r}
abco_subset_seg_temp_change <- abco_subset_seg %>% 
  drop_na(temp_change)

o_mod<-lme(lower_temp_max~lfm + year_month + site, random=~1|id, data=abco_subset_seg_temp_change)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)
os_mod

rsegplot.lfm(os_mod, abco_subset_seg_temp_change, max.x = abco_max_lfm, y.variable = 'lower_temp_max', y.lab = "Maximum Temperature (C)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```

Sustainability Metrics:
### Flame Duration
```{r}
abco_subset_seg_fd <- abco_subset_seg %>% drop_na(fd)

o_mod<-lme(fd~lfm + year_month + site, random=~1|id, data=abco_subset_seg_fd)
os_mod_f<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_f)

rsegplot.lfm(os_mod_f, abco_subset_seg_fd, max.x = abco_max_lfm, y.variable = 'fd', y.lab = "Flame Duration (s)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```


# -------


## Water Potential
```{r}
abco_subset_seg <- abco_subset_seg %>% 
  mutate(mpa_scaled = scale(mpa))
```


 
Ignitability Metrics:

### Time to Ignition
```{r}
o_mod<-lme(tti~mpa + year_month + site, random=~1|id, data=abco_subset_seg_tti)
os_mod_b1<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_b1)

rsegplot.mpa(os_mod_b1, abco_subset_seg_tti, max.x = abco_max_mpa, y.variable = 'tti', y.lab = "Time to Ignition (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```

### Prop_ Ignite (5%)
```{r}
abco_subset_seg_prop_ignite

o_mod<-lme(prop_ignite~mpa + year_month + site, random=~1|id, data=abco_subset_seg_prop_ignite)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

rsegplot.mpa(os_mod, abco_subset_seg_prop_ignite, max.x = abco_max_mpa, y.variable = 'prop_ignite', y.lab = "Proportion Ignted (5% Bins of mpa)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```

### Glow to Ignition
```{r}
abco_subset_seg_gti <- abco_subset_seg_gti %>% 
  filter(gti < 50, 
         gti > 0)

o_mod<-lme(gti~mpa + year_month + site, random=~1|id, data=abco_subset_seg_gti)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

rsegplot.mpa(os_mod, abco_subset_seg_gti, max.x = abco_max_mpa, y.variable = 'gti', y.lab = "Glow to Ignition (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```

### Temp Max
```{r}

o_mod<-lme(lower_temp_max~mpa + year_month + site, random=~1|id, abco_subset_seg_lower_temp_max)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

rsegplot.mpa(os_mod, abco_subset_seg_lower_temp_max, max.x = abco_max_mpa, y.variable = 'lower_temp_max', y.lab = "Lower Temp Max (C)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```

Combustibility Metrics:
### Flame Height
```{r}
o_mod<-lme(fh~mpa + year_month + site, random=~1|id, data=abco_subset_seg_fh)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

rsegplot.mpa(os_mod, abco_subset_seg_fh, max.x = abco_max_mpa, y.variable = 'fh', y.lab = "Flame Height (cm)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```

### Flame Duration
```{r}
o_mod<-lme(fd~mpa + year_month + site, random=~1|id, data=abco_subset_seg_fd)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

rsegplot.mpa(os_mod, abco_subset_seg_fd, max.x = abco_max_mpa, y.variable = 'fd', y.lab = "Flame Duration (sec)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```
# -------

#Split by Sampling Date


