---
title: "abco segmented regressions"
author: "Indra Boving & Joe Celebrezze"
date: "4/15/2021"
output: html_document
---

#NOTES: 
This is a markdown that we can use to to run segmented regessions on individual species, by finding and replacing one lowercase spp code (e.g. "abco" in this doc) witn another lowercase spp code. 
 
The existing models include year_month and site (i.e. site 1 or 2 at either CZO or SEKI)and either LFM or MPa respectively. 

Could try: 
Having lfm and mpa in the same model 
Adding sample weight
Removing Aug 2021 sample date, which is what we do in the MEMs
Running with RWC instead of LFM. (started spp_rwc.Rmd code for that, but did not get far)

If making big changes, I'd suggest starting a new markdown and then adding model changes in bulk (i.e. find '+ site +' and replace with '+ site + sample_wt') to add sample weight. 


#Setup:
```{r}
knitr::opts_chunk$set(echo = TRUE)
#lots of extra here, but oh well___ 
library(ggplot2)
library(gapminder)
library(tidyverse)
library(lme4)
library(here)
library(segmented)
library(nlme)
library(lubridate)
library(plotrix)
filter = dplyr::filter
here = here::here
select = dplyr::select

# Function to plot mixed effects model segmented regressions:
source(here::here("scripts", "scripts_functions", "plot_segmented_MEM_V2.R"))
```

# Reading in Dataframe
```{r}
seg_data_subset <- read_csv(here("processed-data", "analysis 2.0", "sierra_flam_data_all.csv")) %>% 
  mutate(id = individual)
```

# Color by Season

```{r}
seg_data_subset$color <- "#ee8577"
seg_data_subset$color[seg_data_subset$year_month=='2020_october']="#ce4441"
seg_data_subset$color[seg_data_subset$year_month=='2020_september']="#c969a1"
seg_data_subset$color[seg_data_subset$year_month=='2021_august']="#ffbb44"
```

# Splitting by Species and by Sampling Date

```{r} 
seg_data_subset <- seg_data_subset %>% 
  mutate_if(is.character, str_to_lower) %>% 
  mutate(spp = str_trim(spp),
         lfm_scaled = scale(lfm),
    name = paste(spp,"_max", sep = ""), 
    name_subset = paste(spp, "_subset_seg", sep = ""), #this is def working. 
   # name_yearmonth = intersect(spp, year_month), 
    name_yearmonth = paste(spp, year_month, "subset_seg", sep = "_")) %>% 
  drop_na(lfm, mpa) #Dropping NA values for both LFM and mpa

abco_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco")

abco_2020_oct_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month == "2020_october")

abco_2020_sept_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month == "2020_september")

abco_2020_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month %in% c("2020_september", "2020_october"))

abco_2021_aug_subset_seg <- seg_data_subset %>% 
  filter(spp == "abco", 
         year_month == "2021_august")

# seg_data_subset %>% 
#   group_split(spp) %>%
#   #rowwise() %>% 
#   setNames(unique(seg_data_subset$name_subset))  %>% #this is not working...wrong name for df. 
#   list2env(envir = globalenv())

# seg_data_subset %>% 
#   group_split(name_yearmonth) %>%
#   setNames(unique(seg_data_subset$name_yearmonth))  %>%
#   list2env(envir = globalenv())
```


# Maximums for LFM, MPa

```{r}
max_seg_data <- seg_data_subset %>% 
  type.convert(as.is = TRUE) %>% 
  select(mpa, lfm, spp) %>% 
  group_by(spp) %>% 
  summarise(across(where(is.numeric), max, .names = "max_{.col}")) 

abco_max_mpa <- max_seg_data %>% 
  filter(spp == "abco") %>% 
  select(max_mpa) %>% 
  pull()

abco_max_lfm <- max_seg_data %>% 
  filter(spp == "abco") %>% 
  select(max_lfm) %>% 
  pull()
```

# PV Curve Data


```{r}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"), show_col_types = FALSE) %>% 
   filter(timing == "fall") %>% 
  mutate_if(is.character, str_to_lower) %>% 
  #mutate_at(spp, str_to_lower) %>% 
  mutate(spp = str_trim(spp),
    name = paste(spp,"_pv", sep = ""), 
    mean_tlp = -1*mean_tlp, 
    lwr = -1*lwr, 
    upr = -1*upr) %>% 
  filter(!spp %in% c("ADFA", "CEME")) 
  

pv_summary_df_timing %>% 
  group_split(spp) %>%
   setNames(unique(pv_summary_df_timing$name)) %>%
  list2env(envir = globalenv())

mean_mpa_abco <- abco_pv %>% 
  select(mean_tlp) %>% 
  pull()

lwr_mpa_abco <- abco_pv %>% 
  select(lwr) %>% 
  pull()

upr_mpa_abco <- abco_pv %>% 
  select(upr) %>% 
  pull()

mean_lfm_abco <- abco_pv %>% 
  select(mean_lfm) %>% 
  pull()

lwr_lfm_abco <- abco_pv %>% 
  select(lwr_lfm) %>% 
  pull()

upr_lfm_abco <- abco_pv %>% 
  select(upr_lfm) %>% 
  pull()
```
# -------

#Summary visualizations:

```{r}
abco_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(year_month, location, tti, fh, fd, gd, temp_change, prop_ignite) %>%
  gather(-year_month, -location, key = "var", value = "value") %>%
  ggplot() +
  geom_density(aes(x = value, 
                   color = year_month, 
                   fill = year_month), 
               alpha = .4) +
  facet_wrap(~ var, scales = "free") 
```

```{r}
abco_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(year_month, year, location, tti, fh, fd, gd, temp_change, prop_ignite) %>%
  gather(-year_month, -location, -year, key = "var", value = "value") %>%
  ggplot() +
  geom_density(aes(x = value, 
                   color = as.factor(year), 
                   fill =  as.factor(year)),
               alpha = .4) +
  facet_wrap(~ var, scales = "free") 
```

```{r}
abco_cor <- abco_subset_seg %>% 
  filter(ignition == 1) %>% 
  select(tti, fh, fd, gd, temp_change, prop_ignite, lfm, mpa) %>% 
  drop_na() %>% 
  cor()

corrplot::corrplot.mixed(abco_cor, order = 'AOE')
```


# -------

#Segmented regressions: 

We're just going to do a few metrics, to represent each of the axes: 

Ignitability: TTI, Prop.ignite

Combustibility: FH, Max Temp, Temp Change

Sustainability: FD, 

Consumability: GD

Maybe: Max temp

#LFM

###Holding vectors: this will be a df with all to collect results as we go: 

No random effects: 

```{r}
lfm_psi_tti <- c(rep(NaN, 1))
lfm_psi_fh <- c(rep(NaN, 1))
lfm_psi_fd <- c(rep(NaN, 1))
lfm_psi_gd <- c(rep(NaN, 1))
#lfm_psi_gti <- c(rep(NaN, 1))
#lfm_psi_lfm_pfg <- c(rep(NaN, 1))
#lfm_psi_ttfg <- c(rep(NaN, 1))
lfm_psi_fd <- c(rep(NaN, 1))
lfm_psi_prop_ignite <- c(rep(NaN, 1))
lfm_psi_temp_change <- c(rep(NaN, 1))

lfm_st_err_tti <- c(rep(NaN, 1))
lfm_st_err_fh <- c(rep(NaN, 1))
lfm_st_err_fd <- c(rep(NaN, 1))
lfm_st_err_gd <- c(rep(NaN, 1))
#lfm_st_err_gti <- c(rep(NaN, 1))
#lfm_st_err_lfm_pfg <- c(rep(NaN, 1))
#lfm_st_err_ttfg <- c(rep(NaN, 1))
lfm_st_err_fd <- c(rep(NaN, 1))
lfm_st_err_prop_ignite <- c(rep(NaN, 1))
lfm_st_err_temp_change <- c(rep(NaN, 1))

lfm_p_value_tti <- c(rep(NaN, 1))
lfm_p_value_fh <- c(rep(NaN, 1))
lfm_p_value_fd <- c(rep(NaN, 1))
lfm_p_value_gd <- c(rep(NaN, 1))
#lfm_p_value_gti <- c(rep(NaN, 1))
#lfm_p_value_lfm_pfg <- c(rep(NaN, 1))
#lfm_p_value_ttfg <- c(rep(NaN, 1))
lfm_p_value_fd <- c(rep(NaN, 1))
lfm_p_value_prop_ignite <- c(rep(NaN, 1))
lfm_p_value_temp_change <- c(rep(NaN, 1))

lfm_abco_thresholds_seg <- tibble::data_frame(lfm_psi_tti, lfm_st_err_tti, lfm_p_value_tti,
                              lfm_psi_fh, lfm_st_err_fh, lfm_p_value_fh,
                              lfm_psi_fd, lfm_st_err_fd,lfm_p_value_fd,
                              lfm_psi_gd, lfm_st_err_gd, lfm_p_value_gd, 
                              #lfm_psi_gti, lfm_st_err_gti, 
                              #lfm_psi_lfm_pfg, lfm_st_err_lfm_pfg, 
                              #lfm_psi_ttfg, lfm_st_err_ttfg,
                              lfm_psi_prop_ignite, lfm_st_err_prop_ignite, lfm_p_value_prop_ignite,
                              lfm_psi_temp_change, lfm_st_err_temp_change, lfm_p_value_temp_change
                              )
```


Randem effecs: 

```{r}
lfm_psi_tti <- c(rep(NaN, 1))
lfm_psi_fh <- c(rep(NaN, 1))
lfm_psi_fd <- c(rep(NaN, 1))
lfm_psi_gd <- c(rep(NaN, 1))
#lfm_psi_gti <- c(rep(NaN, 1))
#lfm_psi_lfm_pfg <- c(rep(NaN, 1))
#lfm_psi_ttfg <- c(rep(NaN, 1))
lfm_psi_fd <- c(rep(NaN, 1))
lfm_psi_prop_ignite <- c(rep(NaN, 1))
lfm_psi_temp_change <- c(rep(NaN, 1))

lfm_st_err_tti <- c(rep(NaN, 1))
lfm_st_err_fh <- c(rep(NaN, 1))
lfm_st_err_fd <- c(rep(NaN, 1))
lfm_st_err_gd <- c(rep(NaN, 1))
#lfm_st_err_gti <- c(rep(NaN, 1))
#lfm_st_err_lfm_pfg <- c(rep(NaN, 1))
#lfm_st_err_ttfg <- c(rep(NaN, 1))
lfm_st_err_fd <- c(rep(NaN, 1))
lfm_st_err_prop_ignite <- c(rep(NaN, 1))
lfm_st_err_temp_change <- c(rep(NaN, 1))

lfm_abco_thresholds_rand_seg <- tibble::data_frame(lfm_psi_tti, lfm_st_err_tti,
                              lfm_psi_fh, lfm_st_err_fh, 
                              lfm_psi_fd, lfm_st_err_fd,
                              lfm_psi_gd, lfm_st_err_gd, 
                              #lfm_psi_gti, lfm_st_err_gti, 
                              #lfm_psi_lfm_pfg, lfm_st_err_lfm_pfg, 
                              #lfm_psi_ttfg, lfm_st_err_ttfg,
                              lfm_psi_prop_ignite, lfm_st_err_prop_ignite, 
                              lfm_psi_temp_change, lfm_st_err_temp_change)
```


### Time to Ignition

```{r}
abco_subset_seg_tti <- abco_subset_seg %>%
  drop_na(tti)

#Segmented regression with random changepoints: 

o_mod<-lme(tti~lfm + year_month + site, random=~1|id, data=abco_subset_seg_tti)
os_mod_b<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_b)

#put into the df:
lfm_abco_thresholds_rand_seg[1] <- summary(os_mod_b)$psi[2]
lfm_abco_thresholds_rand_seg[2] <- summary(os_mod_b)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(tti~lfm + year_month + site, data = abco_subset_seg_tti)
u_mod_b <- segmented(u_mod, ~lfm)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
lfm_abco_thresholds_seg[1] <- summary(u_mod_b)$psi[2]
lfm_abco_thresholds_seg[2] <- summary(u_mod_b)$psi[3]
lfm_abco_thresholds_seg[3] <- u_mod_davies$p.value


rsegplot.lfm(os_mod_b, abco_subset_seg_tti, max.x = abco_max_lfm, y.variable = 'tti', y.lab = "Time to Ignition (s)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```
Combustibility Metrics:

### Flame Height
```{r}
abco_subset_seg_fh <- abco_subset_seg %>% drop_na(fh) 

o_mod<-lme(fh~lfm + year_month + site, random=~1|id, data=abco_subset_seg_fh)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
lfm_abco_thresholds_rand_seg[3] <- summary(os_mod)$psi[2]
lfm_abco_thresholds_rand_seg[4] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fh~lfm + year_month + site, data = abco_subset_seg_fh)
u_mod_b <- segmented(u_mod, ~lfm)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
lfm_abco_thresholds_seg[4] <- summary(u_mod_b)$psi[2]
lfm_abco_thresholds_seg[5] <- summary(u_mod_b)$psi[3]
lfm_abco_thresholds_seg[6] <- u_mod_davies$p.value

rsegplot.lfm(os_mod, abco_subset_seg_fh, max.x = abco_max_lfm, y.variable = 'fh', y.lab = "Flame Height (cm)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```

Sustainability Metrics:
### Flame Duration
```{r}
abco_subset_seg_fd <- abco_subset_seg %>% drop_na(fd)

o_mod<-lme(fd~lfm + year_month + site, random=~1|id, data=abco_subset_seg_fd)
os_mod <-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
lfm_abco_thresholds_rand_seg[5] <- summary(os_mod)$psi[2]
lfm_abco_thresholds_rand_seg[6] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fd~lfm + year_month + site, data = abco_subset_seg_fd)
u_mod_b <- segmented(u_mod, ~lfm)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
lfm_abco_thresholds_seg[7] <- summary(u_mod_b)$psi[2]
lfm_abco_thresholds_seg[8] <- summary(u_mod_b)$psi[3]
lfm_abco_thresholds_seg[9] <- u_mod_davies$p.value

rsegplot.lfm(os_mod, abco_subset_seg_fd, max.x = abco_max_lfm, y.variable = 'fd', y.lab = "Flame Duration (s)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```

### Glow Duration
```{r}
abco_subset_seg_gd <- abco_subset_seg %>% drop_na(gd)

o_mod<-lme(gd~lfm + year_month + site, random=~1|id, data=abco_subset_seg_gd)
os_mod <-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
lfm_abco_thresholds_rand_seg[7] <- summary(os_mod)$psi[2]
lfm_abco_thresholds_rand_seg[8] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(gd~lfm + year_month + site, data = abco_subset_seg_gd)
u_mod_b <- segmented(u_mod, ~lfm)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
lfm_abco_thresholds_seg[10] <- summary(u_mod_b)$psi[2]
lfm_abco_thresholds_seg[11] <- summary(u_mod_b)$psi[3]
lfm_abco_thresholds_seg[12] <- u_mod_davies$p.value

rsegplot.lfm(os_mod, abco_subset_seg_gd, max.x = abco_max_lfm, y.variable = 'gd', y.lab = "Glow Duration (s)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```


### Prop. Ignite (5%)
```{r}
abco_subset_seg_prop_ignite <- abco_subset_seg %>% drop_na(prop_ignite)

o_mod<-lme(prop_ignite~lfm + year_month + site, random=~1|id, abco_subset_seg_prop_ignite )
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
lfm_abco_thresholds_rand_seg[9] <- summary(os_mod)$psi[2]
lfm_abco_thresholds_rand_seg[10] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(prop_ignite~lfm + year_month + site, data = abco_subset_seg_prop_ignite)
u_mod_b <- segmented(u_mod, ~lfm)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
lfm_abco_thresholds_seg[13] <- summary(u_mod_b)$psi[2]
lfm_abco_thresholds_seg[14] <- summary(u_mod_b)$psi[3]
lfm_abco_thresholds_seg[15] <- u_mod_davies$p.value

rsegplot.lfm(os_mod, abco_subset_seg_prop_ignite, max.x = abco_max_lfm, y.variable = 'prop_ignite', y.lab = "Proportion Ignted (5% Bins of LFM)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```

<!-- ### Glow to Ignition -->
<!-- ```{r} -->
<!-- abco_subset_seg_gti <- abco_subset_seg %>%  -->
<!--   drop_na(gti) -->

<!-- o_mod<-lme(gti~lfm + year_month + site, random=~1|id, data=abco_subset_seg_gti) -->
<!-- os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1)) -->
<!-- #summarizing results (note the '_coef' argument) -->
<!-- summary.segmented(os_mod) -->

<!-- #rsegplot.lfm(os_mod, abco_subset_seg_gti, max.x = abco_max_lfm, y.variable = 'gti', y.lab = "Glow to Ignition (s)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco) -->
<!-- ``` -->



<!-- ### Max_ Temp_ -->
<!-- ```{r} -->
<!-- abco_subset_seg_lower_temp_max <- abco_subset_seg %>%  -->
<!--   drop_na(lower_temp_max) -->

<!-- o_mod<-lme(lower_temp_max~lfm + year_month + site, random=~1|id, data=abco_subset_seg_lower_temp_max) -->
<!-- os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1)) -->
<!-- #summarizing results (note the '_coef' argument) -->
<!-- summary.segmented(os_mod) -->
<!-- os_mod -->

<!-- #rsegplot.lfm(os_mod, abco_subset_seg_lower_temp_max, max.x = abco_max_lfm, y.variable = 'lower_temp_max', y.lab = "Maximum Temperature (C)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco) -->
<!-- ``` -->


### Temp change: 

```{r}
abco_subset_seg_temp_change <- abco_subset_seg %>% 
  drop_na(temp_change)

o_mod<-lme(lower_temp_max~lfm + year_month + site, random=~1|id, data=abco_subset_seg_temp_change)
os_mod<-segmented.default(o_mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)
os_mod

#put into the df:
lfm_abco_thresholds_rand_seg[11] <- summary(os_mod)$psi[2]
lfm_abco_thresholds_rand_seg[12] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(temp_change~lfm + year_month + site, data = abco_subset_seg_temp_change)
u_mod_b <- segmented(u_mod, ~lfm)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
lfm_abco_thresholds_seg[16] <- summary(u_mod_b)$psi[2]
lfm_abco_thresholds_seg[17] <- summary(u_mod_b)$psi[3]
lfm_abco_thresholds_seg[18] <- u_mod_davies$p.value

rsegplot.lfm(os_mod, abco_subset_seg_temp_change, max.x = abco_max_lfm, y.variable = 'temp_change', y.lab = "Temp Change (C)", tlp = mean_lfm_abco, tlp.lower = lwr_lfm_abco, tlp.upper = upr_lfm_abco)
```
#LFM: FInal table: 


```{r}
#No random effects: 
abco_lfm_summary_df <- lfm_abco_thresholds_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'lfm_', ''),
         across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "segmented") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
abco_lfm_summary_df

#with random effects: 
abco_lfm_rand_summary_df <- lfm_abco_thresholds_rand_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'lfm_', ''),
         across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "random") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
abco_lfm_rand_summary_df

abco_lfm <- bind_rows(abco_lfm_rand_summary_df, abco_lfm_summary_df) %>% 
  mutate(spp = "abco", 
         water_variable = "lfm") 

ggsave(plot=gridExtra::tableGrob(abco_lfm), filename=here("figures", "segmented_tables", "rand_segmented_lfm_abco.png"))
```



# -------

#MPa

###Holding vectors: this will be a df with all to collect results as we go: 

No random effects: 

```{r}
mpa_psi_tti <- c(rep(NaN, 1))
mpa_psi_fh <- c(rep(NaN, 1))
mpa_psi_fd <- c(rep(NaN, 1))
mpa_psi_gd <- c(rep(NaN, 1))
#mpa_psi_gti <- c(rep(NaN, 1))
#mpa_psi_mpa_pfg <- c(rep(NaN, 1))
#mpa_psi_ttfg <- c(rep(NaN, 1))
mpa_psi_fd <- c(rep(NaN, 1))
mpa_psi_prop_ignite <- c(rep(NaN, 1))
mpa_psi_temp_change <- c(rep(NaN, 1))

mpa_st_err_tti <- c(rep(NaN, 1))
mpa_st_err_fh <- c(rep(NaN, 1))
mpa_st_err_fd <- c(rep(NaN, 1))
mpa_st_err_gd <- c(rep(NaN, 1))
#mpa_st_err_gti <- c(rep(NaN, 1))
#mpa_st_err_mpa_pfg <- c(rep(NaN, 1))
#mpa_st_err_ttfg <- c(rep(NaN, 1))
mpa_st_err_fd <- c(rep(NaN, 1))
mpa_st_err_prop_ignite <- c(rep(NaN, 1))
mpa_st_err_temp_change <- c(rep(NaN, 1))

mpa_p_value_tti <- c(rep(NaN, 1))
mpa_p_value_fh <- c(rep(NaN, 1))
mpa_p_value_fd <- c(rep(NaN, 1))
mpa_p_value_gd <- c(rep(NaN, 1))
#mpa_p_value_gti <- c(rep(NaN, 1))
#mpa_p_value_mpa_pfg <- c(rep(NaN, 1))
#mpa_p_value_ttfg <- c(rep(NaN, 1))
mpa_p_value_fd <- c(rep(NaN, 1))
mpa_p_value_prop_ignite <- c(rep(NaN, 1))
mpa_p_value_temp_change <- c(rep(NaN, 1))

mpa_abco_thresholds_seg <- tibble::data_frame(mpa_psi_tti, mpa_st_err_tti, mpa_p_value_tti,
                              mpa_psi_fh, mpa_st_err_fh, mpa_p_value_fh,
                              mpa_psi_fd, mpa_st_err_fd,mpa_p_value_fd,
                              mpa_psi_gd, mpa_st_err_gd, mpa_p_value_gd, 
                              #mpa_psi_gti, mpa_st_err_gti, 
                              #mpa_psi_mpa_pfg, mpa_st_err_mpa_pfg, 
                              #mpa_psi_ttfg, mpa_st_err_ttfg,
                              mpa_psi_prop_ignite, mpa_st_err_prop_ignite, mpa_p_value_prop_ignite,
                              mpa_psi_temp_change, mpa_st_err_temp_change, mpa_p_value_temp_change
                              )
```


Randem effecs: 

```{r}
mpa_psi_tti <- c(rep(NaN, 1))
mpa_psi_fh <- c(rep(NaN, 1))
mpa_psi_fd <- c(rep(NaN, 1))
mpa_psi_gd <- c(rep(NaN, 1))
#mpa_psi_gti <- c(rep(NaN, 1))
#mpa_psi_mpa_pfg <- c(rep(NaN, 1))
#mpa_psi_ttfg <- c(rep(NaN, 1))
mpa_psi_fd <- c(rep(NaN, 1))
mpa_psi_prop_ignite <- c(rep(NaN, 1))
mpa_psi_temp_change <- c(rep(NaN, 1))

mpa_st_err_tti <- c(rep(NaN, 1))
mpa_st_err_fh <- c(rep(NaN, 1))
mpa_st_err_fd <- c(rep(NaN, 1))
mpa_st_err_gd <- c(rep(NaN, 1))
#mpa_st_err_gti <- c(rep(NaN, 1))
#mpa_st_err_mpa_pfg <- c(rep(NaN, 1))
#mpa_st_err_ttfg <- c(rep(NaN, 1))
mpa_st_err_fd <- c(rep(NaN, 1))
mpa_st_err_prop_ignite <- c(rep(NaN, 1))
mpa_st_err_temp_change <- c(rep(NaN, 1))

mpa_abco_thresholds_rand_seg <- tibble::data_frame(mpa_psi_tti, mpa_st_err_tti,
                              mpa_psi_fh, mpa_st_err_fh, 
                              mpa_psi_fd, mpa_st_err_fd,
                              mpa_psi_gd, mpa_st_err_gd, 
                              #mpa_psi_gti, mpa_st_err_gti, 
                              #mpa_psi_mpa_pfg, mpa_st_err_mpa_pfg, 
                              #mpa_psi_ttfg, mpa_st_err_ttfg,
                              mpa_psi_prop_ignite, mpa_st_err_prop_ignite, 
                              mpa_psi_temp_change, mpa_st_err_temp_change)
```


### Time to Ignition

```{r}
abco_subset_seg_tti <- abco_subset_seg %>%
  drop_na(tti)

#Segmented regression with random changepoints: 

o_mod<-lme(tti~mpa + year_month + site, random=~1|id, data=abco_subset_seg_tti)
os_mod_b<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod_b)

#put into the df:
mpa_abco_thresholds_rand_seg[1] <- summary(os_mod_b)$psi[2]
mpa_abco_thresholds_rand_seg[2] <- summary(os_mod_b)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(tti~mpa + year_month + site, data = abco_subset_seg_tti)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[1] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[2] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[3] <- u_mod_davies$p.value


rsegplot.mpa(os_mod_b, abco_subset_seg_tti, max.x = abco_max_mpa, y.variable = 'tti', y.lab = "Time to Ignition (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```
Combustibility Metrics:

### Flame Height
```{r}
abco_subset_seg_fh <- abco_subset_seg %>% drop_na(fh) 

o_mod<-lme(fh~mpa + year_month + site, random=~1|id, data=abco_subset_seg_fh)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
mpa_abco_thresholds_rand_seg[3] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[4] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fh~mpa + year_month + site, data = abco_subset_seg_fh)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[4] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[5] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[6] <- u_mod_davies$p.value

rsegplot.mpa(os_mod, abco_subset_seg_fh, max.x = abco_max_mpa, y.variable = 'fh', y.lab = "Flame Height (cm)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)

```

Sustainability Metrics:
### Flame Duration
```{r}
abco_subset_seg_fd <- abco_subset_seg %>% drop_na(fd)

o_mod<-lme(fd~mpa + year_month + site, random=~1|id, data=abco_subset_seg_fd)
os_mod <-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
mpa_abco_thresholds_rand_seg[5] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[6] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(fd~mpa + year_month + site, data = abco_subset_seg_fd)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[7] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[8] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[9] <- u_mod_davies$p.value

rsegplot.mpa(os_mod, abco_subset_seg_fd, max.x = abco_max_mpa, y.variable = 'fd', y.lab = "Flame Duration (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```

### glow Duration
```{r}
abco_subset_seg_gd <- abco_subset_seg %>% drop_na(gd)

o_mod<-lme(gd~mpa + year_month + site, random=~1|id, data=abco_subset_seg_gd)
os_mod <-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
mpa_abco_thresholds_rand_seg[7] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[8] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(gd~mpa + year_month + site, data = abco_subset_seg_gd)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[10] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[11] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[12] <- u_mod_davies$p.value

rsegplot.mpa(os_mod, abco_subset_seg_gd, max.x = abco_max_mpa, y.variable = 'gd', y.lab = "Glow Duration (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```


### Prop. Ignite (5%)
```{r}
abco_subset_seg_prop_ignite <- abco_subset_seg %>% drop_na(prop_ignite)

o_mod<-lme(prop_ignite~mpa + year_month + site, random=~1|id, abco_subset_seg_prop_ignite )
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)

#put into the df:
mpa_abco_thresholds_rand_seg[9] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[10] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(prop_ignite~mpa + year_month + site, data = abco_subset_seg_prop_ignite)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[13] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[14] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[15] <- u_mod_davies$p.value

rsegplot.mpa(os_mod, abco_subset_seg_prop_ignite, max.x = abco_max_mpa, y.variable = 'prop_ignite', y.lab = "Proportion Ignted (5% Bins of mpa)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```

<!-- ### Glow to Ignition -->
<!-- ```{r} -->
<!-- abco_subset_seg_gti <- abco_subset_seg %>%  -->
<!--   drop_na(gti) -->

<!-- o_mod<-lme(gti~mpa + year_month + site, random=~1|id, data=abco_subset_seg_gti) -->
<!-- os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1)) -->
<!-- #summarizing results (note the '_coef' argument) -->
<!-- summary.segmented(os_mod) -->

<!-- #rsegplot.mpa(os_mod, abco_subset_seg_gti, max.x = abco_max_mpa, y.variable = 'gti', y.lab = "Glow to Ignition (s)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco) -->
<!-- ``` -->



<!-- ### Max_ Temp_ -->
<!-- ```{r} -->
<!-- abco_subset_seg_lower_temp_max <- abco_subset_seg %>%  -->
<!--   drop_na(lower_temp_max) -->

<!-- o_mod<-lme(lower_temp_max~mpa + year_month + site, random=~1|id, data=abco_subset_seg_lower_temp_max) -->
<!-- os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1)) -->
<!-- #summarizing results (note the '_coef' argument) -->
<!-- summary.segmented(os_mod) -->
<!-- os_mod -->

<!-- #rsegplot.mpa(os_mod, abco_subset_seg_lower_temp_max, max.x = abco_max_mpa, y.variable = 'lower_temp_max', y.lab = "Maximum Temperature (C)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco) -->
<!-- ``` -->


### Temp change: 

```{r}
abco_subset_seg_temp_change <- abco_subset_seg %>% 
  drop_na(temp_change)

o_mod<-lme(lower_temp_max~mpa + year_month + site, random=~1|id, data=abco_subset_seg_temp_change)
os_mod<-segmented.default(o_mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '_coef' argument)
summary.segmented(os_mod)
os_mod

#put into the df:
mpa_abco_thresholds_rand_seg[11] <- summary(os_mod)$psi[2]
mpa_abco_thresholds_rand_seg[12] <- summary(os_mod)$psi[3]

# Segmented regression no random changepoints: 

u_mod <- lm(temp_change~mpa + year_month + site, data = abco_subset_seg_temp_change)
u_mod_b <- segmented(u_mod, ~mpa)
summary.segmented(u_mod_b)

u_mod_davies <- davies.test(u_mod_b)

#put into the df:
mpa_abco_thresholds_seg[16] <- summary(u_mod_b)$psi[2]
mpa_abco_thresholds_seg[17] <- summary(u_mod_b)$psi[3]
mpa_abco_thresholds_seg[18] <- u_mod_davies$p.value

rsegplot.mpa(os_mod, abco_subset_seg_temp_change, max.x = abco_max_mpa, y.variable = 'temp_change', y.lab = "Temp Change (C)", tlp = mean_mpa_abco, tlp.lower = lwr_mpa_abco, tlp.upper = upr_mpa_abco)
```
#mpa: FInal table: 


```{r}
#No random effects: 
abco_mpa_summary_df <- mpa_abco_thresholds_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'mpa_', ''),
        across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "segmented") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
abco_mpa_summary_df

#with random effects: 
abco_mpa_rand_summary_df <- mpa_abco_thresholds_rand_seg %>% 
  pivot_longer(everything(), 
               names_to = "flam_metric", 
              values_to = "value") %>% 
  group_by(flam_metric) %>% 
   summarise(value = mean(value)) %>% 
             #sd_bootstrap = sd(value)) %>% 
  mutate(across('flam_metric', str_replace, 'mpa_', ''),
        across('flam_metric', str_replace_all, '_', ' '), 
         statistic = case_when(
           grepl("p value", flam_metric) ~ "p value",
            grepl("psi", flam_metric) ~"psi",
            grepl("st err", flam_metric) ~"st err")) %>% 
  mutate(across('flam_metric', str_replace, 'p value|st err|psi', ''), 
         analysis = "random") %>% 
  arrange(flam_metric, statistic, value, analysis)
         
abco_mpa_rand_summary_df

abco_mpa <- bind_rows(abco_mpa_rand_summary_df, abco_mpa_summary_df) %>% 
  mutate(spp = "abco", 
         water_variable = "mpa") 

ggsave(plot=gridExtra::tableGrob(abco_mpa), filename=here("figures", "segmented_tables", "rand_segmented_mpa_abco.png"))
```


#------------

#All together now:

```{r}
abco_all_segmented <- bind_rows(abco_lfm, abco_mpa)

abco_all_segmented_wide <- abco_all_segmented %>% 
  mutate(across('statistic', str_replace, ' ', '_')) %>% 
  pivot_wider(names_from = statistic, 
              values_from = value)

write_csv(abco_all_segmented_wide, 
          here::here("processed-data", "analysis 2.0", "segmented_reg_all", "abco_all_segmented_wide.csv"))
```

#Visualize: 

```{r}
abco_all_segmented_wide %>% 
  #filter(statistic == "psi") %>% 
  ggplot(aes(
    y = psi, 
    x = flam_metric,
    color = analysis, 
   # size = p_value
  )) +
  geom_point() +
  facet_wrap(~water_variable,scales = "free")
```


