---
title: "MPa and LFM"
author: "Joe Celebrezze"
date: "7/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This script is a "quick script" showing how the water potential and LFM changed over the 2020 season and how this compares to the 2021 season.

NOTE: Some things to fix when doing more in-depth data analysis...
  Duplicate measures for mpa when looking at old vs. new growth
  Comparing old/new growth to combined LFM right now -- combine old and new like we did with stems/leaves
  Old vs. new could be driving differences early season -- compare with phenology data (meet with Isaac)
  Isohydry vs. anisohydry
  
Reading in data and loading necessary packages:
```{r}
library(tidyverse)
library(here)
here = here::here
select = dplyr::select
```

```{r}
df_2020 <- readr::read_csv(here("raw-data", "field.summer.2020.csv"))
df_2021 <- readr::read_csv(here("raw-data", "CZO_alldata_compiled.csv"))
```
#------------------------------------
# Data Wrangling
```{r}
df_2020[df_2020 == "ABCO "] <- "ABCO"

#source("http://goo.gl/UUyEzD") #outlier KD (original function)

    #The following function is derived from outlierKD (from above)
outlierKD2 <- function(dt, var) {
  var_name <- eval(substitute(var),eval(dt))
  tot <- sum(!is.na(var_name))
  na1 <- sum(is.na(var_name))
  m1 <- mean(var_name, na.rm = T)
  par(mfrow=c(2, 2), oma=c(0,0,3,0))
  boxplot(var_name, main="With outliers")
  hist(var_name, main="With outliers", xlab=NA, ylab=NA)
  outlier <- boxplot.stats(var_name)$out
  mo <- mean(outlier)
  var_name <- ifelse(var_name %in% outlier, NA, var_name)
  boxplot(var_name, main="Without outliers")
  hist(var_name, main="Without outliers", xlab=NA, ylab=NA)
  title("Outlier Check", outer=TRUE)
  na2 <- sum(is.na(var_name))
  message("Outliers identified: ", na2 - na1, " from ", tot, " observations")
  message("Proportion (%) of outliers: ", (na2 - na1) / tot*100)
  message("Mean of the outliers: ", mo)
  m2 <- mean(var_name, na.rm = T)
  message("Mean without removing outliers: ", m1)
  message("Mean if we remove outliers: ", m2)
    dt[as.character(substitute(var))] <- invisible(var_name)
    assign(as.character(as.list(match.call())$dt), dt, envir = .GlobalEnv)
    message("Outliers successfully removed", "\n")
    return(invisible(dt))
}

df_2020 <- df_2020 %>% 
  mutate(lfm.outliers.out = lfm)

outlierKD2(df_2020, lfm.outliers.out) #check for outliers and remove (happens in outliers.out column, lfm column still contains outliers)
```

Dealing with outliers -- LFM, 2021
```{r}
##make column to take out outliers from lfm, while keeping column with original lfms too
df_2021 <- df_2021 %>%
  mutate(lfm.outliers.out = lfm)

outlierKD2(df_2021, lfm.outliers.out) #check for outliers and remove (happens in outliers.out column, lfm column still contains outliers)
```



```{r}
df_2020_subset <- df_2020 %>% 
  select(spp, midday, lfm.outliers.out, date)

df_2021_subset <- df_2021 %>% 
  select(spp, midday, lfm.outliers.out, date)
```


```{r}
df_lfm_mpa <- rbind(df_2020_subset, df_2021_subset) %>% 
  drop_na() %>% 
  mutate(lfm = lfm.outliers.out, 
         ate = lubridate::mdy(date), 
         mpa = midday) %>% 
  filter(lfm > 45, 
         #lfm < 250, 
         mpa < -.10) %>% 
  select(spp, lfm, mpa)

df_lfm_mpa %>% 
  ggplot(aes(y = lfm, x = mpa, color = spp)) +
  geom_point()
```

#------------------------------------
# Data Visualization

## Water Potential

### 2020 Data
```{r}
mpa.predawn.2020.plot <- ggplot(data = df_2020, aes(x = doy, y = predawn)) +
  geom_point(size = 0.5) +
  geom_smooth(se = F, color = "black", size = 0.3, method = 'lm') +
  facet_wrap(~spp) + 
  labs(title = "2020 Predawn", x = "Day of Year", y = "Predawn (MPa)") +
  theme_bw()
mpa.predawn.2020.plot

mpa.midday.2020.plot <- ggplot(data = df_2020, aes(x = doy, y = midday)) +
  geom_point(size = 0.5) +
  geom_smooth(se = F, color = "black", size = 0.3, method = 'lm') +
  facet_wrap(~spp) + 
  labs(title = "2020 Midday", x = "Day of Year", y = "Midday (MPa)") +
  theme_bw()
mpa.midday.2020.plot
```

### 2021 Data
```{r}
mpa.predawn.2021.plot <- ggplot(data = df_2021, aes(x = doy, y = predawn)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = "black", size = 0.3) +
  facet_wrap(~spp) + 
  labs(title = "2021 Predawn", x = "Day of Year", y = "Predawn (MPa)") +
  theme_bw()
mpa.predawn.2021.plot

mpa.midday.2021.plot <- ggplot(data = df_2021, aes(x = doy, y = midday)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = "black", size = 0.3) +
  facet_wrap(~spp) + 
  labs(title = "2021 Midday", x = "Day of Year", y = "Midday (MPa)") +
  theme_bw()
mpa.midday.2021.plot
```
#------------------------------------
## Live Fuel Moisture

### 2020 Data
```{r}
lfm.2020.plot <- ggplot(data = df_2020, aes(x = doy, y = lfm)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = "black", size = 0.3) +
  facet_wrap(~spp) + 
  labs(title = "2020 LFM", x = "Day of Year", y = "Live Fuel Moisture") +
  theme_bw()
lfm.2020.plot
```

### 2021 Data
```{r}
lfm.2021.plot <- ggplot(data = df_2021, aes(x = doy, y = lfm)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = "black", size = 0.3) +
  facet_wrap(~spp) + 
  labs(title = "2021 LFM", x = "Day of Year", y = "Live Fuel Moisture") +
  theme_bw()
lfm.2021.plot
```

=======
### 2021 Data (Separated by age)
```{r}
df_2021.new <- df_2021 %>%
  filter(`new/old` == "N")

lfm.2021.new.plot <- ggplot(data = df_2021.new, aes(x = doy, y = lfm.outliers.out)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = "black", size = 0.3) +
  facet_wrap(~spp) + 
  labs(title = "2021 LFM (New Growth)", x = "Day of Year", y = "Live Fuel Moisture") +
  theme_bw()
lfm.2021.new.plot

df_2021.old <- df_2021 %>% 
  filter(`new/old` == "O")
lfm.2021.old.plot <- ggplot(data = df_2021.old, aes(x = doy, y = lfm.outliers.out)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = "black", size = 0.3) +
  facet_wrap(~spp) + 
  labs(title = "2021 LFM (Old Growth)", x = "Day of Year", y = "Live Fuel Moisture") +
  theme_bw()
lfm.2021.old.plot
```
#------------------------------------
## Live Fuel Moisture vs. Water Potential

### Average Water Potential
```{r}
df_2020 <- df_2020 %>% 
  mutate(mpa = (predawn + midday)/2)

df_2021 <- df_2021 %>% 
  mutate(predawn = as.numeric(predawn)) %>% 
  mutate(midday = as.numeric(midday)) %>% 
  mutate(mpa = (predawn + midday)/2)

lfm.vs.mpa.2020 <- ggplot(data = df_2020, aes(x = mpa, y = lfm)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = 'black', size = 0.3) +
  facet_wrap(~spp) +
  labs(title = "2020 LFM vs. Water Potential", 
       x = "Avg Water Potential (MPa)", y = "Live Fuel Moisture") +
  theme_bw()
lfm.vs.mpa.2020

lfm.vs.mpa.2021 <- ggplot(data = df_2021, aes(x = mpa, y = lfm.outliers.out)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = 'black', size = 0.3) +
  facet_wrap(~spp) +
  labs(title = "2021 LFM vs. Water Potential", 
       x = "Avg Water Potential (MPa)", y = "Live Fuel Moisture") +
  theme_bw()
lfm.vs.mpa.2021
```

### Midday
```{r}
lfm.vs.mid.2020 <- ggplot(data = df_2020, aes(x = midday, y = lfm)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = 'black', size = 0.3) +
  facet_wrap(~spp) +
  labs(title = "2020 LFM vs. Midday Water Potential", 
       x = "Midday Water Potential (MPa)", y = "Live Fuel Moisture") +
  theme_bw()
lfm.vs.mid.2020

lfm.vs.mid.2021 <- ggplot(data = df_2021, aes(x = midday, y = lfm.outliers.out)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = 'black', size = 0.3) +
  facet_wrap(~spp) +
  labs(title = "2021 LFM vs. Midday Water Potential", 
       x = "Midday Water Potential (MPa)", y = "Live Fuel Moisture") +
  theme_bw()
lfm.vs.mid.2021
```
### Boxplots
```{r}
site.labs <- c("Site 1", "Site 2")
names(site.labs) <- c(1,2)

mpa.predawn.2021.boxplot <- ggplot(data = df_2021, aes(x = as.character(doy), y = predawn)) +
  geom_boxplot() +
  facet_wrap(~site, labeller = labeller(site = site.labs)) +
  labs(title = "2021 Predawn Water Potential", 
       x = "Day of Year", y = "Predawn Water Potential") +
  theme_bw()     

mpa.predawn.2021.boxplot
```

```{r}
mpa.midday.2021.boxplot <- ggplot(data = df_2021, aes(x = as.character(doy), y = midday)) +
  geom_boxplot() +
  facet_wrap(~site, labeller = labeller(site = site.labs)) +
  labs(title = "2021 Midday Water Potential", 
       x = "Day of Year", y = "Midday Water Potential") +
  theme_bw()     

mpa.midday.2021.boxplot
```

```{r}
lfm.2021.boxplot <- ggplot(data = df_2021, aes(x = as.character(doy), y = lfm.outliers.out)) +
  geom_boxplot() +
  facet_wrap(~site, labeller = labeller(site = site.labs)) +
  labs(title = "2021 Live Fuel Moisture", 
       x = "Day of Year", y = "LFM") +
  theme_bw() 

lfm.2021.boxplot
```

### Stems vs. Leaves
```{r}
df_oct2021 <- read.csv(here('raw-data/CZO_October_StemsLeaves.csv'))

outlierKD2(df_oct2021, lfm)
outlierKD2(df_oct2021, lfm_both)

df_oct2021_no_both <- df_oct2021 %>% 
  filter(spp != "QUKE") %>% 
  filter(spp != "CADE") %>% 
  filter(spp != "PIJE") %>% 
  filter(stem.leaves != 'both')

ggplot(data = df_oct2021_no_both, aes(x = lfm, y = lfm_both, color = stem.leaves)) +
  geom_point() +
  geom_abline() +
  labs(x = "LFM (separated)", y = "LFM (compiled)", color = "Stem or Leaves") +
  scale_color_discrete(name = "Stem or Leaves", labels = c("Leaves", "Stems")) +
  theme_bw()

ggplot(data = df_oct2021_no_both, aes(x = lfm, y = lfm_both, color = stem.leaves)) +
  geom_point() +
  geom_abline() +
  labs(x = "LFM (separated)", y = "LFM (compiled)", color = "Stem or Leaves") +
  scale_color_discrete(name = "Stem or Leaves", labels = c("Leaves", "Stems")) +
  facet_grid(~spp) +
  theme_bw()
```

### Stems vs. Leaves Boxplot
```{r}
ggplot(data = df_oct2021_no_both, aes(x = spp, y = lfm, fill = stem.leaves)) +
  geom_boxplot() +
  labs(x = "Species", y = "LFM", fill = "Stem or Leaves") +
  scale_fill_discrete(name = "Stem or Leaves", labels = c("Leaves", "Stems")) +
  theme_bw()
```

### Difference Between Middays and Predawns
```{r}
df_2021 <- df_2021 %>% 
  mutate(diff_mpa = midday - predawn)

ggplot(data = df_2021, aes(x = as.character(doy), y = diff_mpa)) +
  geom_boxplot() +
  facet_wrap(~site) +
  labs(x = "Day of Year", y = "Difference Between Middays and Predawns") +
  theme_bw()
```

```{r}
df_2021_no_pq <- df_2021 %>% 
  filter(spp != "PIJE") %>% 
  filter(spp != 'QUKE')

ggplot(data = df_2021_no_pq, aes(x = as.character(doy), y = diff_mpa)) +
  geom_boxplot() +
  facet_grid(spp~site) +
  labs(x = "Day of Year", y = "Difference Between Middays and Predawns") +
  theme_bw()

df_2021_pq_only <- df_2021 %>% 
  filter(spp == 'PIJE'| spp == 'QUKE')

ggplot(data = df_2021_pq_only, aes(x = as.character(doy), y = diff_mpa)) +
  geom_boxplot() +
  facet_grid(~spp) +
  labs(x = "Day of Year", y = "Difference Between Middays and Predawns") +
  theme_bw()
```

### LFM vs. Water Potential (later season, old growth only)
```{r}
df_2021_late <- df_2021 %>% 
  filter(doy != 114) %>% filter(doy != 134) %>% filter(doy != 135) %>% filter(doy != 166) %>%  filter(doy != 167) %>%    #filtering out first three trips of the season
  filter(doy!=289) %>% filter(doy!=290)  #filtering out last trip of season (wetter)

df_2021_late_old <- df_2021_late %>% 
  filter(`new/old` == "old") # only old growth

lfm.vs.mid.late.old.2021 <- ggplot(data = df_2021_late_old, aes(x = midday, y = lfm.outliers.out)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = 'black', size = 0.3) +
  facet_wrap(~spp) +
  labs(title = "2021 LFM vs. Midday Water Potential (Late Season)", 
       x = "Midday Water Potential (MPa)", y = "Live Fuel Moisture (*Old* Growth)") +
  theme_bw()
lfm.vs.mid.late.old.2021
```

New vs. old
```{r}
lfm.vs.mid.late.2021 <- ggplot(data = df_2021_late, aes(x = midday, y = lfm.outliers.out, color = `new/old`)) +
  geom_point(size = 0.5) +
  geom_smooth(method = 'lm', se = F, color = 'black', size = 0.3) +
  facet_wrap(~spp) +
  labs(title = "2021 LFM vs. Midday Water Potential (Late Season)", 
       x = "Midday Water Potential (MPa)", y = "Live Fuel Moisture") +
  theme_bw()

lfm.vs.mid.late.2021
```

