---
title: 'PCA on SKI Flammability Trials'
author: "Indra Boving"
date: "Updated last 11/22/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Overview: 

This script performs a PCA on various iterations of the flammability data (logged, not logged, including predictors and not including predictors). It adds the PCA scores from the unlogged flammability metrics back into the master dataset. 

HOWEVER: For modeling purposes, we generally disregard this analysis and rerun the PCA in the modeling script to ensure that we are only generating scores for the data combinations (i.e. species and time points) that we are interested in. 

```{r message=FALSE, warning=FALSE, include=FALSE}
library(ggplot2)
library(gapminder)
library(data.table)
library(purrr) #for visualizing all variables in one big plot
library(naniar)
library(dplyr)
library(tidyverse)
library(devtools)
library(ggbiplot)
library(ggfortify)
library(ggpubr)
library(here)
library(psych)
here = here::here #Gets confused with dplyr::here
```

# Organize Data (in Data_Wrangling.Rmd):

1. Missing values --> NA, then imputed (see DataWrangling.Rmd)
2. Outliers removed from LFM column using oulierKD (outside 1.5 IQR --> NA)
3. Median inserted (grouped by spp) for flam metrics; ungrouped median for chamber NAs (temps, weights). 
4. Normalized flam metrics using the burned sample dry weight (.norm added to names)

### Note: This dataset inludes only Epiradiator and Ignited samples:

```{r echo=FALSE, warning=FALSE}
seki.flamdata <- read.csv(here("processed-data", "compiled-datasets", "SEKI", "seki_flam_data_all.csv")) %>%
  mutate(LFM = lfm.NAs.imputed) %>% 
  filter(model == "HP", ignition == 1)

#colSums(is.na(seki.flamdata))
```


```{r, warning = FALSE}
distributions <- seki.flamdata %>%
  select(spp, mpa, lfm.outliers.out, lfm.NAs.imputed, sample.wt, dw.flam.sample, ttfg, gd, gti, tti, fh, pfg, fd, temp.max, prop.ignite, dry.norm.fh, dry.norm.gd, dry.norm.fd, dry.norm.pfg, dry.norm.gti, dry.norm.ttfg, dry.norm.tti, temp.change) %>%
  gather(-spp, key = "var", value = "value") %>%
  ggplot() +
  geom_density(aes(x = value, color = spp)) +
  facet_wrap(~ var, scales = "free")

distributions +
  ggtitle("HP")
```

Taking the log of the flam metrics, to see if that looks better: 

#### Untransformed values: 

```{r, include=TRUE}
#not transformed:
seki.flamdata.nolog <- (seki.flamdata[c("fh", "ttfg", "tti", "fd", "gd", "gti", "sample.wt", "pfg", "temp.max", "prop.ignite", "flam.index" )])
multi.hist(seki.flamdata.nolog[,sapply(seki.flamdata.nolog, is.numeric)])
```


#### Log-transformed values: 

```{r, include=TRUE}
## log transform normalized flam metrics:
log.seki.flamdata <- log(seki.flamdata[c("fh", "ttfg", "tti", "fd", "gd", "gti", "sample.wt", "pfg", "temp.max", "prop.ignite","mpa", "lfm.NAs.imputed", "flam.index")]) #flam metrics, lfm, and sample weight
#multi.hist(log.seki.flamdata[,sapply(log.seki.flamdata, is.numeric)])
```


```{r}
#Label and subset categorical variables:
cat.seki.flamdata <- (seki.flamdata[c("hydration", "spp", "year.month", "sample")])
```

```{r, include = FALSE}
# #Not transformed: 
# nolog.seki.flamdata.norm <- (seki.flamdata[c("dry.norm.fh", "dry.norm.gd", "dry.norm.fd", "dry.norm.pfg", "dry.norm.gti", "dry.norm.ttfg", "dry.norm.tti")]) #flam metrics, lfm, and sample weight
# multi.hist(nolog.seki.flamdata.norm[,sapply(nolog.seki.flamdata.norm, is.numeric)])
# 
# ## log transform normalized flam metrics:
# log.seki.flamdata.norm <- log(seki.flamdata[c("dry.norm.fh", "dry.norm.gd", "dry.norm.fd", "dry.norm.pfg", "dry.norm.gti", "dry.norm.ttfg", "dry.norm.tti", "mpa", "lfm.NAs.imputed")]) #flam metrics, lfm, and sample weight
# multi.hist(log.seki.flamdata.norm[,sapply(log.seki.flamdata.norm, is.numeric)])
```

# 1. PCA including predictor variables 

```{r warning=FALSE}
#colSums(is.na(seki.flamdata))
seki.flamdata.all <- (seki.flamdata[, c("lfm.NAs.imputed", "mpa",
         "fh", "ttfg", "tti", "fd", "gd", "gti", "sample.wt", "pfg",
         "temp.max", 
         #"prop.ignite", 
         "dw.flam.sample")])


seki.flamdata.all.pca <- prcomp(na.omit(seki.flamdata.all), center = TRUE, scale = TRUE)

#print(seki.flamdata.all.pca)
plot(seki.flamdata.all.pca)
#plot(seki.flamdata.all.pca, type = "l")
summary(seki.flamdata.all.pca)
#biplot(seki.flamdata.all.pca)
```


```{r warning=FALSE}
f <- ggbiplot::ggbiplot(seki.flamdata.all.pca, groups = cat.seki.flamdata[,2], 
                        circle = TRUE, 
                        varname.size = 3, 
                        alpha = .2, 
                        labels.size = 3,
                        varname.adjust = 2.5) +  # by spp
ggtitle("All Values")
print(f)
```


```{r warning=FALSE}
f <- ggbiplot::ggbiplot(seki.flamdata.all.pca, groups = cat.seki.flamdata[,1], 
                        circle = TRUE, 
                        varname.size = 3, 
                        alpha = .2, 
                        labels.size = 3,
                        varname.adjust = 2.5) +  #
ggtitle("All Values")  # by Hydration
print(f)

#f <- ggbiplot::ggbiplot(seki.flamdata.all.pca, groups = cat.seki.flamdata[,5], ellipse = TRUE, circle = TRUE, 
                       # varname.size = 4, alpha = .4)   # by trial (month and year)
#print(f)
```

# 2. PCA on flam. characteristics: 

```{r warning=FALSE}
seki.flamdata.flam <- (seki.flamdata[, c("fh", "ttfg", "tti", "fd", "gd", "gti", "pfg",
         "temp.max")])

seki.flamdata.pca <- prcomp(na.omit(seki.flamdata.flam), center = TRUE, scale = TRUE)

#print(seki.flamdata.pca)
plot(seki.flamdata.pca)
#plot(seki.flamdata.pca, type = "l")
summary(seki.flamdata.pca)
#biplot(seki.flamdata.pca)

f <- ggbiplot::ggbiplot(seki.flamdata.pca, groups = cat.seki.flamdata[,2], 
                        circle = TRUE, 
                        varname.size = 3, 
                        alpha = .2, 
                        labels.size = 3,
                        varname.adjust = 2.5) +  # by spp +  # by spp
ggtitle("Flammability metrics only")
print(f)

f <- ggbiplot::ggbiplot(seki.flamdata.pca, groups = cat.seki.flamdata[,1],
                         circle = TRUE, 
                        varname.size = 3, 
                        alpha = .2, 
                        labels.size = 3,
                        varname.adjust = 2.5) +  # by spp
ggtitle("Flammability metrics only")  # by Hydration
print(f)

f <- ggbiplot::ggbiplot(seki.flamdata.pca,  
                        circle = TRUE, 
                        varname.size = 3, 
                        alpha = .2, 
                        labels.size = 3,
                        varname.adjust = 2.5) +  # by spp
ggtitle("Flammability metrics only")  # by Hydration
print(f)

#f <- ggbiplot::ggbiplot(seki.flamdata.pca, groups = cat.seki.flamdata[,5], ellipse = TRUE, circle = TRUE, 
                       # varname.size = 4, alpha = .4)   # by trial (month and year)
#print(f)
```

# Interpretation: 

```{r}
table_pca <- tab_pca(seki.flamdata.pca)
table_pca
```

PC1 loads positively on flame height & flame duration (**sustainability and combustibility**), and loads negatively on time to ignition and glow to ignition (**ignitability**). 

PC2 is heavily negatively loaded on post-flame glow and glow duration (**consumability**). 

PC1 is the better at explaining flammability overall, especially as far as actual flames are concerned. 


# 3. PCA on flam. characteristics (log-transformed)

```{r warning=FALSE}
seki.flamdata.flam.log <- (log.seki.flamdata[, c("fh", "ttfg", "tti", "fd", "gd", "gti", "pfg",
         "temp.max")])

seki.flamdata.pca.log <- prcomp(na.omit(seki.flamdata.flam.log), center = TRUE, scale = TRUE)

#print(seki.flamdata.pca)
plot(seki.flamdata.pca.log)
#plot(seki.flamdata.pca, type = "l")
summary(seki.flamdata.pca.log)
#biplot(seki.flamdata.pca)

f <- ggbiplot::ggbiplot(seki.flamdata.pca.log, groups = cat.seki.flamdata[,2], 
                        circle = TRUE, 
                        varname.size = 3, 
                        alpha = .2, 
                        labels.size = 3,
                        varname.adjust = 2.5) +  # by spp +  # by spp
ggtitle("Flammability metrics only - log-transformed")
print(f)

f <- ggbiplot::ggbiplot(seki.flamdata.pca.log, groups = cat.seki.flamdata[,1],
                         circle = TRUE, 
                        varname.size = 3, 
                        alpha = .2, 
                        labels.size = 3,
                        varname.adjust = 2.5) +  # by spp
ggtitle("Flammability metrics only - log-transformed")  # by Hydration
print(f)

f <- ggbiplot::ggbiplot(seki.flamdata.pca.log,  
                        circle = TRUE, 
                        varname.size = 3, 
                        alpha = .2, 
                        labels.size = 3,
                        varname.adjust = 2.5) +  # by spp
ggtitle("Flammability metrics only - log-transformed")  # by Hydration
print(f)
```
# Interpretation: 

PC1 


# 4. Create new dataset for MEMs: 

Here: `mem.data.seki.epi.csv"`

- PCA includes only the flammability metrics

```{r warning=FALSE}
### Plot PCA scores yourself (and thus access for plotting against LFM)
#head(seki.flamdata)

x.flam <-predict(seki.flamdata.pca)  ### generate scores for each row in seki.flamdata2
pca.flam.data <- as.data.frame(x.flam) 

#x6 <-predict(seki.flamdata6.pca)  ### generate scores for each row in seki.flamdata2
#pca.flam.data6 <- as.data.frame(x6) 
#pca.flam.data6[which.min(pca.flam.data6$PC1),]

#all.data <- cbind.data.frame(ignite.only.epi, pca.flam.data6) %>%  #ignite.only.all.epi from Data_Wrangling_DATE.Rmd (so run that one first)
 # mutate(PC1.norm = PC1, PC2.norm = PC2, PC3.norm = PC3, PC4.norm = PC4, PC5.norm = PC5, PC6.norm = PC6, PC7.norm = PC7, PC1 = NULL, PC2 = NULL, PC3 = NULL, PC4 = NULL, PC5 = NULL, PC6 = NULL, PC7 = NULL )

all.data.epi <- cbind(seki.flamdata, pca.flam.data)
#colSums(is.na(all.data))
#str(all.data.epi)

#dataset with the above columns, PCA using imputed NAs (medians), and flam metrics with NAs still in there:
mem.data <- all.data.epi 

mem.data %>% 
write_csv(here("processed-data", "compiled-datasets", "SEKI", "pca_flam_data_seki.csv"))

#check out data: 
#str(mem.data)
```