---
title: "Visualizations and Summaries - Figures"
author: "Indra Boving & Joe Celebrezze"
date: "6/21/2022"
output: html_document
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(purrr) #for visualizing all variables in one big plot
library(naniar) #for dealing with NAs nicely 
library(tidyverse)
library(ggpubr)
library(cowplot)
library(GGally) #for corr plots
require(kimisc) # has the nlist function to create a named list
library(strengejacke)
library(sjPlot) # table functions
library(here)
library(effects) #for plofhng model effects
library(sjstats) #use for r2 functions
library("broom.mixed")
library(MuMIn)
library(modelsummary)
library(nlme)
library(MetBrewer)
library(remef)
library(kableExtra)

filter = dplyr::filter
mutate = dplyr::mutate
select = dplyr::select
here = here::here

source(here::here("scripts", "scripts_functions", "figure_info_sierra_flammability.R")) #color and theme info is here
```

#------------------------------------
# 1. Data wrangling
Reading in dataframe

- For the Sierra analysis, this is combining all species and dropping the august sampling data (not enough samples and it was measured a lil differently). 

```{r}
mem_data_all <- read_csv(here("processed-data", "sierra_flam_data_all.csv")) %>% 
  select(lfm, mpa, fh, fh, fd, gd,tti, prop_ignite, temp_change, ignition, sample_wt, dry_wt, fresh_wt, water_wt, location, site, year_month, spp, individual) %>% 
  mutate(dw_flam_sample = sample_wt * (dry_wt/fresh_wt),
         ww_flam_sample = sample_wt * (water_wt/fresh_wt)) %>% 
  mutate(excess_water = (ww_flam_sample - dw_flam_sample)) %>% 
  #group_by(spp) %>% 
  mutate(mpa_scaled = scale(mpa),
         dw_flam_sample_scaled = scale(dw_flam_sample), 
         sample_wt_scaled = scale(sample_wt), 
         ww_flam_sample_scaled = scale(ww_flam_sample),
         lfm_scaled = scale(lfm), 
         excess_water_scaled = scale(excess_water)) %>% 
  filter(!year_month %in% c("2021_august")) %>% 
  drop_na(mpa_scaled, lfm_scaled, sample_wt_scaled)
#%>% 
  #filter(!spp %in% c("ceco"))
```

#2. Remeff figures of each flam metric

```{r}
#fh_mod_noints <- lmer(fh ~ mpa_scaled + lfm_scaled+ spp + site + year_month + (1 | individual), data = mem_data_all)

#tti_mod_noints <- lmer(tti ~ mpa_scaled + lfm_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)

#gd_mod <- lmer(gd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

#gd_mod_noints <- lmer(gd ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

#fd_mod <- lmer(fd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

#fd_mod_noints <- lmer(fd ~ spp+ mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

#temp_change_mod <- lmer(temp_change ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all) 

#temp_change_mod_noints <- lmer(temp_change ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all) 

#prop_ignite_mod <- lmer(prop_ignite ~ spp * mpa_scaled + spp * lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)

#prop_ignite_mod_noints <- lmer(prop_ignite ~ spp + mpa_scaled + lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)
```

#TTI

Lets just do TTI first: 

```{r}
mem_data_all_tti <- mem_data_all 

tti_mod_noints <- lmer(tti ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all_tti)

r_tti <- remef(tti_mod_noints, fix = c("mpa_scaled","lfm_scaled","site"), ran = list(individual = c("(Intercept)")))

mem_data_all_r <- mem_data_all %>% drop_na(tti, mpa_scaled, lfm_scaled, sample_wt_scaled)
mem_data_all_r$r_tti <- r_tti

tti_plot <- mem_data_all_r %>% 
  ggplot(aes(y = tti, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Time to Ignition (sec)") 
   
tti_plot

tti_plot_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_tti, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Time to Ignition (sec)") 
tti_plot_r

tti_plot_lfm <- mem_data_all_r %>% 
  ggplot(aes(y = tti, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many +theme(legend.position = "none", 
                                 axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Time to Ignition (sec)") 
   
tti_plot_lfm

tti_plot_lfm_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_tti, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Time to Ignition (sec)") 
tti_plot_lfm_r


#ggarrange(tti_plot, tti_plot_r, tti_plot_lfm, tti_plot_lfm_r )
```

#FH

```{r}
fh_mod_noints <- lmer(fh ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

r_fh <- remef(fh_mod_noints, fix = c("mpa_scaled","lfm_scaled","site"), ran = list(individual = c("(Intercept)")))

mem_data_all_r <- mem_data_all %>% drop_na(fh)
mem_data_all_r$r_fh <- r_fh

fh_plot <- mem_data_all_r %>% 
  ggplot(aes(y = fh, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Flame Height (cm)") 
   
fh_plot

fh_plot_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_fh, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Flame Height (cm)") 
fh_plot_r

fh_plot_lfm <- mem_data_all_r %>% 
  ggplot(aes(y = fh, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Flame Height (cm)") 
   
fh_plot

fh_plot_lfm_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_fh, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Flame Height (cm)") 
fh_plot_r

#ggarrange(fh_plot, fh_plot_r, fh_plot_lfm, fh_plot_lfm_r, nrow = 2, ncol = 2)
```
#GD

```{r}
gd_mod <- lmer(gd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

#gd_mod_noints <- lmer(gd ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

r_gd <- remef(gd_mod, fix = c("mpa_scaled","lfm_scaled","site"), ran = list(individual = c("(Intercept)")))

mem_data_all_r <- mem_data_all %>% drop_na(gd)
mem_data_all_r$r_gd <- r_gd

gd_plot <- mem_data_all_r %>% 
  ggplot(aes(y = gd, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Glow Duration (sec)") 
   
gd_plot

gd_plot_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_gd, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Glow Duration (sec)") 
gd_plot_r

gd_plot_lfm <- mem_data_all_r %>% 
  ggplot(aes(y = gd, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Glow Duration (sec)") 
   
gd_plot

gd_plot_lfm_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_gd, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Glow Duration (sec)") 
gd_plot_r

#ggarrange(gd_plot, gd_plot_r, gd_plot_lfm, gd_plot_lfm_r, nrow = 2, ncol = 2)
```

#FD

```{r}
fd_mod <- lmer(fd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

#fd_mod_noints <- lmer(fd ~ spp+ mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

r_fd <- remef(fd_mod, fix = c("mpa_scaled","lfm_scaled","site"), ran = list(individual = c("(Intercept)")))

mem_data_all_r <- mem_data_all %>% drop_na(fd)
mem_data_all_r$r_fd <- r_fd

fd_plot <- mem_data_all_r %>% 
  ggplot(aes(y = fd, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Flame Duration (sec)") 
   
fd_plot

fd_plot_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_fd, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "MPa", 
       y = "Flame Duration (sec)") 
fd_plot_r

fd_plot_lfm <- mem_data_all_r %>% 
  ggplot(aes(y = fd, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Flame Duration (sec)") 
fd_plot

fd_plot_lfm_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_fd, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "LFM", 
       y = "Flame Duration (sec)") 
fd_plot_r

#ggarrange(fd_plot, fd_plot_r, fd_plot_lfm, fd_plot_lfm_r, nrow = 2, ncol = 2)
```

#Temp change
```{r}
temp_change_mod <- lmer(temp_change ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + spp*sample_wt_scaled + (1 | individual), data = mem_data_all) 

performance::check_collinearity(temp_change_mod)
temp_change_mod
AIC(temp_change_mod)
```

```{r}
temp_change_mod <- lmer(temp_change ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all) 

temp_change_mod_noints <- lmer(temp_change ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all) 

r_temp_change <- remef(temp_change_mod, fix = c("mpa_scaled","lfm_scaled","site"), ran = list(individual = c("(Intercept)")))

mem_data_all_r <- mem_data_all %>% drop_na(temp_change)
mem_data_all_r$r_temp_change <- r_temp_change

temp_change_plot <- mem_data_all_r %>% 
  ggplot(aes(y = temp_change, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  +
  labs(x = "", 
       y = "Temp Change (C)") 
temp_change_plot

temp_change_plot_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_temp_change, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Temp Change (C)") 
temp_change_plot_r

temp_change_plot_lfm <- mem_data_all_r %>% 
  ggplot(aes(y = temp_change, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Temp Change (C)") 
temp_change_plot

temp_change_plot_lfm_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_temp_change, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Temp. Change (C)") 
temp_change_plot_r

#ggarrange(temp_change_plot, temp_change_plot_r, temp_change_plot_lfm, temp_change_plot_lfm_r, nrow = 2, ncol = 2)
```

#Prop. ignite

```{r}
prop_ignite_mod <- lmer(prop_ignite ~ spp * mpa_scaled + spp * lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)

prop_ignite_mod_noints <- lmer(prop_ignite ~ spp + mpa_scaled + lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)

r_prop_ignite <- remef(prop_ignite_mod, fix = c("mpa_scaled","lfm_scaled","site"), ran = list(individual = c("(Intercept)")))

mem_data_all_r <- mem_data_all %>% drop_na(prop_ignite)
mem_data_all_r$r_prop_ignite <- r_prop_ignite

prop_ignite_plot <- mem_data_all_r %>% 
  ggplot(aes(y = prop_ignite, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many +
  labs(x = "", 
       y = "Proportion Ignited (%)") 
prop_ignite_plot

prop_ignite_plot_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_prop_ignite, 
             x = mpa_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22))+
  labs(x = "", 
       y = "Proportion Ignited (%)") 
prop_ignite_plot_r

prop_ignite_plot_lfm <- mem_data_all_r %>% 
  ggplot(aes(y = prop_ignite, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many +
  labs(x = "", 
       y = "Proportion Ignited (%)") 
prop_ignite_plot

prop_ignite_plot_lfm_r <- mem_data_all_r %>% 
  ggplot(aes(y = r_prop_ignite, 
             x = lfm_scaled, 
             color = spp)) +
  geom_point(alpha= .6)+
  geom_smooth(method = "lm", se = F) + 
  color_many  + theme(legend.position = "none",                                   axis.text = element_text(size = 14), axis.title = element_text(size = 22)) +
  labs(x = "", 
       y = "Proportion Ignited (%)") 
  
prop_ignite_plot_lfm_r

#ggarrange(prop_ignite_plot, prop_ignite_plot_r, prop_ignite_plot_lfm, prop_ignite_plot_lfm_r, nrow = 2, ncol = 2)
```

It looks like it doesnt make a huge difference if we use remeff or not, so we'll go ahead and use it.
Now, putting all figures together, remeff only: 

#All together

```{r}
plot_legend <- mem_data_all %>% 
  ggplot(aes(x = tti, y = mpa, color = spp)) +
  geom_point() +
  color_many  +
  labs(color = "Species") +
  theme(legend.text = element_text(size = 16), 
        legend.title = element_text(size = 22))

legend <- cowplot::get_legend(plot_legend)
```

####MPas:
```{r, fig.height=5, fig.width=9}
#Mpas:
plots <- cowplot::plot_grid(prop_ignite_plot_r, 
          temp_change_plot_r, 
          tti_plot_r,
          fh_plot_r, 
          fd_plot_r,
          gd_plot_r
          #, 
         # ncol = 3, 
         # nrow = 2, 
          )
plots
plots_legend <- cowplot::plot_grid(plots, legend, rel_widths = c(5, .6))
plots_legend

#ggsave(plot=plots_legend, bg = "white" , here::here("figures", "mpa_flam_metrics_scaled_ungrouped"), device="jpg")
```

####LFMs:
```{r, fig.height=5, fig.width=9}
plots <- cowplot::plot_grid(prop_ignite_plot_lfm_r, 
          temp_change_plot_lfm_r, 
          tti_plot_lfm_r,
          fh_plot_lfm_r, 
          fd_plot_lfm_r,
          gd_plot_lfm_r
          #, 
         # ncol = 3, 
         # nrow = 2, 
          )
plots
plots_legend <- cowplot::plot_grid(plots, legend, rel_widths = c(5, .6))
plots_legend

#ggsave(plot=plots_legend, bg = "white" , here::here("figures", "lfm_flam_metrics_scaled_ungrouped"), device="jpg")
```
#3. Species differences: 

####Data

```{r}
tidy_data <- read_csv(here::here("processed-data", "tidy_all_mems.csv")) %>% 
  add_row(term = c("sppabco", "sppabco", "sppabco", "sppabco", "sppabco", "sppabco"),
          estimate =c(0,0,0,0,0,0), 
          y_var = c("fh", "fd", "tti", "gd", "prop_ignite", "temp_change")) %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  mutate(species = case_when(
    term == "sppabco" ~ "A. concolor",
       term ==                "spparpa" ~ "A. patula",
        term ==               "sppcade" ~ "C. decurrens", 
         term ==              "sppceco" ~ "C. cordulatus", 
         term ==              "spppije" ~ "P. jefferyi",
          term ==             "sppquke" ~ "Q. kelloggii"
  )) %>% 
    mutate(y_var_name= case_when(
    y_var == "tti" ~ "Time to ignition",
       y_var ==                "fh" ~ "Flame height",
        y_var ==               "fd" ~ "Flame duration", 
         y_var ==              "prop_ignite" ~ "Prop. ignited", 
         y_var ==              "temp_change" ~ "Temp. change",
          y_var ==             "gd" ~ "Glow duration"
  ))
```
```{r}
unique(tidy_data$term)
```

###Species effects: 

```{r, fig.height=3, fig.width=6}
spp_estimates <- tidy_data  %>% 
  filter(term %in% c("sppabco",
                     "spparpa", 
                     "sppcade" ,
                     "sppceco",
                     "spppije",
                     "sppquke"                 
                     )) %>% 
  ggplot(
    aes(color= species)
    ) + 
  geom_point(aes(x = estimate,y = species), size =3) +
    geom_point(aes(x = upr, y = species), size = 1) +
  geom_point(aes(x = lwr, y = species), size = 1) +
  #geom_line(aes(group = species, y = species, x = upr)) +
  geom_segment(aes(x= lwr, xend = upr, y = species, yend = species, color = species))+
  labs(y = "", 
       color = "Species", 
       x = "Estimate") +
    facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  axis.text.y = element_blank(), axis.ticks.y = element_blank()
)+
  geom_vline(xintercept = 0,
             linetype="dotted") +
  color_many 
spp_estimates

#ggsave(plot=spp_estimates, bg = "white" , here::here("figures", "spp_estimates_flam_metrics_withceco_scaled_ungrouped"), device="jpg")
```

