---
title: "RWC x LFM"
author: "Indra Boving"
date: "10/24/2021"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, results='hide', warning= FALSE)
options(knitr.duplicate.label = "allow")
library(here)
library(janitor)
library(tidyverse)
library(plotly)
library(DT)
library(broom)
library(lubridate)
library(udpipe)
library(equatiomatic)
library(MuMIn)
# rmarkdown::render('lfm_rwc_Rmd', output_file = here("htmls", "lfm_rwc_html"))
```

# Section 1: Pressure Volume Curves

```{r}
data <- read_csv(here("processed-data", "allcurves_clean.csv"), show_col_types = FALSE) %>% 
  mutate(sample = as.factor(sample)) %>% 
  mutate(month = as.factor(month)) %>% 
  mutate(date = date(date)) %>% 
  clean_names()
```
 
### 1.1: Variation in TLPs
 
Look at just one species and timepoint: ABCO and fall

```{r}
pv_all <- data 

ggplot(pv_all) +
  geom_point(aes(x = rwd, y = -1/water_potential, 
                 color = as.factor(date)), 
             size = .5, alpha = .5) +
  facet_wrap(~spp) +
  #theme_light() +
  labs(x = "Relative Water Deficit", 
       y = "-1/Water potential")

pv_fall_summary <- data %>%
  group_by(date, spp) %>% 
  filter(timing == "fall" ) %>% 
  summarise(n=n(), mean=mean(tlp),sd=sd(tlp)) %>% 
  mutate(year = year(date), 
         month = month(date))
```
...Fix this if we want to use it. 
```{r}
ggplot(pv_fall_summary) +
    geom_bar(aes(y = mean, 
                 x = year), 
             position="dodge", 
             stat="identity", 
             fill = "lightblue", 
             alpha = .5) +
    geom_errorbar(aes(x= year, 
                      ymin=mean-sd, 
                      ymax=mean+sd), 
                  width=.4, colour="black", alpha=0.9) +
   labs(title = "All TLPs, fall dates") +
  facet_wrap(~spp, scales = "free")
   #theme_light()
```

In fall and spring: 

- fall both dates combined ()

```{r}
# pv_summary <- data %>%
#   group_by(timing) %>% 
#  # filter(spp == "ABCO") %>% 
#   summarise(n=n(), mean=mean(tlp),sd=sd(tlp))
# 
#  ggplot(pv_summary) +
#     geom_bar(aes(y = mean, x = timing), position="dodge", stat="identity", fill = "lightblue", alpha = .5) +
#     geom_errorbar(aes(x=timing, ymin=mean-sd, ymax=mean+sd), width=0_4, colour="black", alpha=0_9) +
#    labs(title = "ABCO TLP, all dates", 
#         y = "TLP (-Mpa)", 
#         x = "timing") +
#    #theme_light()
```

See if sig. difference in TLP for each spp: 

```{r, include = TRUE}
for (i in unique(pv_all$spp)) {
#Split df into groups, then pull sample vectors
fall_spp <- pv_all %>% 
  filter(timing == "fall", 
         spp == i) %>% 
  group_by(sample) %>% 
  arrange(water_potential) %>%
  filter(row_number()==1) %>% 
  pull(tlp)

spring_spp <- pv_all %>% 
  filter(timing == "spring", spp == i) %>% 
   group_by(sample) %>% 
  arrange(water_potential) %>%
  filter(row_number()==1) %>% 
  pull(tlp)

spp_tlp_t <- t.test(spring_spp, fall_spp)
spp_tlp_t 

t_test_out <- c(i, spp_tlp_t)
}
```


### 1.2: Try to predict Mpa from LFM with just one species

1.  Get datasets in order:

-   select for just the species and date we are interested in
-   remove any anomalous curves
-   pull the TLP as a value
-   make two sub-datasets: one for all points above the TLP, one for all points below the TLP

```{r message=FALSE, warnings=F}
pv_fall <- data %>%
  filter(
    #spp == "ABCO" &
           timing == "fall" )  %>% 
  mutate(sample = as.numeric(sample)) %>% 
  filter(!(spp == "PIJE" & sample == 7)) %>% 
  filter(!(spp == "QUKE" & sample == 2)) %>% 
  filter(!(spp == "ARPA" & sample == 5 & !month == 10)) 

fall_tlp <- pv_fall %>% 
  group_by(spp) %>% 
  summarise(mean(tlp)) %>% pull()

fall_sd <- pv_fall %>% 
  group_by(spp) %>% 
  summarise(sd(tlp)) %>% pull()
```

For fall PV curves, the mean TLP = `r round(mean(fall_tlp,2))`, sd = `r round(mean(fall_sd,2))`

```{r, echo=FALSE, message=FALSE, results='hide'}
pv_fall %>% 
  ggplot(aes(y = water_potential, 
             x = lfm, 
             color = as.factor(date))
         ) +
  geom_point(alpha = .5, size = .5) +
  geom_hline(yintercept = fall_tlp,
             colour = "lightblue") +
  facet_wrap(~spp) +
  labs(title = "Pressure Volume Curves, LFM x Mpa", 
       x = "LFM (%)", y = "Mpa") 

  #theme_light()
```
Subset data based on TLP: 

```{r}
all_above_tlp <- pv_fall %>% 
  group_by(spp) %>% 
  filter(water_potential > tlp) 
# %>% 
#   filter(lfm < 200, lfm > 90)

all_below_tlp <- pv_fall %>% 
   group_by(spp) %>% 
  filter(water_potential < tlp)
```

#### 2.  For points BELOW the TLP, there should be a linear relationship between -1/Mpa and LFM

```{r}
all_below_tlp %>% 
ggplot(aes(y = -1/water_potential, 
           x = lfm, 
           color = as.factor(sample), 
           shape = as.factor(month))) +
  geom_jitter(alpha = .6, size = 1) +
  geom_smooth(method = "lm", se = FALSE, size = .5, alpha = .5) +
  labs(y = "-1/Mpa", x = "LFM (%)") +
  facet_wrap(~spp, scales = "free")
  #theme_light()

fit_below_all <-lm(-1/water_potential~lfm + spp, all_below_tlp)

summary(fit_below_all)

mpa_predicted_r <- predict.lm(fit_below_all, newdata = data_frame(lfm = 180, spp = "CADE")) %>% #180 is a random num
  as.numeric() #use this to extract lfm
mpa_predicted_r

mpa_predicted_r <- predict.lm(fit_below_all, newdata = data_frame(lfm = 180, spp = "ABCO")) %>% #180 is a random num
  as.numeric() #use this to extract lfm
mpa_predicted_r
```

#### 2.1. Try adding in other predictors: 
```{r}
options(na.action = "na.fail") # Required for dredge to run 

fit_below_all <- MuMIn::dredge(lm(-1/water_potential~lfm + po + swc + rwc_at_tlp + spp, all_below_tlp))

options(na.action = "na.omit") # set back to default

head(fit_below_all)
```

This is the model that dredge() likes the best: 

```{r}
top_model_below <- get.models(fit_below_all, subset = 1)[[1]]
summary(top_model_below)
```
 

VIFs:
```{r}
car::vif(top_model_below) ##
plot(top_model_below)
#VIF is ok: less than 4 for mpa and LFM_
extract_eq(top_model_below)
```

 Unfortunately, it's unlikely that we'd know the swc, but we can use spp means for po and rwc at tlp. Lets try with just po though
 
 
#### 3.  For points ABOVE the TLP, there should be a linear relationship between Mpa and lfm

```{r}
ggplot(data = all_above_tlp, aes(y = water_potential, 
                                 x = lfm, 
                                 color = spp, 
                                 shape = as.factor(date))) +
  geom_jitter(alpha = .6, size = 1) +
  geom_smooth(method = "lm", se = FALSE, size = .5, alpha = .5) +
labs(y = "Mpa", x = "LFM (%)")
  #theme_light()
```
Looks like maybe date really matters for CECO? Weird... 

```{r}
fit_above_all <- lm(water_potential ~ lfm + spp, all_above_tlp)
summary(fit_above_all)

lfm_predicted_r_fit1 <- predict.lm(fit_above_all, newdata = data.frame(lfm = 150, spp = "CADE")) %>% 
  as.numeric() #use this to extract lfm
lfm_predicted_r_fit1
```

Try some models based on what we'd probably know: 

```{r}
#Adding in po might help model?
fit2 <- lm(water_potential ~ lfm + po + spp, all_above_tlp)
summary(fit2)

broom::tidy(fit2)

lfm_predicted_r <- predict.lm(fit2, newdata = data.frame(lfm = 150, po = -1.42, spp = "CADE")) %>% as.numeric() #use this to extract lfm
lfm_predicted_r
```

We have some linear models that should be able to predict Mpa from LFM_ Now, to test it out___

#### 3.1. Try adding in other predictors: 
```{r}
options(na_action = "na_fail") # Required for dredge to run 

fit_above_all <- MuMIn::dredge(lm(water_potential~ lfm + po + swc + rwc_at_tlp, all_above_tlp))

options(na_action = "na_omit") # set back to default

head(fit_above_all)
```

This is the model that dredge() likes the best: 

```{r}
top_model_above <- get_models(fit_above_all, subset = 1)[[1]]
summary(top_model_above)
```
 
VIFs:
```{r}
car::vif(top_model_above) ##
plot(top_model_above)
#VIF is ok: less than 4 for mpa and LFM_
```

# Sections 2-3: Can we predict actual values using the models built from the PV curves?

### 2.1: Flam-curve values

- Read in flam curve data

```{r}
flam_curve_phys_all_raw <- read_csv(here("processed-data", "analysis 2.0", "flam_curve_phys_all.csv"), show_col_types = FALSE)

flam_curve_predict_df <- flam_curve_phys_all_raw %>% 
  mutate(water_potential = -1*pos_mpa, 
         swc = swc_sat) %>% 
  select(spp, swc, lfm, mpa, month, tlp, water_potential, po)
```

- Use `predict()` to see if we can use PV curve models to get values collected during flammability curve testing. 

```{r}
#Our models: 
pretty1 <- extract_eq(fit_below_all)
pretty1
pretty2 <- extract_eq(fit_above_all)
pretty2

summary(fit_below_all)
```

We're just interested in ABCO, so just look there: 

```{r}
flam_curve_phys_above <- flam_curve_predict_df %>% 
 # filter(rwc_new < 100) %>% 
 # filter(spp == "ABCO") %>% 
  filter(water_potential > tlp)

flam_curve_phys_below <- flam_curve_predict_df %>% 
 # filter(rwc_new < 100) %>% 
 # filter(spp == "ABCO") %>% 
  filter(water_potential < tlp)
```

###  2.2 Predict below TLP: 

#### 2.2.1 Simple model - below: 

```{r}
fit_below_all <-lm(-1/water_potential~lfm + spp, all_below_tlp)

predict_below <- predict(fit_below_all, 
                         newdata = flam_curve_phys_below, 
                         se_fit = TRUE, 
                         interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_below <- data.frame(flam_curve_phys_below, predict_below)

predict_df_below %>% 
  ggplot(aes(y = -1/water_potential, 
             x = fit, 
         color = spp)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
 # ylim(0, 1) +
 # xlim(0, 1) +
  labs(title = "Actual vs predicted water potential for points BELOW the TLP", 
       y = "Actual -1/Mpa", 
       x = "Predicted -1/Mpa")
   #theme_light() 
```



```{r, echo = FALSE, messages = "hide", warning = FALSE}
predict_graph_below <- ggplot(predict_df_below, aes(x = lfm, 
                                                    y = fit)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_point(data = flam_curve_phys_below, 
             aes(x = lfm, y = -1/water_potential), 
             alpha = 0.7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Predicted (lightblue) vs_ observed (black) LFM and Mpa for point BELOW the TLP") 
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_below
```

#### 2.2.2. Complex model  - below: 

1. all possible inclusions: 

```{r}
complex_model_below <- lm(formula = -1/water_potential ~ lfm + swc + po + spp + 1, data = all_below_tlp)

predict_below <- predict(complex_model_below, newdata = flam_curve_phys_below, se_fit = TRUE, interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_below <- data.frame(flam_curve_phys_below, predict_below)

predict_df_below %>% 
  ggplot(aes(y = -1/water_potential, 
             x = fit, 
             color = spp)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
 # ylim(0, 1) +
 # xlim(0, 1) +
  labs(title = "Complex model: Actual vs_ predicted, BELOW the TLP", 
       y = "Actual -1/Mpa", 
       x = "Predicted -1/Mpa") 
   #theme_light() 



predict_df_below %>% 
  ggplot(aes(y = water_potential, 
             x = -1/fit, 
             color = spp)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, -5) +
  xlim(0, -5) +
  labs(title = "Complex model: Actual vs. predicted BELOW the TLP", 
       y = "Actual Mpa", 
       x = "Predicted Mpa") 
   #theme_light() 

predict_graph_below <- 
  ggplot(predict_df_below, aes(x = lfm, y = fit)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_point(data = flam_curve_phys_below, aes(x = lfm, y = -1/mpa), alpha = 0.7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Complex model: Predicted (lightblue) vs_ observed (black) LFM and Mpa for point BELOW the TLP (ABCO)") 
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_below
```

2. all just po + lfm

```{r}
complex_model_below <- lm(formula = -1/water_potential ~ lfm +  po + spp + 1, data = all_below_tlp)

predict_below <- predict(complex_model_below, newdata = flam_curve_phys_below, se_fit = TRUE, interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_below <- data.frame(flam_curve_phys_below, predict_below)

predict_df_below %>% 
  ggplot(aes(y = -1/water_potential, 
             x = fit, 
             color = spp)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
 # ylim(0, 1) +
 # xlim(0, 1) +
  labs(title = "Complex model: Actual vs_ predicted, BELOW the TLP", 
       y = "Actual -1/Mpa", 
       x = "Predicted -1/Mpa") 
   #theme_light() 



predict_df_below %>% 
  ggplot(aes(y = water_potential, 
             x = -1/fit, 
             color = spp)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, -5) +
  xlim(0, -5) +
  labs(title = "Complex model: Actual vs. predicted BELOW the TLP", 
       y = "Actual Mpa", 
       x = "Predicted Mpa") 
   #theme_light() 

predict_graph_below <- 
  ggplot(predict_df_below, aes(x = lfm, y = fit)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_point(data = flam_curve_phys_below, aes(x = lfm, y = -1/mpa), alpha = 0.7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Complex model: Predicted (lightblue) vs_ observed (black) LFM and Mpa for point BELOW the TLP (ABCO)") 
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_below
```

####2.2.3. Simple model - above: 

```{r}
fit_above_all <- lm(water_potential ~ lfm + spp, all_above_tlp)
summary(fit_above_all)

predict_above <- predict(fit_above_all, newdata = flam_curve_phys_above, se_fit = TRUE, interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_above <- data_frame(flam_curve_phys_above, predict_above)

predict_df_above %>% 
  ggplot(aes(y = water_potential, x = fit_fit)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, -3) +
  xlim(0, -3) +
  labs(title = "Actual vs_ predicted water potential for points ABOVE the TLP", 
       y = "Actual Mpa", 
       x = "Predicted Mpa") +
   #theme_light() 

predict_graph_above <- ggplot(predict_df_above, 
                              aes(x = lfm, y = fit)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_point(data = flam_curve_phys_above, aes(x = lfm, y = mpa), alpha = 0.7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Predicted (lightblue) vs_ observed (black) LFM and Mpa for points ABOVE the TLP (ABCO)") +
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_above
```


#### 2.2.4 Complex model - above: 

1. all possible predictors: 
```{r}
complex_model_above <- lm(formula = water_potential ~ lfm + swc + po + spp + 1, data = all_above_tlp)


predict_above <- predict(complex_model_above, newdata = flam_curve_phys_above, se_fit = TRUE, interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_above <- data.frame(flam_curve_phys_above, predict_above)

predict_df_above %>% 
  ggplot(aes(y = water_potential, x = fit)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, -3) +
  xlim(0, -3) +
  labs(title = "Complex: Actual vs_ predicted water potential for points ABOVE the TLP", 
       y = "Actual Mpa", 
       x = "Predicted Mpa") 

predict_graph_above <- ggplot(predict_df_above, aes(x = lfm, y = fit)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_point(data = flam_curve_phys_above, aes(x = lfm, y = mpa), alpha = 0.7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Complex: Predicted (lightblue) vs_ observed (black) LFM and Mpa for points ABOVE the TLP (ABCO)") 
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_above
```
1. just po, lfm, and spp

```{r}
complex_model_above <- lm(formula = water_potential ~ lfm + po + spp + 1, data = all_above_tlp)


predict_above <- predict(complex_model_above, newdata = flam_curve_phys_above, se_fit = TRUE, interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_above <- data.frame(flam_curve_phys_above, predict_above)

predict_df_above %>% 
  ggplot(aes(y = water_potential, x = fit)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, -3) +
  xlim(0, -3) +
  labs(title = "Complex: Actual vs_ predicted water potential for points ABOVE the TLP", 
       y = "Actual Mpa", 
       x = "Predicted Mpa") 

predict_graph_above <- ggplot(predict_df_above, aes(x = lfm, y = fit)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_point(data = flam_curve_phys_above, aes(x = lfm, y = mpa), alpha = 0.7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Complex: Predicted (lightblue) vs_ observed (black) LFM and Mpa for points ABOVE the TLP (ABCO)") 
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_above
```

### 3.1: Field data

#HERE: Nov. 4

This data is from measurements of predawn and midday Mpa, and midday measured LFM_ SWC is equivalent to the wettest lfm measured for each invidual divided by 100 to get *grams water/grams dry*_ 

- Use `predict()` to see if we can use PV curve models to get values collected in the field (predict midday Mpa from LFM): 

```{r}
field_data_all <- read_csv(here("processed-data", "field_data_csv"), show_col_types = FALSE) %>% 
  filter(spp == "ABCO")
```

We're just interested in ABCO, so just look there: 

```{r}
field_data_above <- field_data_all %>% 
  filter(water_potential > tlp)

field_data_below <- field_data_all %>% 
  filter(water_potential < tlp)
```

#### 3.2.1 Simple model - above

```{r}
eq <-extract_eq(fit_below_all)
eq
```

```{r}
predict_below <- predict(fit_below_all, newdata = field_data_below, se_fit = TRUE, interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_below <- data_frame(field_data_below, predict_below)

predict_df_below %>% 
  ggplot(aes(y = -1/water_potential, x = fit_fit)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, 1) +
  xlim(0, 1) +
  labs(title = "Actual vs_ predicted water potential for points BELOW the TLP (ABCO)", 
       y = "Actual -1/Mpa", 
       x = "Predicted -1/Mpa") +
   #theme_light() 

predict_df_below %>% 
  ggplot(aes(y = water_potential, x = -1/fit_fit)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, -5) +
  xlim(0, -5) +
  labs(title = "Actual vs_ predicted for points BELOW TLP (ABCO)", 
       y = "Actual Mpa", 
       x = "Predicted Mpa") +
   #theme_light() 
```


```{r, echo = FALSE, messages = "hide", warning = FALSE}
predict_graph_below <- ggplot(predict_df_below, aes(x = lfm, y = fit_fit)) +
  geom_point(color = "lightblue", alpha = 0_7) +
  geom_point(data = field_data_below, aes(x = lfm, y = -1/water_potential), alpha = 0_7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Predicted (lightblue) vs_ observed (black) LFM and Mpa BELOW TLP (ABCO)") +
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_below
```

#### 3.2.2. Complex model  - below: 

Since we don't have Po for the field data, so we'll have to do the best we can_ 

```{r}
complex_model_below <- lm(formula = -1/water_potential ~ lfm + swc + 1, data = all_below_tlp)

eq <-extract_eq(complex_model_below)
eq
```

```{r}
predict_below <- predict(complex_model_below, newdata = field_data_below, se_fit = TRUE, interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_below <- data_frame(field_data_below, predict_below)

predict_df_below %>% 
  ggplot(aes(y = -1/water_potential, x = fit_fit)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, 1) +
  xlim(0, 1) +
  labs(title = "ABCO - Complex model: Actual vs_ predicted, BELOW the TLP", 
       y = "Actual -1/Mpa", 
       x = "Predicted -1/Mpa") +
   #theme_light() 
```


```{r}
predict_df_below %>% 
  ggplot(aes(y = water_potential, x = -1/fit_fit)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, -5) +
  xlim(0, -5) +
  labs(title = "ABCO - Complex model: Actual vs_ predicted BELOW the TLP", 
       y = "Actual Mpa", 
       x = "Predicted Mpa") +
   #theme_light() 
```


```{r, echo = FALSE, messages = "hide", warning = FALSE}
predict_graph_below <- ggplot(predict_df_below, aes(x = lfm, y = fit_fit)) +
  geom_point(color = "lightblue", alpha = 0_7) +
  geom_point(data = flam_curve_phys_below, aes(x = lfm, y = -1/mpa), alpha = 0_7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Complex model: Predicted (lightblue) vs_ observed (black) LFM and Mpa for point BELOW the TLP (ABCO)") +
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_below
```

#### 3.2.3 Simple model - above

```{r}
eq <- extract_eq(fit_above_all)
eq
```

```{r}
predict_above <- predict(fit_above_all, newdata = field_data_above, se_fit = TRUE, interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_above <- data_frame(field_data_above, predict_above)

predict_df_above %>% 
  ggplot(aes(y = water_potential, x = fit_fit)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, -3) +
  xlim(0, -3) +
  labs(title = "Actual vs_ predicted water potential for points ABOVE the TLP (ABCO)", 
       y = "Actual Mpa", 
       x = "Predicted Mpa") +
 #theme_light() 
```

```{r, echo = FALSE, messages = "hide", warning = FALSE}
predict_graph_above <- ggplot(predict_df_above, aes(x = lfm, y = fit_fit)) +
  geom_point(color = "lightblue", alpha = 0_7) +
  geom_point(data = field_data_above, aes(x = lfm, y = water_potential), alpha = 0_7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Predicted (lightblue) vs_ observed (black) LFM and Mpa for points ABOVE the TLP (ABCO)")+
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_above
```

#### 3.2.4 Complex model - above: 

```{r}
complex_model_above <- lm(formula = water_potential ~ lfm + swc + 1, data = all_above_tlp)

eq <-extract_eq(complex_model_above)
eq
```

```{r}
predict_above <- predict(complex_model_above, newdata = field_data_above, se_fit = TRUE, interval = "confidence") #make prediction

# Bind to the data to make it actually useful:

predict_df_above <- data_frame(field_data_above, predict_above)

predict_df_above %>% 
  ggplot(aes(y = water_potential, x = fit_fit)) +
  geom_point() +
  geom_abline(method = lm) +
  geom_abline(color = "red") +
  ylim(0, -3) +
  xlim(0, -3) +
  labs(title = "Complex: Actual vs_ predicted water potential for points ABOVE the TLP", 
       y = "Actual Mpa", 
       x = "Predicted Mpa") +
   #theme_light() 
```

```{r, echo = FALSE, messages = "hide", warning = FALSE}
predict_graph_above <- ggplot(predict_df_above, aes(x = lfm, y = fit_fit)) +
  geom_point(color = "lightblue", alpha = 0_7) +
  geom_point(data = flam_curve_phys_above, aes(x = lfm, y = mpa), alpha = 0_7) +
 # facet_wrap(~St) +
  labs(x = "LFM (%)", 
       y = "Water Potential (Mpa)", 
       title = "Complex: Predicted (lightblue) vs_ observed (black) LFM and Mpa for points ABOVE the TLP (ABCO)") +
 # scale_x_continuous(limits = c(500,3500), breaks = seq(500, 3500, by = 1000)) +
 # scale_y_continuous(limits = c(0,1.5e6))
  #theme_light() 
predict_graph_above
```
