---
title: "Mixed Effects Models"
author: "Indra Boving & Joe Celebrezze"
date: "6/21/2022"
output: html_document
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#lots of extra here, but oh well... 
library(ggplot2)
library(gapminder)
library(data.table)
library(purrr) #for visualizing all variables in one big plot
library(naniar) #for dealing with NAs nicely 
library(tidyverse)
library(devtools)
library(ggfortify)
library(ggpubr)
library(jtools)
library(cowplot)
library(lmerTest)
library(ggeffects)  
library(GGally) #for corr plots
require(kimisc) # has the nlist function to create a named list
require(AICcmodavg) # has the aictab function
library(psych)

#devtools::install_github("strengejacke/strengejacke")
library(strengejacke)
library(sjPlot) # table functions
library(sjmisc) # sample data
library(lme4) # fifhng models
library(here)
library(effects) #for plofhng model effects
library(sjstats) #use for r2 functions
library(TMB)
library(glmmTMB)
library(lattice)
library(equatiomatic)
library("broom.mixed")
#library(ggbiplot)
select = dplyr::select
here = here::here
library(MuMIn)
library(modelsummary)
#install_github("BlakeRMills/MetBrewer") 
#library("BlakeRMills/MetBrewer")
#library(memmented)
filter = dplyr::filter
mutate = dplyr::mutate
library(nlme)
library(MetBrewer)
#install.packages("memmented")
#devtools::install_github("hohenstein/remef")
library(remef)
library(kableExtra)
```

#------------------------------------
# 1. Data wrangling
Reading in dataframe

- For the Sierra analysis, this is combining all species and dropping the august sampling data (not enough samples and it was measured a lil differently). 

```{r}
mem_data_all <- read_csv(here("processed-data", "analysis 2.0", "sierra_flam_data_all.csv")) %>% 
  select(lfm, mpa, fh, fh, fd, gd,tti, prop_ignite, temp_change, ignition, sample_wt, dry_wt, fresh_wt, water_wt, location, site, year_month, spp, individual) %>% 
  mutate(dw_flam_sample = sample_wt * (dry_wt/fresh_wt),
         ww_flam_sample = sample_wt * (water_wt/fresh_wt)) %>% 
  mutate(excess_water = (ww_flam_sample - dw_flam_sample)) %>% 
   #group_by(spp) %>% 
  mutate(mpa = -1*mpa,
    mpa_scaled = scale(mpa),
         dw_flam_sample_scaled = scale(dw_flam_sample), 
         sample_wt_scaled = scale(sample_wt), 
         ww_flam_sample_scaled = scale(ww_flam_sample),
         lfm_scaled = scale(lfm), 
         excess_water_scaled = scale(excess_water)) %>% 
  filter(!year_month %in% c("2021_august")) %>% 
  drop_na(mpa_scaled, lfm_scaled, sample_wt_scaled)
```

#Visualize: 
```{r}
mem_data_all %>% 
  ggplot(aes(y = fh, 
             x = sample_wt, 
             color = spp)) +
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", se = F)
```


#Top models by metric: 

##Flame height: 

```{r}
sw_m1 <- lmer(fh ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + spp*sample_wt_scaled + (1 | individual), data = mem_data_all)
AIC(sw_m1)
BIC(sw_m1)
performance::multicollinearity(sw_m1)

sw_m1 <- lmer(fh ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + spp*sample_wt_scaled + (1 | individual), data = mem_data_all)
```

```{r}
sw_m1.5 <- lmer(fh ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
AIC(sw_m1.5)
performance::multicollinearity(sw_m1.5)
```

```{r}
m2 <- lmer(fh ~ spp * mpa_scaled + spp* lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)
AIC(m2)
BIC(m2)
x <- performance::multicollinearity(m2)
x <- performance::check_collinearity(m2)
#plot(x)
```

```{r}
m12 <- lmer(fh ~ excess_water_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)
performance::multicollinearity(m12)
```

```{r}
m7 <- lmer(fh ~ mpa_scaled + lfm_scaled+ spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m7)
```

```{r}
m10 <- lmer(fh ~ lfm_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)

qqnorm(resid(m10))
r <- resid(m10)
plot(fitted(m10), r)

performance::multicollinearity(m10)
```

 
```{r}
tab_model(m10, m12, m7, m2,
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          dv.labels = c(
            "m10", 
            "m12",
            "m7", 
            "m2"),
         string.pred = "Coeffcient", 
  string.p = "P-Value", 
  p.style = "stars"
  ) 
```

Best models for FH: 

######final model


```{r}
sw_m1 <- lmer(fh ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
AIC(sw_m1)
BIC(sw_m1)
performance::multicollinearity(sw_m1)
qqnorm(resid(sw_m1))
r <- resid(sw_m1)
plot(fitted(sw_m1), r)

```


```{r}
# m7_fh <- lmer(fh ~ mpa_scaled + lfm_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)
# AIC(m7_fh)
# qqnorm(resid(m7_fh))
# r <- resid(m7_fh)
# plot(fitted(m7_fh), r)
# 
# performance::multicollinearity(m7_fh)
```


```{r}
tidy_fh <- broom.mixed::tidy(sw_m1)%>% 
  mutate(y_var = "fh")

fh_mod <- lmer(fh ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

fh_mod_noints <- lmer(fh ~ mpa_scaled + lfm_scaled + spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
```


##Time to ignition: 

```{r}
m11 <- lmer(tti ~ mpa_scaled*spp + site + year_month + (1 | individual), data = mem_data_all)
AIC(m11)
performance::multicollinearity(m11)

m11.5 <- lmer(tti ~ mpa_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)
AIC(m11.5)
performance::multicollinearity(m11.5)
```

```{r}
sw_m12.5 <- lmer(tti ~ excess_water_scaled + mpa_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
AIC(sw_m12.5)
performance::multicollinearity(sw_m12.5) ##High correlation! Don't use
```

```{r}
sw_m1 <- lmer(tti ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
AIC(sw_m1)
performance::multicollinearity(sw_m1)
```

```{r}
m2 <- lmer(tti ~ spp * mpa_scaled + spp* lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)
AIC(m2)
performance::multicollinearity(m2)
```

```{r}
m7 <- lmer(tti ~ mpa_scaled + lfm_scaled+ spp + site + year_month + (1 | individual), data = mem_data_all)
AIC(m7)
performance::multicollinearity(m7)
```

```{r}
sw_m11 <- lmer(tti ~ mpa_scaled*spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
AIC(sw_m11)
performance::multicollinearity(sw_m11)
```

```{r}
tab_model(sw_m11, m7, m2, sw_m1, sw_m12.5, m11,
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          dv.labels = c(
            "sw_m11", 
            "m7",
            "m2", 
            "sw_m1",
            "sw_m12.5", 
            "m11"),
         string.pred = "Coeffcient", 
  string.p = "P-Value", 
  p.style = "stars"
  ) 
```

Best model for TTI: 

```{r}
mem_data_all %>% 
ggplot(aes(y = tti, 
           x = mpa, color = spp)) +
  geom_point()+
  geom_smooth(method = "lm")
```


```{r}
mem_data_all %>% 
ggplot(aes(y = tti, 
           x = lfm, 
           color = spp)) +
  geom_point()+
  geom_smooth(method = "lm")
```


```{r}
m2 <- lmer(tti ~ spp * mpa_scaled + spp* lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m2)

qqnorm(resid(m2))
r <- resid(m2)
plot(fitted(m2), r)
```

######final model

```{r}
#This is the best model: 
m11 <- lmer(tti ~ spp*mpa_scaled + spp*lfm_scaled + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
AIC(m11)
BIC(m11)
performance::multicollinearity(m11)
```


```{r}
#check VIF when not in the same model: 
m11.5 <- lmer(tti ~ spp*mpa_scaled + spp*lfm_scaled + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
AIC(m11.5)
performance::multicollinearity(m11.5)
```



```{r}
qqnorm(resid(m11))
r <- resid(m11)
plot(fitted(m11), r)

tidy_tti <- broom.mixed::tidy(m11)%>% 
  mutate(y_var = "tti")

tti_mod <- lmer(tti ~ spp*mpa_scaled + spp*lfm_scaled + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

tti_mod_noints <- lmer(tti ~ mpa_scaled + lfm_scaled + spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
```

##Glow duration: 

```{r}
sw_m1 <- lmer(gd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1)
```

```{r}
sw_m2 <- lmer(gd ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m2)
```

```{r}
sw_m11 <- lmer(gd ~ mpa_scaled*spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m11)
```

```{r}
m15 <- lmer(gd ~ excess_water_scaled * spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m15)
```


```{r}
m11 <- lmer(gd ~ mpa_scaled*spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m11)
```

```{r}
tab_model(sw_m2,
  sw_m1, 
          sw_m11, 
          m15, 
          m11,
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          dv.labels = c(
            "sw_m2",
            "sw_m1",
            "sw_m11", 
            "m15",
            "m11"),
         string.pred = "Coeffcient", 
  string.p = "P-Value", 
  p.style = "stars"
  ) 
```

Best model for glow duration: 

######final model

```{r}
sw_m1 <- lmer(gd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1)
plot(performance::check_collinearity(sw_m1))

qqnorm(resid(sw_m1))
r <- resid(sw_m1)
plot(fitted(sw_m1), r)

tidy_gd <- broom.mixed::tidy(sw_m1)%>% 
  mutate(y_var = "gd")

gd_mod <- lmer(gd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

gd_mod_noints <- lmer(gd ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
```

##Flame duration: 

```{r}
sw_m7 <- lmer(fd ~ mpa_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m7)
```

```{r}
max_model_noww <- lmer(fd ~ spp + dw_flam_sample_scaled +  mpa_scaled + lfm_scaled+ excess_water_scaled + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(max_model_noww)
```

```{r}
m15 <- lmer(fd ~ excess_water_scaled * spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m15)
```

```{r}
sw_m12.5 <- lmer(fd ~ excess_water_scaled + mpa_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m12.5) ##High correlation! Don't use
```

```{r}
sw_m1 <- lmer(fd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1)
```

```{r}
m12 <- lmer(fd ~ excess_water_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m12)
```

```{r}
m14 <- lmer(fd ~ excess_water_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m14)
```

```{r}
m1 <- lmer(fd ~ spp +  mpa_scaled + lfm_scaled+ excess_water_scaled + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m1)
```

```{r}
tab_model(m1, 
          #m14, 
          m12, 
         # sw_m1, 
          sw_m12.5 ,
          m15, 
          max_model_noww, 
          sw_m7, 
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          dv.labels = c(
            "m1", 
         # "m14", 
          "m12", 
         # "sw_m1", 
          "sw_m12.5" ,
          "m15", 
          "max_model_noww", 
          "sw_m7"),
         string.pred = "Coeffcient", 
  string.p = "P-Value", 
  p.style = "stars"
  ) 
```


Best model for flame duration: 

```{r}
sw_m1 <- lmer(fd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1)

#check without interaction terms:

sw_m1.5 <- lmer(fd ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1.5)
```

```{r}
m12 <- lmer(fd ~ excess_water_scaled + spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m12)
```
######final model

```{r}
sw_m1 <- lmer(fd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1)
plot(performance::check_collinearity(sw_m1))

qqnorm(resid(sw_m1))
r <- resid(sw_m1)
plot(fitted(sw_m1), r)

tidy_fd <- broom.mixed::tidy(sw_m1)%>% 
  mutate(y_var = "fd")

fd_mod <- lmer(fd ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

fd_mod_noints <- lmer(fd ~ spp+ mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)
```

##Temp change: 

```{r}
sw_m1 <- lmer(temp_change ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1)
```

```{r}
m2 <- lmer(temp_change ~ spp * mpa_scaled + spp* lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m2)
```

```{r}
max_model_noww <- lmer(temp_change ~ spp + dw_flam_sample_scaled +  mpa_scaled + lfm_scaled+ excess_water_scaled + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(max_model_noww)
```

```{r}
m15 <- lmer(temp_change ~ excess_water_scaled * spp + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m15)
```

```{r}
sw_m11 <- lmer(temp_change ~ mpa_scaled*spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m11)
```

```{r}
sw_m12.5 <- lmer(temp_change ~ excess_water_scaled + mpa_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m12.5) ##High correlation! Don't use
```

```{r}
sw_m7 <- lmer(temp_change ~ mpa_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m7)
```

```{r}
tab_model(sw_m1, 
          m2,
         # m12, 
          sw_m11,
          sw_m12.5 ,
          m15, 
          max_model_noww, 
          sw_m7, 
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          dv.labels = c(
            "sw_m1", 
         "m2",
          #"m12", 
        "sw_m11",
          "sw_m12.5" ,
          "m15", 
          "max_model_noww", 
          "sw_m7"),
         string.pred = "Coeffcient", 
  string.p = "P-Value", 
  p.style = "stars"
  ) 
```

######final model

```{r}
sw_m1 <- lmer(temp_change ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1)

#check without interaction terms: 

sw_m1.5 <- lmer(temp_change ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1.5)


qqnorm(resid(sw_m1))
r <- resid(sw_m1)
plot(fitted(sw_m1), r)

tidy_temp_change <- broom.mixed::tidy(sw_m1)%>% 
  mutate(y_var = "temp_change")

temp_change_mod <- lmer(temp_change ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all) 

temp_change_mod_noints <- lmer(temp_change ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all) 
```


##Prop ignite: 

```{r}
sw_m1 <- lmer(prop_ignite ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1)
```

```{r}
m2 <- lmer(prop_ignite ~ spp * mpa_scaled + spp* lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m2)
```

```{r}
sw_m7 <- lmer(prop_ignite ~ mpa_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m7)
```

```{r}
sw_m11 <- lmer(prop_ignite ~ mpa_scaled*spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m11)
```

```{r}
sw_m12.5 <- lmer(prop_ignite ~ excess_water_scaled + mpa_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m12.5) ##High correlation! Don't use
```

```{r}
sw_m13 <- lmer(prop_ignite ~ excess_water_scaled + lfm_scaled+ spp + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m13) ##High correlation! Don't use
```

```{r}
tab_model(sw_m1, 
          m2,
         # m12, 
          sw_m7,
         sw_m11,
          sw_m12.5 ,
          sw_m13, 
        
          show.reflvl = TRUE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          dv.labels = c(
            "sw_m1", 
         "m2",
        "sw_m7",
        "sw_m11",
          "sw_m12.5" ,
          "m13"),
         string.pred = "Coeffcient", 
  string.p = "P-Value", 
  p.style = "stars"
  ) 
```


```{r}
sw_m1 <- lmer(prop_ignite ~ spp*mpa_scaled + spp*lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1)
```

```{r}
sw_m1.5 <- lmer(prop_ignite ~ spp + mpa_scaled + lfm_scaled +  site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all)

performance::multicollinearity(sw_m1.5)
```

######final model

```{r}
m2 <- lmer(prop_ignite ~ spp * mpa_scaled + spp * lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m2)

m2.5 <- lmer(prop_ignite ~ spp + mpa_scaled +  lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)

performance::multicollinearity(m2.5)


qqnorm(resid(m2))
r <- resid(m2)
plot(fitted(m2), r)

tidy_prop_ignite <- broom.mixed::tidy(m2) %>% 
  mutate(y_var = "prop_ignite")

prop_ignite_mod <- lmer(prop_ignite ~ spp * mpa_scaled + spp * lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)

prop_ignite_mod_noints <- lmer(prop_ignite ~ spp + mpa_scaled + lfm_scaled  + site + year_month + (1 | individual), data = mem_data_all)
```

#----------------------

#Combine all tidy df: 

```{r}
tidy_all_mems <- bind_rows(tidy_fd, 
                           tidy_fh, 
                           tidy_gd, 
                           tidy_prop_ignite, 
                           tidy_temp_change, 
                           tidy_tti)
write_csv(tidy_all_mems, here::here("processed-data", "analysis 2.0", "tidy_all_mems.csv"))
```

#Combine all table: 

These do have interactions: 
```{r}
tab_model(tti_mod, 
          fh_mod, 
          fd_mod, 
          gd_mod, 
          temp_change_mod, 
          prop_ignite_mod,
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          # dv.labels = c(
          #   "sw_m11", 
          #   "m7",
          #   "m2", 
          #   "sw_m1",
          #   "sw_m12.5", 
          #   "m11"),
         string.pred = "Coeffcient", 
  string.p = "P-Value", 
  p.style = "stars",
  show.reflvl = TRUE, 
  file = here('figures', 'MEM_figures', 'top_models_final.html'))
```
These do NOT have interactions: 
```{r}
tab_model(tti_mod_noints, 
          fh_mod_noints, 
          fd_mod_noints, 
          gd_mod_noints, 
          temp_change_mod_noints, 
          prop_ignite_mod_noints,
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          # dv.labels = c(
          #   "sw_m11", 
          #   "m7",
          #   "m2", 
          #   "sw_m1",
          #   "sw_m12.5", 
          #   "m11"),
         string.pred = "Coeffcient", 
  string.p = "P-Value", 
  p.style = "stars",
  show.reflvl = TRUE, 
  file = here('figures', 'MEM_figures', 'top_mod_nointsels_final.html'))
```

```{r}
tab_model(tti_mod, 
          fh_mod, 
          fd_mod, 
          gd_mod, 
          temp_change_mod, 
          prop_ignite_mod,
          digits = 3, 
          show.aic = FALSE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          # dv.labels = c(
          #   "sw_m11", 
          #   "m7",
          #   "m2", 
          #   "sw_m1",
          #   "sw_m12.5", 
          #   "m11"),
         string.pred = "Coeffcient", 
  string.p = "P-Value", 
  p.style = "stars",
  show.reflvl = TRUE,
    pred.labels = c('Intercept', 
                    'LFM (scaled)', 
                    'MPa (scaled)', 
                      'Sample weight (scaled)',
                    'Site',
                    # 'Sequoia Sites',
                     'CZO Sites',
                  
                   # 'A. concolor',
                    'A. patula',
                     'C. decurrens', 
                    'C. cordulatus', 
                    'P. jeffryii', 
                     'Q. kelloggii', 
                    'LFM x A. patula',
                     'MPa x A. patula',
                    'LFM x C. decurrens', 
                    'MPa x C. decurrens', 
                    
                     'LFM x C. cordulatus', 
                     'MPa x C. cordulatus', 
                    
                     'LFM x P. jeffryii', 
                     'MPa x P. jeffryii', 
                  
                     'LFM x Q. kelloggii',
                     'MPa x Q. kelloggii'
                    
                   ), 
  file = here('figures', 'MEM_figures', 'top_models_pretty.html'))
  
```
