---
title: "Visualizations and Summaries - Figures"
author: "Indra Boving & Joe Celebrezze"
date: "6/21/2022"
output: html_document
---
# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(tidyverse)
library(ggpubr)
library(cowplot)
#library(strengejacke)
library(sjPlot) # table functions
library(here)
library("broom.mixed")
library(nlme)
library(lme4)
library(remef)
library(kableExtra)
library(modelr)
library(lubridate)
library(ggbeeswarm)

#some weird functions:
filter = dplyr::filter
mutate = dplyr::mutate
select = dplyr::select
here = here::here
group_by = dplyr::group_by

source(here("scripts", "scripts_functions", "figure_info_sierra_flammability.R")) #color and theme info is here
```

Goal here is to make a plot that shows flammability over time: 

1. Get a df of field LFM and MPa values
2. Use best lm to predict TTI, FH, and Max temp from corresponding LFM/Mpa
#Data: 
```{r}
field_data_all_6_raw <- read_csv(here("processed-data", "field_data_2020_2021.csv")) 

field_data_all_6 <-  field_data_all_6_raw %>% 
 # mutate(mpa = -1*mpa) %>% 
 # filter(age_new == "new") %>% 
  filter(lfm < 350) %>% #remove weirdly large LFMS
  filter(lfm > 50) %>% 
  select(spp, lfm, year, month, water_potential, site, wet_weight, unique_id, date, midday, age_new) %>% 
  filter(wet_weight > 50) %>% #remove weirdly small wet weights
  #group_by(spp) %>% 
  mutate(mpa = -1*water_potential,
    lfm_scaled = c(scale(lfm)), 
    #lfm_scaled = lfm,
     mpa_scaled = c(scale(mpa)), 
    #mpa_scaled = mpa, 
        # mpa = water_potential, 
         year_month = paste(year, month, sep = "_", collapse = NULL),
        # sample_wt_scaled = c(scale(wet_weight)), 
     sample_wt_scaled = 1,
         individual = unique_id, 
         spp = tolower(spp)) %>% 
  mutate(Species = case_when(
    spp == "arpa" ~ "Ar. patula", 
    spp == "abco" ~ "Ab. concolor",
    spp == "cade" ~ "Ca. decurrens",
    spp == "ceco" ~ "Ce. cordulatus",
    spp == "pije" ~ "Pi. jeffreyi",
    spp == "quke" ~ "Qu. kelloggii"
  )) %>% 
  filter(spp != "ceco") %>% 
  drop_na(spp) %>% 
  mutate(mpa_scaled = as.numeric(mpa_scaled), 
         lfm_scaled = as.numeric(lfm_scaled), 
         sample_wt_scaled = as.numeric(sample_wt_scaled)) 

field_data_all_6$Species <- factor(field_data_all_6$Species, levels = c('Ab. concolor',  'Pi. jeffreyi', 'Ca. decurrens', 'Ar. patula', 'Qu. kelloggii'))
field_data_all_6$spp <- factor(field_data_all_6$spp, levels = c("abco", "pije", "cade", "arpa", "quke"))

mem_data_all_6 <- read_csv(here("processed-data", "sierra_flam_data_all.csv"), show_col_types = FALSE) %>% 
   select(lfm, mpa, fh, fh, fd, gd,tti, prop_ignite, temp_change, lower_temp_max, ignition, sample_wt, dry_wt, fresh_wt, water_wt, location, site, year_month, spp, individual, bins10lfm, bins5lfm, bins20lfm, notes_flam) %>% 
  mutate(dw_flam_sample = sample_wt * (dry_wt/fresh_wt),
         ww_flam_sample = sample_wt * (water_wt/fresh_wt),
         excess_water = (ww_flam_sample - dw_flam_sample),
         mpa_scaled = scale(mpa)) %>% 
  group_by(spp) %>% 
  mutate(dw_flam_sample_scaled = scale(dw_flam_sample), 
         sample_wt_scaled = scale(sample_wt), 
         ww_flam_sample_scaled = scale(ww_flam_sample),
         lfm_scaled = scale(lfm), 
         excess_water_scaled = scale(excess_water)) %>% 
  ungroup() %>% 
  filter(!year_month %in% c("2021_august")) %>% 
  mutate(fun_gr = case_when(
    spp == "arpa" ~ "Angiosperm", 
    spp == "abco" ~ "Gymnosperm",
    spp == "cade" ~ "Gymnosperm",
    spp == "ceco" ~ "Angiosperm",
    spp == "pije" ~ "Gymnosperm",
    spp == "quke" ~ "Angiosperm"
  ))  %>% 
  mutate(Species = case_when(
    spp == "arpa" ~ "Ar. patula", 
    spp == "abco" ~ "Ab. concolor",
    spp == "cade" ~ "Ca. decurrens",
    spp == "ceco" ~ "Ce. cordulatus",
    spp == "pije" ~ "Pi. jeffreyi",
    spp == "quke" ~ "Qu. kelloggii"
  )) %>% 
  filter(ignition != 2) %>% # Removing manual ignitions
  drop_na(mpa_scaled, lfm_scaled, sample_wt_scaled)  %>% 
  filter(spp != "ceco") %>% 
  mutate(mpa_scaled = as.numeric(mpa_scaled), 
         lfm_scaled = as.numeric(lfm_scaled), 
         sample_wt_scaled = as.numeric(sample_wt_scaled))
```


```{r}
field_data_all_6 %>% 
ggplot()+
  geom_point(aes(y = wet_weight, 
                 x = week(date), 
                 shape = as.factor(year(date)))) +
  facet_wrap(~spp)


field_data_all_6 %>% 
ggplot()+
  geom_histogram(aes(y = wet_weight)) +
  facet_wrap(~spp)

field_data_all_6 %>% 
ggplot()+
  geom_histogram(aes(y = sample_wt_scaled)) +
  facet_wrap(~spp)

sw <- aov(sample_wt_scaled ~ spp, data = mem_data_all_6)
summary(sw)

TukeyHSD(sw, conf.level=.95)

field_data_all_6 %>% 
  ggplot(aes(y = mpa, x = lfm, color = spp)) +
  geom_point()

mem_data_all_6 %>% 
  ggplot(aes(y = mpa, x = lfm, color = spp)) +
  geom_point()
```


```{r}
mem_data_all_6 %>% 
ggplot()+
  geom_histogram(aes(y = sample_wt)) +
  facet_wrap(~spp)

mem_data_all_6 %>% 
ggplot()+
  geom_histogram(aes(y = sample_wt_scaled)) +
  facet_wrap(~spp)

sw <- aov(sample_wt_scaled ~ spp, data = mem_data_all_6)
summary(sw)

TukeyHSD(sw, conf.level=.95)
```

# TTI

```{r}
tti_mod <- lm(tti ~ spp*lfm_scaled + sample_wt_scaled
              , data = mem_data_all_6)
summary(tti_mod)

tti_df <- field_data_all_6 %>%
  modelr::add_predictions(tti_mod)

tti_pred <- tti_df %>% 
  filter(year == 2021) %>% 
ggplot() +
  geom_jitter(aes(y = pred*-1, 
                 x = date, 
                 color = spp,
                 shape= age_new), alpha = .3, size = 2
             ) +
  geom_smooth(aes(y = pred*-1, x = date, color = spp),span = .6,
              se = F) +
  theme(legend.position = "none",
        axis.text.y = element_text(size = 14),
        #axis.text.x = element_text(size = 18),
        axis.title = element_text(size = 22, face = 'bold'),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = unit(c(0, 0.1, 0, 0.1), 'cm')) +
  labs(y = "Ignitability", 
       x = "") +
  color_many
tti_pred
```

#FH:
```{r}
fh_mod <- lm(fh ~mpa_scaled + spp*lfm_scaled 
            # + site
             + sample_wt_scaled,
             data = mem_data_all_6)

fh_df <- field_data_all_6 %>% 
  modelr::add_predictions(fh_mod)

fh_pred <- fh_df %>% 
  filter(year == 2021) %>% 
ggplot() +
  geom_jitter(aes(y = pred, 
                 x = date, 
                 color = spp), alpha = .3, size = 2
             ) +
  geom_smooth(aes(y = pred, x = date, color = spp), 
              span = .6,
              se = F) +
  theme(legend.position = "none",
        axis.text.y = element_text(size = 14), 
        #axis.text.x = element_text(size = 18),
        axis.title = element_text(size = 22, face = 'bold'),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = unit(c(0, 0.1, 0, 0.5), 'cm')) +
  labs(y = "Flame Height", 
       x = "")+
  color_many
fh_pred
```

#Max Temp

```{r}
lower_temp_max_mod <- lm(lower_temp_max ~ mpa_scaled 
                           + spp*lfm_scaled 
                           #+  site 
                          #+ year_month 
                           + sample_wt_scaled
                           ,data = mem_data_all_6)

temp_max_df <- field_data_all_6 %>% 
  modelr::add_predictions(lower_temp_max_mod)

temp_max_pred <- temp_max_df %>% 
  filter(year == 2021) %>% 
ggplot() +
  geom_point(aes(y = pred, 
                 x = date, 
                 color = spp), alpha = .3, size = 2
             ) +
  geom_smooth(aes(y = pred, x = date, color = spp), 
              span = .6,
              se = F) +
  theme(legend.position = "none") +
  labs(y = "Max. Temperature", 
       x = " ")+
  color_many +
  theme(legend.position = "none",
        axis.text.y = element_text(size = 14), 
        axis.text.x = element_text(size = 18),
        axis.title = element_text(size = 22, face = 'bold'),
        plot.margin = unit(c(0, 0.1, 0.1, 0.2), 'cm'))
temp_max_pred
```

#Temp change

```{r}
temp_mod <- lm(temp_change ~spp*lfm_scaled 
              + sample_wt_scaled 
              #+ (1 | individual)
              , data = mem_data_all_6)

temp_df <- field_data_all_6 %>% 
  modelr::add_predictions(temp_mod)

temp_pred <- temp_df %>% 
  filter(year == 2021) %>% 
ggplot() +
  geom_point(aes(y = pred, 
                 x = date, 
                 color = spp), alpha = .3, size = 2
             ) +
  geom_smooth(aes(y = pred, x = date, color = spp), 
              span = .6,
              se = F) +
  labs(y = "Temp Change", 
       x = "Date")+
  color_many +
  theme(legend.position = "none",
        axis.text.y = element_text(size = 14), 
        axis.text.x = element_text(size = 18),
        axis.title = element_text(size = 22, face = 'bold'))
temp_pred
```

##Combine together: 

```{r}
leg_plot_pred<- temp_df %>% 
 # mutate(spp = fct_relevel(spp, "ABCO","PIJE","CADE","ARPA", "CECO", "QUKE")) %>% 
ggplot() +
  geom_point(aes(y = pred, 
                 x = date, 
                 color = Species), alpha = .6, size = 2.8) +
  geom_smooth(aes(y = pred, x = date, color = Species), se = F)+
  labs(color = "Species") +
  theme(legend.title = element_text(face = 'bold', size = 22),
        legend.text = element_text(face = 'italic', size = 20),
        legend.key = element_blank()) +
  color_noceco
leg_plot_pred
```

```{r}
legend <- cowplot::get_legend(leg_plot_pred)

plots <- cowplot::plot_grid(tti_pred, fh_pred, 
                            #temp_pred, 
                            temp_max_pred,
                                   ncol = 1
                                   , rel_heights = c(1, 1, 1,1)
                                   )

legend_plots <- cowplot::plot_grid(plots, legend, 
                                   ncol = 2,
                                   rel_widths = c(3,1)#rel_widths = c(6,.5)
                                   )
legend_plots
```
#-------
# MAIN FIGURE
Using mean LFM, MPa, Sample Weight instead of all observations per week
```{r}
field_data_all_means <- field_data_all_6 %>% 
  mutate(date = case_when(
    date == '2021-04-24' ~ "04/24",
    date == '2021-05-14' ~ "05/14",
    date == '2021-05-15' ~ "05/14",
    date == '2021-06-15' ~ "06/15",
    date == '2021-06-16' ~ "06/15",
    date == '2021-07-08' ~ "07/8",
    date == '2021-07-09' ~ "07/8",
    date == '2021-07-30' ~ "07/30",
    date == '2021-07-31' ~ "07/30",
    date == '2021-08-19' ~ "08/19",
    date == '2021-08-20' ~ "08/19",
    date == '2021-09-16' ~ "09/16",
    date == '2021-09-17' ~ "09/16",
    date == '2021-10-16' ~ "10/16",
    date == '2021-10-17' ~ "10/16"
  )) %>%
  drop_na(lfm_scaled, mpa_scaled, sample_wt_scaled) %>% 
  group_by(spp, month) %>% 
  mutate(lfm_scaled = mean(lfm_scaled, na.rm = T),
         mpa_scaled = mean(mpa_scaled, na.rm = T),
         sample_wt_scaled = mean(sample_wt_scaled, na.rm = T)) %>%
  ungroup()
field_data_all_means$date <- as.Date(field_data_all_means$date, format='%m/%d')
```

For labels:
```{r}
x <- as.Date(c(rep('2023-04-24', 5)))
y <- c(-34, 49.5, 44.2, 365, 90)
labs <- c('a', 'b', 'c', ' ', 'd')
plot <- c('tti', 'fh', 'fd', 'mt', 'tc')
labelData <- data.frame(x, y, labs, plot)
```


## TTI
```{r}
tti_df <- mem_data_all_6 %>% 
  drop_na(mpa_scaled, 
          lfm_scaled, sample_wt_scaled, tti)

tti_mod <- lm(tti ~ spp*lfm_scaled + mpa_scaled + sample_wt_scaled, data = tti_df)
summary(tti_mod)

tti_df <- field_data_all_means %>% 
  modelr::add_predictions(tti_mod) %>% 
   drop_na(pred) 

# To get standard deviations
tti_df_stdev <- field_data_all_6 %>% 
  add_predictions(tti_mod)

tti_df_stdev <- tti_df_stdev %>% 
  drop_na(pred) %>% 
  group_by(spp, month) %>% 
  mutate(stdev.pred = sd(pred))

tti_df <- tti_df %>% 
  mutate(stdev.pred = tti_df_stdev$stdev.pred)

tti_pred <- tti_df %>%
  filter(year == 2021) %>% 
  ggplot(aes(y = pred*-1, x = date, color = spp)) +
   geom_point(alpha = .3, size = 2) +
   #geom_smooth(se = F) +
   geom_line() +
  # geom_linerange(aes(ymin = pred*-1 - 0.5*stdev.pred, ymax = pred*-1 + 0.5*stdev.pred)) +
   scale_y_continuous(breaks = c(-100, -80, -60, -40)) +
    theme(legend.position = "none",
        axis.text.y = element_text(size = 14),
        #axis.text.x = element_text(size = 18, angle = 20),
        axis.title = element_text(size = 22, face = 'bold'),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = unit(c(0.05, 0.1, 0, 0.1), 'cm')) +
    labs(y = "Ignitability (-1*sec)", 
       x = "") +
    geom_text(data = subset(labelData, subset = plot == 'tti'),
              aes(x, y, label = labs, group = NULL, color = NULL),
              size = 12, fontface = 'bold') +
    color_noceco
tti_pred
```

## FH
```{r}
fh_df <- mem_data_all_6 %>% 
  drop_na(mpa, lfm, fh)
fh_mod <- lm(fh ~  spp*lfm_scaled + mpa_scaled + sample_wt_scaled, data = fh_df)
summary(fh_mod)

fh_df <- field_data_all_means %>% 
  modelr::add_predictions(fh_mod)
# To get standard deviations
fh_df_stdev <- field_data_all_6 %>% 
  add_predictions(fh_mod) %>% 
  drop_na(pred) %>% 
  group_by(spp, month) %>% 
  mutate(stdev.pred = sd(pred)) %>% 
  select(unique_id, stdev.pred)

fh_df1 <- merge(fh_df, fh_df_stdev, by = c("unique_id")) %>% 
  distinct()

fh_df <- fh_df %>% 
  mutate(stdev.pred = fh_df_stdev$stdev.pred)

fh_pred <- fh_df %>%
  filter(year == 2021) %>% 
  ggplot(aes(y = pred, x = date, color = spp)) +
   geom_point(alpha = .3, size = 2) +
   #geom_smooth(se = F) +
   geom_line() +
  # geom_linerange(aes(ymin = pred - 0.5*stdev.pred, ymax = pred + 0.5*stdev.pred)) +
   scale_y_continuous(limits = c(25, 51), breaks = c(30, 35, 40, 45)) +
   theme(legend.position = "none",
        axis.text.y = element_text(size = 14),
        #axis.text.x = element_text(size = 18, angle = 20),
        axis.title = element_text(size = 22, face = 'bold'),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = unit(c(0, 0.1, 0, 0.5), 'cm')) +
    labs(y = "Flame Height (cm)", 
       x = "") +
   geom_text(data = subset(labelData, subset = plot == 'fh'),
              aes(x, y, label = labs, group = NULL, color = NULL),
              size = 12, fontface = 'bold') +
    color_noceco
fh_pred
```

## FD
```{r}
fd_df <- mem_data_all_6 %>% 
  drop_na(mpa, lfm, fd)
fd_mod <- lm(fd ~ mpa_scaled*spp + lfm_scaled*spp + sample_wt_scaled, data = fd_df)
summary(fd_mod)

fd_df <- field_data_all_means %>% 
  modelr::add_predictions(fd_mod)
# To get standard deviations
fd_df_stdev <- field_data_all_6 %>% 
  add_predictions(fd_mod)
fd_df_stdev <- fd_df_stdev %>% 
  drop_na(pred) %>% 
  group_by(spp, month) %>% 
  mutate(stdev.pred = sd(pred))
fd_df <- fd_df %>% 
  mutate(stdev.pred = fd_df_stdev$stdev.pred)

fd_pred <- fd_df %>%
  filter(year == 2021) %>% 
  ggplot(aes(y = pred, x = date, color = spp)) +
   geom_point(alpha = .3, size = 2) +
   #geom_smooth(se = F) +
   geom_line() +
   geom_linerange(aes(ymin = pred - 0.5*stdev.pred, ymax = pred + 0.5*stdev.pred)) +
   #scale_y_continuous(limits = c(16, 46), breaks = c(20, 25, 30, 35, 40)) +
    theme(legend.position = "none",
        axis.text.y = element_text(size = 14),
        #axis.text.x = element_text(size = 18, angle = 20),
        axis.title = element_text(size = 22, face = 'bold'),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = unit(c(0, 0.1, 0, 0.5), 'cm')) +
    labs(y = "Flame Duration (sec)", 
       x = "") +
    geom_text(data = subset(labelData, subset = plot == 'fd'),
              aes(x, y, label = labs, group = NULL, color = NULL),
              size = 12, fontface = 'bold') +
    color_noceco
fd_pred
```

## Max Temp
```{r}
temp_max_df <- mem_data_all_6 %>% 
  drop_na(mpa, lfm, lower_temp_max)
temp_max_mod <- lm(lower_temp_max ~ mpa_scaled + spp*lfm_scaled +
                           sample_wt_scaled, data = temp_max_df)
summary(temp_max_mod)

temp_max_df <- field_data_all_means %>% 
  modelr::add_predictions(temp_max_mod)
#To get standard deviations
temp_max_df_stdev <- field_data_all_6 %>% 
  add_predictions(temp_max_mod)
temp_max_df_stdev <- temp_max_df_stdev %>% 
  drop_na(pred) %>% 
  group_by(spp, month) %>% 
  mutate(stdev.pred = sd(pred))
temp_max_df <- temp_max_df %>% 
  mutate(stdev.pred = temp_max_df_stdev$stdev.pred)

temp_max_pred <- temp_max_df %>%
  filter(year == 2021) %>% 
  ggplot(aes(y = pred, x = date, color = spp)) +
   geom_point(alpha = .3, size = 2) +
   #geom_smooth(se = F) +
   geom_line() +
   geom_linerange(aes(ymin = pred - 0.5*stdev.pred, ymax = pred + 0.5*stdev.pred)) +
    theme(legend.position = "none",
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 18, angle = 20),
        axis.title = element_text(size = 22, face = 'bold'),
        plot.margin = unit(c(0, 0.1, 0.1, 0.2), 'cm')) +
    labs(y = "Maximum Temp. (C)", 
       x = "") +
    geom_text(data = subset(labelData, subset = plot == 'mt'),
              aes(x, y, label = labs, group = NULL, color = NULL),
              size = 12, fontface = 'bold') +
    color_noceco
temp_max_pred
```


## Temp change
```{r}
temp_change_df <- mem_data_all_6 %>% 
  drop_na(mpa, lfm, temp_change)
temp_change_mod <- lm(temp_change ~ mpa_scaled + spp*lfm_scaled +
                           sample_wt_scaled, data = temp_change_df)
summary(temp_change_mod)

temp_change_df <- field_data_all_means %>% 
  modelr::add_predictions(temp_change_mod)
#To get standard deviations
temp_change_df_stdev <- field_data_all_6 %>% 
  add_predictions(temp_change_mod)
temp_change_df_stdev <- temp_change_df_stdev %>% 
  drop_na(pred) %>% 
  group_by(spp, month) %>% 
  mutate(stdev.pred = sd(pred))
temp_change_df <- temp_change_df %>% 
  mutate(stdev.pred = temp_change_df_stdev$stdev.pred)

temp_change_pred <- temp_change_df %>%
  filter(year == 2021) %>% 
  ggplot(aes(y = pred, x = date, color = spp)) +
   geom_point(alpha = .3, size = 2) +
   #geom_smooth(se = F) +
   geom_line() +
   geom_linerange(aes(ymin = pred - 0.5*stdev.pred, ymax = pred + 0.5*stdev.pred)) +
    theme(legend.position = "none",
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 18, angle = 20),
        axis.title = element_text(size = 22, face = 'bold'),
        plot.margin = unit(c(0, 0.1, 0.1, 0.55), 'cm')) +
    labs(y = "Temp. Change (C)", 
       x = "") +
    geom_text(data = subset(labelData, subset = plot == 'tc'),
              aes(x, y, label = labs, group = NULL, color = NULL),
              size = 12, fontface = 'bold') +
    color_noceco
temp_change_pred
```
## Combined
```{r}
plots <- cowplot::plot_grid(tti_pred, fh_pred, fd_pred, temp_change_pred, ncol = 1
                                   ,rel_heights = c(1, 1, 1, 1))

legend_plots <- cowplot::plot_grid(plots, legend, 
                                   ncol = 2,
                                   rel_widths = c(2.8,1))
legend_plots

ggsave(here('figures', 'main-figures', 'Fig4.predicted.flam.from.field_REVISED.jpg'), height = 15, width = 9)
```

#-------

#Boxplots, all 2021: 

NOTE: did not finish this, prob wont. 

#TTI

```{r}
#tti_mod <- lmer(tti ~ spp*mpa_scaled + spp*lfm_scaled + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all_6)
#summary(tti_mod)
#str(mem_data_all_6)

tti_mod <- lm(tti ~ spp*mpa_scaled + spp*lfm_scaled 
              +site + sample_wt_scaled
              , data = mem_data_all_6)
summary(tti_mod)

tti_df <- field_data_all_6 %>% 
  modelr::add_predictions(tti_mod)

df_mean <- tti_df %>% 
  filter(year == 2021) %>% 
  mutate(week_cut = cut(date, breaks = "week")) %>% 
  group_by(week_cut, spp) %>% 
  summarize(average = mean(pred)) %>%
  ungroup() %>% 
  drop_na(average)
	
#tti_pred <- 
  tti_df %>% 
  filter(year == 2021) %>% 
ggplot() +
  geom_point(aes(y = pred*-1, 
                 x = date, 
                 color = spp)) +
  geom_smooth(aes(y = -1*pred, x = date, color = spp), 
              se = F,
              span = .6)+
  theme(legend.position = "none") +
  labs(y = "Ignitability") +
  color_many 

#tti_pred
```

#FH:
```{r}
fh_mod <- lm(fh ~ spp*mpa_scaled + spp*lfm_scaled 
             + site
            # + sample_wt_scaled, 
             ,data = mem_data_all_6)

fh_df <- field_data_all_6 %>% 
  modelr::add_predictions(fh_mod)

fh_pred <- fh_df %>% 
  filter(year == 2021) %>% 
ggplot() +
  geom_beeswarm(aes(y = pred, 
                 x = date, 
                 color = spp)) +
  geom_smooth(aes(y = pred, x = date, color = spp), 
              se = F,
              span = .6) +
  theme(legend.position = "none") +
  labs(y = "Flame Height")+
  color_many
fh_pred
```

#Temp change

```{r}
temp_mod <- lm(temp_change ~ spp*mpa_scaled + spp*lfm_scaled 
              +  site 
             # + year_month 
              + sample_wt_scaled 
              #+ (1 | individual)
              , data = mem_data_all_6)

temp_df <- field_data_all_6 %>% 
  modelr::add_predictions(temp_mod)

temp_pred <- temp_df %>% 
  filter(year == 2021) %>% 
ggplot() +
  geom_point(aes(y = pred, 
                 x = date, 
                 color = spp)) +
  geom_smooth(aes(y = pred, x = date, color = spp), 
              se = F,
              span = .6
  #formula = pred ~ lfm_scaled + mpa_scaled + spp + sample_wt
) +
  theme(legend.position = "none") +
  labs(y = "Temp Change")+
  color_many
temp_pred
```

##Combine together: 

```{r}
leg_plot<- temp_df %>% 
ggplot() +
  geom_point(aes(y = pred, 
                 x = date, 
                 color = spp)) +
  geom_smooth(aes(y = pred, x = date, color = spp)) +
  color_many
```

```{r, fig.height= 4, fig.width=2.5}
legend <- cowplot::get_legend(leg_plot)

plots <- cowplot::plot_grid(tti_pred, fh_pred, temp_pred,
                                   ncol = 1
                                   , rel_heights = c(1, 1, 1)
                                   )

legend_plots <- cowplot::plot_grid(plots, legend, ncol = 2, rel_widths = c(4,1))
legend_plots
```

#-------
#Boxplots, old vs. new

#TTI

```{r}
#tti_mod <- lmer(tti ~ spp*mpa_scaled + spp*lfm_scaled + site + year_month + sample_wt_scaled + (1 | individual), data = mem_data_all_6)
#summary(tti_mod)
#str(mem_data_all_6)

tti_mod <- lm(tti ~ spp*mpa_scaled + spp*lfm_scaled + sample_wt_scaled, data = mem_data_all_6)
summary(tti_mod)

tti_df <- field_data_all_means %>% 
  modelr::add_predictions(tti_mod)


df_mean <- tti_df %>% 
  group_by(spp) %>% 
  summarize(average = -1*mean(pred)) %>%
  ungroup()

tti_pred_box <- tti_df %>% 
  filter(year == 2021, 
         month < 10) %>% 
ggplot() +
  geom_boxplot(aes(y = pred*-1, 
                 x = cut(date, breaks = "quarter"),
                 fill = spp)) +
  # geom_line(aes(y = pred*-1, 
  #               #x = cut(date, breaks = "quarter"),
  #               color = spp)) +
  #geom_line(data = df_mean,
           # mapping = aes(x = cut(date, breaks = "quarter"),
                         # y = average)) +
  theme(legend.position = "none") +
  labs(y = "Ignitability", x = "") +
  color_many
tti_pred_box
```

#FH:
```{r}
fh_mod <- lm(fh ~ spp*mpa_scaled + spp*lfm_scaled 
             + site
             + sample_wt_scaled, 
             ,data = mem_data_all_6)

fh_df <- field_data_all_6 %>% 
  modelr::add_predictions(fh_mod)

fh_pred_box <- fh_df %>% 
  filter(year == 2021, 
         month < 10) %>% 
ggplot() +
  geom_boxplot(aes(y = pred*-1, 
                 x = cut(date, breaks = "quarter"),
                 fill = spp)) +
 # geom_smooth(aes(y = pred*-1, x = date, color = spp)) +
  theme(legend.position = "none") +
  labs(y = "Flame Height", x = "")+
  color_many
fh_pred_box
```

#Temp change

```{r}
temp_mod <- lm(temp_change ~ spp*mpa_scaled + spp*lfm_scaled 
              +  site 
             # + year_month 
              + sample_wt_scaled 
              #+ (1 | individual)
              , data = mem_data_all_6)

temp_df <- field_data_all_6 %>% 
  modelr::add_predictions(temp_mod)

temp_pred_box <- temp_df %>% 
  filter(year == 2021, 
         month < 10) %>% 
ggplot() +
  geom_boxplot(aes(y = pred*-1, 
                 x = cut(date, breaks = "quarter"),
                 fill = spp)) +
 # geom_smooth(aes(y = pred*-1, x = date, color = spp)) +
  theme(legend.position = "none") +
  labs(y = "Temp Change", x = "Date")

temp_pred_box
```

##Combine together: 

```{r}
leg_plot_box<- temp_df %>% 
ggplot() +
  geom_boxplot(aes(y = pred, 
                 x = date, 
                 fill = spp))
```

```{r, fig.height= 4, fig.width=2.5}
legend_box <- cowplot::get_legend(leg_plot_box)

plots_box <- cowplot::plot_grid(tti_pred, fh_pred, temp_pred,
                                   ncol = 1
                                   , rel_heights = c(2, 1, 1)
                                   )

legend_plots_box <- cowplot::plot_grid(plots_box, legend_box, ncol = 2, rel_widths = c(4,1))
legend_plots_box
```

#-------
#just sept: 

```{r}
field_data_all_sept <- field_data_all_6 %>% 
  filter(month %in% c(8,9), 
         year == 2021) %>% 
  filter(lfm < 250)

field_data_all_sept$spp <- factor(field_data_all_sept$spp, levels = c("quke", "arpa", "abco", "pije", "cade"))

lfm_sept <- field_data_all_sept %>% 
  ggplot(aes(y = lfm, 
             x = spp, 
             fill = spp)) +
  geom_boxplot() +
  theme(legend.position = "none")

mpa_sept <- field_data_all_sept %>% 
  ggplot(aes(y = -1*mpa, 
             x = spp, 
             fill = spp)) +
  geom_boxplot() +
  theme(legend.position = "none")


#ALL together:


tti_mod <- lm(tti ~ spp*mpa_scaled + spp*lfm_scaled
              +  site 
              + sample_wt_scaled
              ,data = mem_data_all_6)


fh_mod <- lm(fh ~ spp*mpa_scaled + spp*lfm_scaled 
             + site
             + sample_wt_scaled 
             ,data = mem_data_all_6)

temp_mod <- lm(temp_change ~ spp*mpa_scaled + spp*lfm_scaled 
              +  site 
             # + year_month 
             + sample_wt_scaled 
              #+ (1 | individual)
              , data = mem_data_all_6)


fd_mod <- lm(fd ~ spp*mpa_scaled + spp*lfm_scaled 
              +  site 
             # + year_month 
              + sample_wt_scaled 
              #+ (1 | individual)
              , data = mem_data_all_6)


tti_df <- field_data_all_sept %>% 
  modelr::add_predictions(tti_mod) %>% 
  mutate(pred_tti = pred, 
         .keep = "unused")

tti_fh_df <- tti_df %>% 
  modelr::add_predictions(fh_mod) %>% 
  mutate(pred_fh = pred, 
         .keep = "unused")

tti_fh_temp_df <- tti_fh_df %>% 
  modelr::add_predictions(temp_mod) %>% 
  mutate(pred_temp = pred, 
         .keep = "unused")

tti_fh_temp_fd_df <- tti_fh_temp_df %>% 
  modelr::add_predictions(fd_mod) %>% 
  mutate(pred_fd = pred, 
         .keep = "unused")

pred_long_df <- tti_fh_temp_fd_df %>% 
  pivot_longer(cols = c(pred_temp, pred_tti, pred_fh, pred_fd),
                        names_to = "metric", 
               values_to = "prediction"
               )

pred_long_df$spp <- factor(pred_long_df$spp, levels = c("quke", "arpa", "abco", "pije", "cade"))

allmetrics <- pred_long_df %>% 
  ggplot(aes(y = prediction, 
             #x = metric, 
             fill = spp)) +
  geom_boxplot() +
  facet_wrap(~metric, scales = "free", nrow = 1) +
  theme(legend.position = "none")

legend <- get_legend(pred_long_df %>% 
  ggplot(aes(y = prediction, 
             #x = metric, 
             fill = spp)) +
  geom_boxplot())

p1 <- cowplot::plot_grid(lfm_sept, mpa_sept, allmetrics, ncol = 1)
p1

p2 <- cowplot::plot_grid(p1, legend, ncol = 2, rel_widths = c(3,.5))
p2
```



